---
title: "Untitled"
author: "Yingjie"
date: "3/26/2020"
output:
  word_document: default
  pdf_document: default
  html_document: default
editor_options: 
  chunk_output_type: console
---


# Dirs and packages
```{r include=FALSE}
### To clear your environment 
remove(list = ls())

## set work dir
path <- rstudioapi::getSourceEditorContext()$path
dir  <- dirname(rstudioapi::getSourceEditorContext()$path); dir
setwd(dir)
getwd()
dirname(dir)
setwd(dirname(dir))
getwd()

dir.raw     <- './Data/data_raw/'
dir.results <- './Data/data_results/'
dir.figures <- './Data/figures/';      dir.figures


source('./Code/_packages.R')
library(writexl)

```




#  1.  Data

## 1.1 SDG coded data cleaning

### - goal level data (df1)

```{r}

## main data read in
getwd()
xls   <- paste0(dir.raw, 'UNGSII/Yingjie_data_02242020_YL.xlsx'); xls
excel_sheets(xls)

sheet   <- '2017 detailed data'; 
data_yr <- as.numeric(gsub("\\D", "", sheet)); data_yr
df17    <- readxl::read_excel(path = xls, sheet = sheet) %>% 
  dplyr::mutate(yr = data_yr) %>%
  as.data.frame()

sheet   <- '2018 detailed data'; 
data_yr <- as.numeric(gsub("\\D", "", sheet)); data_yr
df18    <- readxl::read_excel(path = xls, sheet = sheet) %>% 
  dplyr::mutate(yr = data_yr) %>%
  as.data.frame()

df0     <- rbind(df17, df18)


## data cleaning - goal level --------------------------------------------------
names(df0)
str(df0)
names(df0) <- c("Company", "Region", "Target", "SDG", 'n_statement', 'yr')
# unique(df0$Target)
unique(df0$SDG)

n_sdg    <- length(unique(df0$SDG)) -2; n_sdg
n_target <- length(unique(df0$Target)); n_target
print(paste0('There are total ', n_sdg,    ' goals.'))
print(paste0('There are total ', n_target, ' SDG targets.'))


### split the goal id and description into 2 cols
# df_splt <- colsplit(df0$SDG, pattern = ' ', c('goal', 'goal_desc'))
# df1 <- cbind(df0, df_splt) 

df1 <- separate(data = df0, col = SDG, sep = " ", remove = F,
                extra = 'merge',
                into = c('goal', 'goal_desc')) %>%
  # dplyr::mutate(Target = gsub('\\(', '', Target),
  #               Target = gsub('\\)', '', Target)) %>%
  # dplyr::mutate(Target = trimws(Target)) %>%
  as.data.frame()


sort(unique(df1$goal))
df1$goal <- factor(df1$goal, levels = c(paste0('SDG', seq(1, 17)), 'SDG', 'noSDG'))
levels(df1$goal)
```



### - target level data (df2)

  Since there is no Target ID in the raw dataset. The author manfully coded the target ID based on the description from UN's SDG indicator list, and then left join the coded target ID to the raw dataset.
  
  This target list includes unique values from both 2017 and 2018 data. 
  
```{r}
### Tidy target and add numbered ID --------------------------------------------
ls_target_df1 <- df1 %>% distinct(SDG, Target) %>% arrange(SDG, Target)

fname <- './Data/data_raw/_ls_goal_target.xlsx'; fname
writexl::write_xlsx(x = ls_target_df1, path = fname)


### --> read in manually matched target list 
ls_target <- readxl::read_xlsx(path = './Data/data_raw/_ls_goal_target_manualTidy.xlsx', sheet = 1) %>%
  dplyr::select(Target_id, Target) %>%
  dplyr::distinct(Target_id, Target, .keep_all = T) %>%
  # dplyr::mutate(Target = gsub('\\(', '', Target),
  #               Target = gsub('\\)', '', Target)) %>%
  # dplyr::mutate(Target = trimws(Target)) %>%
  separate(col = Target_id, into = c('goal_id', 'target_id'), sep = '\\_', remove = F) %>%
  as.data.frame()

str(ls_target)



### Match UNGSII's target name with UN's ----------------------------------------
### --> UN Goal and Target list 
library(reshape2)
ls_un <- read.csv('./Data/data_raw/_ls_un_goal_target.csv', stringsAsFactors = F) %>%
  dplyr::filter(!is.na(GoalID)) %>%
  tidyr::separate(Targets, c('target_id_un', 'target_desc_un'), 
           sep = ' ', extra = 'merge', remove = T)
str(ls_un)
ls_un_id <- ls_un %>%
  dplyr::select(GoalID, target_id_un) %>%
  separate(target_id_un, c('target_id_un1', 'target_id_un2'), 
           sep = '\\.', remove = F) %>%
  dplyr::select(-target_id_un1) %>%
  dplyr::mutate(goalname = paste0('SDG', GoalID))
str(ls_un_id)
ls_un_id$goalname <- factor(x = ls_un_id$goalname, levels = unique(ls_un_id$goalname))


### --> merge the two lists 
names(df1)
str(df1)
df1.2 <- merge(x = df1, y = ls_target, by.x = 'Target', by.y = 'Target', all.x = T) %>%
  ungroup() %>%
  arrange(!is.na(Target_id), goal, Target_id) #%>%
  ### check on any duplicated records as I re-coded Target to Target_id
  # dplyr::count(Company, Target_id) %>%




### --> unique target description in the original raw data set, & new coded data -------------------
target_desc_raw <- df1.2 %>% 
  dplyr::select(#Company, goal, 
                Target_id, Target) %>%
  distinct(Target, .keep_all = T)

target_desc_new <- df1.2 %>% 
  dplyr::select(#Company, goal, 
                Target_id, Target) %>%
  distinct(Target_id, .keep_all = T)


### --> Use new coded target ID (`Target_id`) for the final `level 2 data` -------------------------
###     Because I further coded the target ids (i.e., 'Target_id') based on the raw data (i.e., 'Target'), it is necessary to summarize the data and keep unique 'Target_id' and 'n_statement'. 
names(df1.2)

df2 <- df1.2 %>%
  ungroup() %>%
  dplyr::group_by(Company, Region, 
                  Target,  ## this has been re-coded
                  SDG, 
                  # n_statement,
                  goal, goal_desc, Target_id, goal_id, target_id, yr) %>%
  dplyr::summarise(n_statement = sum(n_statement, na.rm = T)) %>%
  ## correct company names
  dplyr::mutate(Company = gsub('Northrop Gruman', 'Northrop Grumman', Company)) %>%
  # mutate(id = seq.int(nrow(.))) %>%
  arrange(yr, goal, Target_id)


# unique(df2$n)
names(df2)
unique(df2$goal)


### --> to check if any not matched rows, then add to the manual coding xls - "_ls_goal_target_manualTidy.xlsx"
df2_na <- df2 %>% dplyr::filter(is.na(Target_id)); df2_na
# writexl::write_xlsx(x = df2_na, path = './data_raw/_ls_goal_target_na_notMatch.xlsx')

hist(df2$n_statement)
# boxplot(df2$n_statement)
length(unique(df2$Company))
```




```{r - compare 2017 vs 2018}
### company list in the coded data (356) -----------------------------------------------------------
com_df2_byYear <- df2 %>%
  ungroup() %>%
  dplyr::select(Company, yr, n_statement) %>%
  group_by(yr, Company) %>%
  dplyr::summarise(n = sum(n_statement, na.rm = T)/17) %>%
  as.data.frame()

## data in wide format
com_df2_byYear_w <- com_df2_byYear %>%
  spread(key = yr, value = n) %>%
  as.data.frame()

## plot to compare the difference
com_df2_byYear_w %>%
  ggplot(aes(x = `2018`, y = `2017`)) +
  # ggplot(aes(x = log(`2018`), y = log(`2017`))) +
  geom_point() +
  geom_smooth(formula = y~x, method = 'lm') +
  theme_bw()

```



### - save data
```{r}

## save as RData
fname <- paste0(dir.results, 'df1_df2.RData'); fname
save(df1, df2, file = fname)
save(ls_un_id, file = paste0(dir.results, 'ls_un_id.RData'))


## or save as XLSX
fname <- paste0(dir.results, 'df1.xlsx'); fname
writexl::write_xlsx(df1, path = fname)
fname <- paste0(dir.results, 'df2.xlsx'); fname
writexl::write_xlsx(df2, path = fname)
```




## 1.2 Company info cleaning

  In addition to the company names in the coded data, there are `two` other data sets that include more detailed company information. 
  
  Here, we need to use the other two to enrich the company info we have in the coded data. 
  
```
Yingjie_Companies_190930_updateYL.xlsx
          |
          v
         com1  -->  com2  -----------------> `com700`
                                                 |
                                                 |
                                                 |
Companies in SCR500.xlsx                         |
          |                                      |
          v                                      |
      `com500`-----------------------            |
                                    |            v
                                    |------> `com500_plus` ------> `com_final`
                                    |
      `com_ls_inData` ---------------
```



### * Company info - in data
```{r}
names(df2)

com_ls_inData <- df2 %>%
  ungroup() %>%
  group_by(yr) %>%
  dplyr::distinct(Company, Region)


com_ls_2018 <- com_ls_inData %>%
  dplyr::filter(yr == 2018) %>%
  as.data.frame()
```


### * Company info - 700+

```{r - clean 700+ com}
## company info - all 700+
xls <- paste0(dir.raw, 'UNGSII/Yingjie_Companies_190930_updateYL.xlsx')
excel_sheets(xls)
sheet <- "Companies"
com0 <- readxl::read_excel(path = xls, sheet = sheet)
names(com0)
head(com0, 2)

### cleaning data --------------------------------------------------------------
names(com0) <- c("Company", 'Industry', 'Industry2', 
                 "Country", 'Continent', 'Location', 'name_long', 'ISIN')
com1 <- com0 %>% ## create a new name col for the country
  dplyr::mutate(Country = gsub(' in general', '', Country)) %>%
  dplyr::select(-c(Industry2, Location, name_long, ISIN))

### detect rows containing NA values in any column 
com1 %>% filter_all(any_vars(is.na(.))) ## if no NA, then good
```



```{r - industry info}
### check industry info
n.industry <- unique(com0$Industry); #n.industry
print(paste0('There are total ', length(n.industry), ' industries.'))

### number of countries by industry --------------------------------------------
ls_industry <- com1 %>%
  group_by(Industry) %>% tally() %>% arrange(n)

## write to local and tidy this list 
# writexl::write_xlsx(x = ls_industry, path = './Data/data_raw/_ls_industry.xlsx')


### read in again after clearning up Industry info ----------------------------
df.industry <- 
  readxl::read_excel(path = paste0(dir.raw, '_ls_industry_manualTidy.xlsx')) %>%
  # dplyr::select(Industry, ind) %>%
  dplyr::mutate(ind_agg = str_to_sentence(ind_agg),
                ind_7sys= str_to_sentence(ind_7sys))


### change to factor and add levels
unique(df.industry$ind_7sys)

ind_levels <- c(
  "Energy, natural resources, and basic materials", ## primary
  "Industrial manufacturing",                       ## secondary
  "Mobility and transportation",
  "Healthcare and life sciences",                   ## Tertiary
  "Telecommunications and technology",
  "Financial services",
  "Food, beverage, and consumer goods",             ## Quaternary         
  "Media & entertainment"
)


## --> shorten the names for label use
ind_labels <- c(
  'Resources and materials',
  'Industrial manufacturing',
  'Mobility and transportation',
  'Healthcare',
  'IT and Telecommunications',
  'Financial services',
  'Food and consumer goods',
  'Media & entertainment'
)

df.industry <- df.industry  %>%
  dplyr::mutate(
    ## choose one classification sys for analysis
    ind_7sys = factor(ind_7sys, levels = ind_levels), # , labels = ind_labels
    ind = ind_7sys) %>%
  dplyr::select(-n, -id)


### --> add the updated industry info to the company dataframe
com2 <- merge(com1, df.industry, by = 'Industry', all.x = T)
str(com2)

```



```{r - country name info}
names(com2)
head(com2, 2)

### save the nation info to local to coding the ISO3
### 52 countries
df.ctr <- com2 %>% dplyr::select(Continent, Country) %>%
  distinct(Country, .keep_all = T) %>%
  arrange(Country) 
writexl::write_xlsx(x=df.ctr, path = paste0(dir.raw, '_country_info_raw.xlsx'))

df.ctr.test <- com2 %>% dplyr::filter(Country=='South Africa (Rep.)')
## change one row using "South Africa" to "South Africa (Rep.)". Raw data error. 

### read in the updated and manually coded country info
ctr <- readxl::read_excel(path = paste0(dir.raw, '_country_info_raw_iso3.xlsx'), 
                          range = 'B1:C100') %>%
  filter(!is.na(Country))

com700 <- com2 %>%
  merge(., ctr, 'Country', all.x = T) %>%
  dplyr::mutate(
    Company = gsub('Northrop Gruman', 'Northrop Grumman', Company),
    Company = gsub('Anheuser-Busch \\(AB InBev\\)', 'AB Inbev', Company),
    Company = trimws(Company),
    Continent = ifelse(Company =='Emirates Group', 'Asia', Continent),
                )
str(com700)
```


### * Company info - 500+

```{r}
### this is the final list of 500 companies for SDG commitment coding
com500 <- readxl::read_excel(path = paste0(dir.raw, 'UNGSII/Companies in SCR500.xlsx')) %>%
  ## unify the company names
  dplyr::mutate(
    company_name = gsub('Advanced Card Systems', 'Advanced Card Systems Holdings (ACS)', company_name),
    company_name = gsub('Ab Inbev', 'AB Inbev', company_name),
    company_name = gsub('Amazon', 'Amazon.co', company_name),
    company_name = gsub('Delta Corporation \\(Zumbabwe\\)', 'Delta Corporation Limited \\(Zimbabwe\\)',  company_name),
    company_name = gsub('Emirates Airlines', 'Emirates Group', company_name),
    company_name = gsub('Inditex', 'Industria de Diseno Textil', company_name),
    company_name = gsub('Northrop Gruman', 'Northrop Grumman', company_name),
       # company_name = gsub('Sompo Japan Nipponkoa', 'Sompo Holdings', company_name),
    company_name = gsub('Standard Bank Group', 'Standard Bank Group Limited', company_name),
    region = ifelse(company_name=='Emirates Group', 'Asia', region),
    company_name = trimws(company_name),
    region       = trimws(region)
  ) %>% as.data.frame() 


### combine the company list from SCR500 list AND coded data. 
com500_plus <- 
  merge(x = com500, 
        y = com_ls_inData %>% ungroup() %>% dplyr::distinct(Company, Region), 
        by.x = 'company_name', by.y = 'Company', all = T) %>%
  arrange(company_name) %>% ## !is.na(region), 
  dplyr::mutate(
    region = ifelse(company_name == 'Austrian Post', 'Europe', region),
    region = ifelse(company_name == 'Estee Lauder', 'North America',  region),
    region = ifelse(company_name == 'Fluor', 'North America', region),
    region = ifelse(company_name == 'Julius Bär', 'Europe', region),
    region = ifelse(company_name == 'Principal Financial Group', 'North America', region),
    region = ifelse(company_name == 'Prudential Financial', 'North America',  region),
    region = ifelse(company_name == 'Rio Tinto Group', 'Europe',  region),
    region = ifelse(company_name == 'SoftBank Group' ,'Asia',  region),
    region = ifelse(company_name == 'AB Inbev','Europe',  region)
    ) %>%
  arrange(!is.na(region), company_name) %>% 
  as.data.frame()


### --> companies that are not coded in 2017 and 2018 data
com500_notCoded <- com500_plus %>%
  dplyr::filter(is.na(Region))


### --> keep filling the missing info in `region`, by comparing with `Region` column, then remove this column 
com500_plus <- com500_plus %>% dplyr::select(-Region)
```


### * Com final list + Save
```{r}
com_final <- com500_plus %>%
  ## left join with the all companies data table
  left_join(., com700, by = c('company_name'='Company')) %>% 
  dplyr::mutate(
    company_name = gsub('Chiristian Dior', 'Christian Dior', company_name),
    company_name = gsub('Taiwan Semicondctor Manufacturing', 'Taiwan Semiconductor Manufacturing', company_name)) %>% 
  arrange(!is.na(Country), Country)
  


## --> check on data ----------------------------
# sort(unique(com700$Company))
# str(com700)
# str(com_final)
length(unique(com_final$company_name)) # --> 508 companies
unique(com_final$region)               # -->   5 regions

com_final %>% group_by(company_name) %>% tally() %>% dplyr::filter(n > 1)
length(unique(com_final$Country))      # -->  48 countries



## --> save data ---------------------------------
fname <- paste0(dir.results, '/com_final_500_scr.RData'); fname
save(com_final, file = fname)

fname <- paste0(dir.results, '/com_final_500_scr.xlsx')
writexl::write_xlsx(x = com_final, path = fname)
```







## 1.3 Merge 'coded data' and 'com info' 


```

  df1
   |
   |
   v
  df2 -----------
                |               (rename)
                | ---> dfcom ---------------> df
                |
  com700 --------


  com_final (508)

```

```{r}
## bind df.dt and com700
dfcom <- merge(df2, com700, 'Company', all.x = T) %>% 
  arrange(Company, goal) %>%
  dplyr::mutate(
    Company = gsub('Taiwan Semicondctor Manufacturing', 'Taiwan Semiconductor Manufacturing', Company),
    target_id = ifelse(goal_id == 'SDGs'  & is.na(target_id), 'g', target_id),
    target_id = ifelse(goal_id == 'noSDG' & is.na(target_id), 'g', target_id),
    goal_desc = ifelse(goal_id == 'noSDG' & is.na(goal_desc), 'noSDG', goal_desc)
  )

## check NA
dfcom.na <- dfcom %>% dplyr::filter_all(any_vars(is.na(.))) 
df2.na   <- df2   %>% dplyr::filter_all(any_vars(is.na(.))) 
dfcom.na <- dfcom %>% dplyr::select(-target_id) %>%
  dplyr::filter_all(any_vars(is.na(.))) 
print(paste0('There are ', length(unique(dfcom.na$Company)), ' missing data!'))


### rename the final dataset
names(dfcom)
df <- dfcom %>%
  dplyr::select(Company, iso3, goal_id, Target_id, target_id, goal, yr,
                n_statement,
                goal_desc, 
                # Target, SDG, Country,
                ind, Industry, ind_agg, ind_7sys, ind_3,
                Region, Continent) %>%
  arrange(Company, Target_id, yr)
str(df)
```



  * get familiar with the data
```{r}
### how to normalize the data ???
df %>% dplyr::filter(yr == 2018) %>%
  ggplot(aes(x=n_statement)) + 
  geom_histogram(binwidth=2) + 
  ylim(0, 150) +
  theme_bw()

df %>% dplyr::filter(yr == 2018) %>%
  ggplot(aes(y=n_statement)) + 
  geom_boxplot() + 
  ylim(0, 50) + theme_bw()

df %>% dplyr::filter(yr == 2018) %>%
  ggplot(aes(x=n_statement)) + 
  geom_density() + theme_bw()


### find the intervals for classifying the raw data
### jenks - will be very slow; quantile - better
nclass = 10
# classint_jk <- classIntervals(df$n_statement,n=nclass, style= "jenks"); classint_jk
classint_qt <- classIntervals(df$n_statement,n=nclass, style="quantile"); classint_qt
pal <- c("red", "blue") #'yellow', 
plot(classint_qt, pal=pal, main="Quantile")

classint    <- classint_qt
brks <- c(unique(as.integer(classint$brk))); brks
seqs <- seq(1, length(brks)-1); seqs

```



### - data for MS
```{r - Final data}
### the final version of data input for analysis
df <- df %>%
  dplyr::mutate(
    ns = cut(n_statement, breaks = brks, 
             labels = NULL, include.lowest = T, 
             right = F, dig.lab = 3))
unique(df$ns)
unique(df$Company) %>% length()
str(df)

getwd()
fname <- paste0(dir.results, 'df.RData'); fname
save(df, file = fname)
# load(fname)
```



  The world's 500 largest companies generated USD 32.7 trillion *in revenues* and USD 2.15 trillion in profits in 2018. Together, this year's Fortune Global 500 companies employ 69.3 million people worldwide and are represented by 34 countries.
  
  Fortune Global 500 were ranked by **Revenues**. https://fortune.com/global500/2019/

```{r - Check un-coded companies}

## `com_final` --> 508 companies listed by UNGSII
## `df` ---------> 443 coded companies
unique(df$Company) %>% length()


### which companies do not have coded data? --------------------------------------------------------
com_final_naCheck <- 
  merge(x = com_final %>% ungroup() %>% dplyr::select(1:6, iso3),   ## 508       companies
        y = df %>% ungroup() %>% dplyr::select(1:7) %>%             ## 443 coded companies
          dplyr::rename(iso3_2 = iso3) %>% 
          dplyr::distinct(Company, .keep_all = TRUE), 
        by.x = 'company_name', by.y = 'Company', all = T) %>%
  arrange(is.na(goal_id), company_name, iso3, goal_id)


### double check
# ls1 <- com_final$company_name
# ls2 <- com_final_naCheck$company_name
# setdiff(ls1, ls2)
# setdiff(ls2, ls1) ## "Taiwan Semicondctor Manufacturing"


### merge with Fortune-Global500 to get the ranking 
xls <- paste0(dir.raw, '/company_info_Zilong/zilong5_zong_0612/fortune-Global500Companies-(2019).xlsx')
com_g500 <- readxl::read_excel(path = xls) %>% 
  ### fix company names
  dplyr::mutate(
    Name = gsub('Alibaba Group Holding', 'Alibaba', Name),
    Name = gsub('Air France-KLM Group', 'Air France',Name),
    Name = gsub('Airbus', 'Airbus Group',Name),
    Name = gsub('Alphabet', 'Alphabet (Google)',Name),
    Name = gsub('Amazon.com', 'Amazon.co', Name),
    Name = gsub('América Móvil', 'America Movil',Name),
    Name = gsub('Anheuser-Busch InBev', 'Anheuser-Busch (AB InBev)',Name),
    Name = gsub('Banco Bilbao Vizcaya Argentaria', 'Banco Bilbao Vizcaya Argenaria', Name),
    Name = gsub('Bank of America Corp.', 'Bank of America', Name),
    Name = gsub('AEON', 'Aeon', Name),
    Name = gsub('BHP Group', 'BHP Billiton', Name),
    Name = gsub('BMW Group', 'BMW', Name),
    Name = gsub('Costco Wholesale', 'Costco',  Name),
    Name = gsub('Dell Technologies', 'Dell', Name),
    Name = gsub('Deutsche Post DHL Group', 'Deutsche Post',  Name),
    Name = gsub('Dongfeng Motor', 'Dongfeng Motor Group',  Name),
    Name = gsub('Electricité de France', 'Electricite de France',  Name),
    Name = gsub('Formosa Petrochemical', 'Formosa', Name),
    Name = gsub('Goldman Sachs Group', 'Goldman Sachs',  Name),
    Name = gsub('Itaú Unibanco Holding', 'Itau Unibanco Holding', Name),
    Name = gsub('JPMorgan Chase & Co.', 'JP Morgan Chase', Name),
    Name = gsub('Kraft Heinz', 'Kraft-Heinz', Name),
    Name = gsub('Nestlé', 'Nestle', Name),
    Name = gsub('OMV Group', 'OMV AG',  Name),
    Name = gsub('Philip Morris International', 'Philip Morris',  Name),
    Name = gsub('Procter & Gamble', 'Procter& Gamble',  Name),
    # Name = gsub('Prudential Financial', 'Prudential',  Name), ## these two are diferent firms, but `df` do not include 'Prudential'
    Name = gsub('Randstad', 'Randstad Holding',  Name),
    Name = gsub('Samsung Electronics', 'Samsung',  Name),
    Name = gsub('Telefónica', 'Telefonica',  Name),
    Name = gsub('Verizon Communications', 'Verizon',  Name),
    Name = gsub('Westpac Banking', 'Westpac Bank',  Name),
    Name = gsub('Woolworths Group', 'Woolworths',  Name),
    
  ) %>%
  as.data.frame()

com_final_naCheck_LinkG500 <- 
  merge(x = com_final_naCheck,  
        y = com_g500,
        by.x = 'company_name', by.y = 'Name', all = T) %>%
  arrange(#Rank,is.na(goal_id), iso3, 
          company_name, goal_id) %>%
  as.data.frame()


### save to local for inspection 
com_final_naCheckNA <- com_final_naCheck_LinkG500 %>% 
  dplyr::filter(is.na(goal), !is.na(region)) %>%
  dplyr::select(1:4, Rank, country) %>%
  dplyr::rename(Rank_Fortune = Rank)
writexl::write_xlsx(x = com_final_naCheckNA, path = paste0(dir.raw, '/com_final_naCheckNA_2017_2018.xlsx'))
```




```{r - Data for Text mining}

fname <- paste0(dir.results, 'df.RData'); fname
load(fname)


comp_name <- 'Cemex'
df_x <- df %>%
  dplyr::filter(Company %in% c(comp_name))


comp_name <- 'Apple'
df_x <- df %>%
  dplyr::filter(Company %in% c(comp_name))


comp_name <- 'Pfizer'
df_x <- df %>%
  dplyr::filter(Company %in% c(comp_name))


### save to local, and compare to the text mining approach 
writexl::write_xlsx(x = df_x, path = paste0('./Data/data_TextMining/df_', comp_name, '_reference.xlsx'))

### report pdf: 
### - https://investor.apple.com/investor-relations/default.aspx#tabs_content--2019
### - https://s2.q4cdn.com/470004039/files/doc_financials/2018/q4/10-K-2018-(As-Filed).pdf

```




```{r - Number for MS}
### To look at the details for MS writing
d1 <- df1.2 %>% dplyr::filter(Target_id == '3_c') %>% 
  left_join(., com700, 'Company') 

d2 <- df1.2 %>% dplyr::filter(Target_id == '16_6') %>% 
  left_join(., com700, 'Company') 
```





## 1.4 Shapefile data
```{r}

library(rnaturalearthdata)
library(rnaturalearth)
library(sf)
shp <- ne_countries(scale = 'medium', type = 'countries', returnclass = 'sf') %>%
  dplyr::select(name, type, iso_a3, economy, income_grp) %>%
  dplyr::mutate(
    iso_a3 = ifelse(name == 'Norway', 'NOR', iso_a3),
    iso_a3 = ifelse(name == 'N. Cyprus', 'CYP', iso_a3),
    iso_a3 = ifelse(name == 'France', 'FRA', iso_a3))
# plot(shp['iso_a3'])
shp_iso_na <- shp %>% 
  st_drop_geometry() %>%
  dplyr::filter(is.na(iso_a3))


### group info from the shp data
sort(unique(shp$economy))
sort(unique(shp$income_grp))

grp <- shp %>% 
  st_drop_geometry() %>% 
  ### re-code ctr group
  mutate(eco_group = case_when(
    str_detect(economy, "Developed") ~ "1. Developed",
    str_detect(economy, "Emerging")  ~ "2. Developing",
    str_detect(economy, "eveloping|Least") ~ "2. Developing",
    TRUE ~ .$economy
  ))  %>% 
  ### re-code income group
  mutate(inc_group = case_when(
    str_detect(income_grp, "High")  ~ "1. High income",
    str_detect(income_grp, "Upper") ~ "2. Upper middle income",
    str_detect(income_grp, "Lower") ~ "3. Lower middle income",
    str_detect(income_grp, "Low income") ~ "4. Low income",
    TRUE ~ .$income_grp
  )) %>%
  arrange(!is.na(iso_a3)) %>% ### check missing info and fill the data gap
  dplyr::mutate(iso_a3 = ifelse(name == 'Norway', 'NOR', iso_a3))


### save 
fname <- paste0(dir.results, 'grp.RData'); fname
save(grp, shp, file = fname)

```




```
# 2. Data summary

```

