---
title: "Untitled"
author: "Yingjie"
date: "3/26/2020"
output:
  word_document: default
  pdf_document: default
  html_document: default
editor_options: 
  chunk_output_type: inline
---


# Dirs and packages
```{r include=FALSE}
## To clear your environment
remove(list = ls())

## load work dir
source('./Code/_directories.R')

source('./Code/_packages.R')

```




#  1.  Data

## 1.1 SDG coded data cleaning


```

(318)       (356)
`df17`      `df18`
    \        /
     \      /
      \    /
      `df0` (443)
        |
        |
        |
        |
        V
  (goal level)
      `df1` (443)                              `com_inData`
        |                                           ^
        |                                           |
        v                                           |
      `df2` -----------                             |
  (target level)      |               (rename)      |
                      |------->`dfcom` ----------> `df` (443 company, with both 2017 and 2018)
                      |                             ^
    `com700` ----------                             |
  (with com info)                                   |
                                                    | (to check which companies were not coded)
                                                    |
                                                    |
                                                `com_final` 
                                                  (508)

```

### - Goal level data (df1)

```{r include=FALSE}

## main data read in
getwd()
xls   <- paste0(dir.raw, 'UNGSII/Yingjie_data_02242020_YL.xlsx'); xls
excel_sheets(xls)

sheet   <- '2017 detailed data'; 
data_yr <- as.numeric(gsub("\\D", "", sheet)); data_yr
df17    <- readxl::read_excel(path = xls, sheet = sheet) %>% 
  dplyr::mutate(yr = data_yr) %>%
  as.data.frame()

sheet   <- '2018 detailed data'; 
data_yr <- as.numeric(gsub("\\D", "", sheet)); data_yr
df18    <- readxl::read_excel(path = xls, sheet = sheet) %>% 
  dplyr::mutate(yr = data_yr) %>%
  as.data.frame()

df0     <- rbind(df17, df18) %>%
  dplyr::mutate(
    Company = gsub('Chiristian Dior', 'Christian Dior', Company),
    Company = gsub('AB Inbev', 'AB InBev', Company),
    Company = gsub('US Foods Holing', 'US Foods Holding', Company)
  )
  


## data cleaning - goal level --------------------------------------------------
names(df0)
str(df0)
names(df0) <- c("Company", "Region", "Target", "SDG", 'n_statement', 'yr')
# unique(df0$Target)
unique(df0$SDG)

n_sdg    <- length(unique(df0$SDG)) -2; n_sdg
n_target <- length(unique(df0$Target)); n_target
print(paste0('There are total ', n_sdg,    ' goals.'))
print(paste0('There are total ', n_target, ' SDG targets.'))


### split the goal id and description into 2 cols
# df_splt <- colsplit(df0$SDG, pattern = ' ', c('goal', 'goal_desc'))
# df1 <- cbind(df0, df_splt) 

df1 <- separate(data = df0, col = SDG, sep = " ", remove = F,
                extra = 'merge',
                into = c('goal', 'goal_desc')) %>%
  # dplyr::mutate(Target = gsub('\\(', '', Target),
  #               Target = gsub('\\)', '', Target)) %>%
  # dplyr::mutate(Target = trimws(Target)) %>%
  as.data.frame()


sort(unique(df1$goal))
df1$goal <- factor(df1$goal, levels = c(paste0('SDG', seq(1, 17)), 'SDG', 'noSDG'))
levels(df1$goal)
```



### - Target level data (df2)

  Since there is no Target ID in the raw dataset. The author manfully coded the target ID based on the description from UN's SDG indicator list, and then left join the coded target ID to the raw dataset.
  
  This target list includes unique values from both 2017 and 2018 data. 
  
```{r}
### Tidy target and add numbered ID --------------------------------------------
ls_target_df1 <- df1 %>% distinct(SDG, Target) %>% arrange(SDG, Target)

fname <- './Data/data_raw/_ls_goal_target.xlsx'; fname
writexl::write_xlsx(x = ls_target_df1, path = fname)


### --> read in manually matched target list 
ls_target <- readxl::read_xlsx(path = './Data/data_raw/_ls_goal_target_manualTidy.xlsx', sheet = 1) %>%
  dplyr::select(Target_id, Target) %>%
  dplyr::distinct(Target_id, Target, .keep_all = T) %>%
  # dplyr::mutate(Target = gsub('\\(', '', Target),
  #               Target = gsub('\\)', '', Target)) %>%
  # dplyr::mutate(Target = trimws(Target)) %>%
  separate(col = Target_id, into = c('goal_id', 'target_id'), sep = '\\_', remove = F) %>%
  as.data.frame()

str(ls_target)



### Match UNGSII's target name with UN's ----------------------------------------
### --> UN Goal and Target list 
ls_un <- read.csv('./Data/data_raw/_ls_un_goal_target.csv', stringsAsFactors = F) %>%
  dplyr::filter(!is.na(GoalID)) %>%
  tidyr::separate(Targets, c('target_id_un', 'target_desc_un'), 
           sep = ' ', extra = 'merge', remove = T)
str(ls_un)
ls_un_id <- ls_un %>%
  dplyr::select(GoalID, target_id_un) %>%
  separate(target_id_un, c('target_id_un1', 'target_id_un2'), 
           sep = '\\.', remove = F) %>%
  dplyr::select(-target_id_un1) %>%
  dplyr::mutate(goalname = paste0('SDG', GoalID))
str(ls_un_id)
ls_un_id$goalname <- factor(x = ls_un_id$goalname, levels = unique(ls_un_id$goalname))


### --> merge the two lists 
names(df1)
str(df1)
df1.2 <- merge(x = df1, y = ls_target, by.x = 'Target', by.y = 'Target', all.x = T) %>%
  ungroup() %>%
  arrange(!is.na(Target_id), goal, Target_id) #%>%
  ### check on any duplicated records as I re-coded Target to Target_id
  # dplyr::count(Company, Target_id) %>%




### --> unique target description in the original raw data set, & new coded data -------------------
target_desc_raw <- df1.2 %>% 
  dplyr::select(#Company, goal, 
                Target_id, Target) %>%
  distinct(Target, .keep_all = T)

target_desc_new <- df1.2 %>% 
  dplyr::select(#Company, goal, 
                Target_id, Target) %>%
  distinct(Target_id, .keep_all = T)


### --> Use new coded target ID (`Target_id`) for the final `level 2 data` -------------------------
###     Because I further coded the target ids (i.e., 'Target_id') based on the raw data (i.e., 'Target'), it is necessary to summarize the data and keep unique 'Target_id' and 'n_statement'. 
names(df1.2)

df2 <- df1.2 %>%
  ungroup() %>%
  dplyr::group_by(Company, Region, 
                  Target,  ## this has been re-coded
                  SDG, 
                  # n_statement,
                  goal, goal_desc, Target_id, goal_id, target_id, yr) %>%
  dplyr::summarise(n_statement = sum(n_statement, na.rm = T)) %>%
  ## correct company names
  dplyr::mutate(Company = gsub('Northrop Gruman', 'Northrop Grumman', Company)) %>%
  # mutate(id = seq.int(nrow(.))) %>%
  arrange(yr, goal, Target_id)


# unique(df2$n)
names(df2)
unique(df2$goal)


### --> to check if any not matched rows, then add to the manual coding xls - "_ls_goal_target_manualTidy.xlsx"
df2_na <- df2 %>% dplyr::filter(is.na(Target_id)); df2_na
# writexl::write_xlsx(x = df2_na, path = './data_raw/_ls_goal_target_na_notMatch.xlsx')

hist(df2$n_statement)
# boxplot(df2$n_statement)
length(unique(df2$Company))
```


  *Note: * The coded data for 2018 is very different from the data for 2017. 
  
  As a result, we can **NOT** use 2017 data to supplement 2018. 

```{r - compare 2017 vs 2018}

df2yr <- df2 %>%
  ungroup() %>%
  dplyr::select(Company, yr, goal, Target_id, n_statement) %>%
  group_by(Company, yr, 
           # Target_id, 
           goal) %>%
  dplyr::summarise(n = sum(n_statement, na.rm = T)) %>%
  tidyr::spread(key = yr, value = n) %>%
  as.data.frame()


## remove rows with NA and compare
df2yr1 <- df2yr %>%
  drop_na()
df2yr1 %>%
  # ggplot(aes(x = `2018`, y = `2017`, color = goal)) +
  ggplot(aes(x = log(`2018`), y = log(`2017`), color = goal)) +
  geom_point() +
  geom_smooth(formula = y~x, method = 'lm') +
  geom_abline(linetype = "dashed") +
  theme_bw()
  


### company list in the coded data (356) -----------------------------------------------------------
com_df2_byYear <- df2 %>%
  ungroup() %>%
  dplyr::select(Company, yr, n_statement) %>%
  group_by(yr, Company) %>%
  dplyr::summarise(n = sum(n_statement, na.rm = T)/17) %>%
  as.data.frame()

## data in wide format
com_df2_byYear_w <- com_df2_byYear %>%
  spread(key = yr, value = n) %>%
  as.data.frame()

## plot to compare the difference
com_df2_byYear_w %>%
  drop_na() %>%
  ggplot(aes(x = `2018`, y = `2017`)) +
  # ggplot(aes(x = log(`2018`), y = log(`2017`))) +
  geom_point() +
  geom_smooth(formula = y~x, method = 'lm') +
  geom_abline(linetype = "dashed") +
  theme_bw()

```


```{r - Number for MS}
### To look at the details for MS writing
d1 <- df1.2 %>% dplyr::filter(Target_id == '3_c') %>% 
  left_join(., com700, 'Company') 

d2 <- df1.2 %>% dplyr::filter(Target_id == '16_6') %>% 
  left_join(., com700, 'Company') 
```


### - Save data

```{r include=FALSE}

## save as RData
fname <- paste0(dir.results, 'df1_df2.RData'); fname
save(df1, df2, file = fname)
save(ls_un_id, file = paste0(dir.results, 'ls_un_id.RData'))


## or save as XLSX
fname <- paste0(dir.results, 'df1.xlsx'); fname
writexl::write_xlsx(df1, path = fname)
fname <- paste0(dir.results, 'df2.xlsx'); fname
writexl::write_xlsx(df2, path = fname)
```

