---
title: "Company info"
author: "Yingjie Li"
date: "6/11/2020"
output: html_document
editor_options: 
  chunk_output_type: inline
---



# Dirs and packages
```{r include=FALSE}
### To clear your environment 
remove(list = ls())

## load work dir
source('./Code/_directories.R')

source('./Code/_packages.R')
source('./Code/helper_theme_NS_map.R')


version <- '_R1'
```




# 1. Company info from UNGSII


  In addition to the company names in the *coded data*, there are `two` other data sets that include more detailed company information. 
  
  Here, we need to use the other two to enrich the company info we have in the coded data. 
  
```
Yingjie_Companies_190930_updateYL.xlsx
          |
          v
         com1  -->  com2  -----------------> `com700`
                                                 |
                                                 |
                                                 |
Companies in SCR500.xlsx                         |
          |                                      |
          v                                      |
      `com500`-----------------------            |
                                    |            v
                                    |------> `com500_plus` ------> `com_final`
                                    |                                 (508)
      `com_ls_inData` ---------------
          ^
          |
  (companies in the coded data)
```




### * Company info - in data
```{r}
fname <- paste0(dir.results, 'df1_df2.RData'); fname
load(fname)

## company list for (2017 + 2018) data: 443 unique ---------------------------------------
com_ls_inData <- df2 %>%
  ungroup() %>%
  group_by(yr) %>%
  dplyr::distinct(Company, Region) %>%
  arrange(desc(yr)) 

com_ls_inData_unique <- com_ls_inData %>%
  ungroup() %>%
  distinct(Company, Region, .keep_all = T)

com_ls_inData_unique %>% group_by(yr) %>% tally()


## company list for 2018 data: 356 -------------------------------------------------------
com_ls_2018 <- com_ls_inData %>%
  dplyr::filter(yr == 2018) %>%
  arrange(Company) %>%
  as.data.frame()

## company list for 2017 data: 318 -------------------------------------------------------
com_ls_2017 <- com_ls_inData %>%
  dplyr::filter(yr == 2017) %>%
  as.data.frame()


## any difference? -----------------------------------------------------------------------
# if (!require(devtools)) install.packages("devtools")
# devtools::install_github("yanlinlin82/ggvenn")
library(ggvenn)

com_2018 = com_ls_2018$Company
com_2017 = com_ls_2017$Company

x <- list(com_2018 = com_ls_2018$Company,
          com_2017 = com_ls_2017$Company)
ggvenn(
  x, 
  fill_color = c("#0073C2FF", "#EFC000FF"), #show_elements = T, 
  stroke_size = 0.5, set_name_size = 4
)


# setdiff(com_2018, com_2017)

cat('The list in 2017 but not in 2018\n')
setdiff(com_2017, com_2018) %>% sort()
```


## * Company info - 700+

```{r}
## company info
xls <- paste0(dir.raw, 'UNGSII/', 'Yingjie_Companies_190930_updateYL.xlsx')
excel_sheets(xls)
sheet <- "Companies"
df.co <- readxl::read_excel(path = xls, sheet = sheet) 
names(df.co)
# head(df.co,2)

### cleaning data --------------------------------------------------------------
names(df.co) <- c("Company", 'Industry', 'Industry2', 
                  "Country", 'Continent', 
                  "Location",  "name_specifc", "ISIN")


df.co <- df.co %>% ## create a new name col for the country
  as.data.frame() %>%
  mutate(Country = gsub(' in general', '', Country)) %>%
  dplyr::select(-c(Industry2, Location))

### detect rows containing NA values in any column 
df.co %>% 
  filter_all(any_vars(is.na(.))) 

n.industry <- unique(df.co$Industry); #n.industry
print(paste0('There are total ', length(n.industry), ' industries.'))


## data
com1 <- df.co
```


### Industry info

```{r - number of countries by industry}

ls_industry <- df.co %>%
  group_by(Industry) %>% tally() %>% arrange(n)
## write to local and tidy this list
# writexl::write_xlsx(x = ls_industry, path = './data_raw/_ls_industry.xlsx')


### read in again after cleaning up Industry info ----------------------------
f <- paste0(dir.raw, '_ls_industry_manualTidy.xlsx')
df.industry <- readxl::read_excel(path = f) %>%
  dplyr::mutate(ind_agg = str_to_sentence(ind_agg),
                ind_7sys= str_to_sentence(ind_7sys))
# unique(df.industry$ind_agg)



df.co2 <- merge(df.co, df.industry, by = 'Industry', all.x = T)

print(paste0('There are total ', length(unique(df.co2$ind_agg)), ' industries.'))
```


```{r}
df.co2 %>%
  group_by(ind_agg) %>% tally() %>% arrange(n) %>%
  ggplot() +
  geom_col(aes(x= reorder(ind_agg, n), y = n)) +
  coord_flip() + theme_bw()

```






**Update on industry classification**

f <- '_ls_industry_manualTidy.xlsx'    ## 
f <- '_ls_industry_manualTidy_R1.xlsx' ## revised classification on 6/11/2022


```{r eval=FALSE, include=FALSE}

### change to factor and add levels
unique(df.industry$ind_7sys)

ind_levels <- c(
  "Energy, natural resources, and basic materials", ## primary
  "Industrial manufacturing",                       ## secondary
  "Mobility and transportation",
  "Healthcare and life sciences",                   ## Tertiary
  "Telecommunications and technology",
  "Financial services",
  "Food, beverage, and consumer goods",             ## Quaternary         
  "Media & entertainment"
)


## --> shorten the names for label use
ind_labels <- c(
  'Resources and materials',
  'Industrial manufacturing',
  'Mobility and transportation',
  'Healthcare',
  'IT and Telecommunications',
  'Financial services',
  'Food and consumer goods',
  'Media & entertainment'
)
```


```{r include=FALSE}
f <- '_ls_industry_manualTidy_R1.xlsx' ## revised classification on 6/11/2022
df.industry <- 
  readxl::read_excel(path = paste0(dir.raw, f)) %>%
  # dplyr::select(Industry, ind) %>%
  dplyr::mutate(ind_agg = str_to_sentence(ind_agg),
                ind_7sys= str_to_sentence(ind_7sys))


### change to factor and add levels
unique(df.industry$ind_7sys) ## now with 13 classes, not 7

ind_levels <- c(
  "Energy", 
  "Basic materials",                                ## primary
  "Industrial manufacturing",                       ## secondary
  "Mobility and transportation",
  "Health care",                                    ## Tertiary
  "Telecommunications and technology",
  "Financial services",
  "Food, beverage & tobacco",             ## Quaternary   
  "Consumer products and services", 
  "Media & entertainment",
  "Automobiles and parts",
  "Insurance",
  "Retail"
)


## --> shorten the names for label use
ind_labels <- c(
  "Energy", 
  "Basic materials",
  'Industrial manufacturing',
  'Mobility and transportation',
  'Health care',
  'IT and Telecommunications',
  'Financial services',
  'Food, beverage & tobacco',
  "Consumer products & services", 
  "Media & entertainment",
  "Automobiles and parts",
  "Insurance",
  "Retail"
)


df.industry <- df.industry  %>%
  dplyr::mutate(
    ## choose one classification sys for analysis
    ind_7sys = factor(ind_7sys, levels = ind_levels), # , labels = ind_labels
    ind = ind_7sys) %>%
  dplyr::select(-n, -id)


### --> add the updated industry info to the company dataframe
com2 <- merge(com1, df.industry, by = 'Industry', all.x = T)
str(com2)

```




### Country name data

```{r include=FALSE}
names(com2)
head(com2, 2)

### save the nation info to local to coding the ISO3
### 52 countries
df.ctr <- com2 %>% dplyr::select(Continent, Country) %>%
  distinct(Country, .keep_all = T) %>%
  arrange(Country) 
writexl::write_xlsx(x=df.ctr, path = paste0(dir.raw, '_country_info_raw.xlsx'))

df.ctr.test <- com2 %>% dplyr::filter(Country=='South Africa (Rep.)')
## change one row using "South Africa" to "South Africa (Rep.)". Raw data error. 


### read in the updated and manually coded country info
ctr <- readxl::read_excel(path = paste0(dir.raw, '_country_info_raw_iso3.xlsx'), 
                          range = 'B1:C100') %>%
  filter(!is.na(Country))

com700 <- com2 %>%
  merge(., ctr, 'Country', all.x = T) %>%
  dplyr::mutate(
    Company = gsub('Northrop Gruman', 'Northrop Grumman', Company),
    Company = gsub('Anheuser-Busch \\(AB InBev\\)', 'AB InBev', Company),
    Company = gsub('Chiristian Dior', 'Christian Dior', Company),
    Company = gsub('US Foods Holing', 'US Foods Holding', Company),
    Company = gsub('Flextronics International', 'Flex', Company),
    Company = trimws(Company),
    Continent = ifelse(Company =='Emirates Group', 'Asia', Continent),
                )
str(com700)

## save data
f <- paste0(dir.results, 'com700.rds')
saveRDS(object = com700, file = f)
```


## * Company info - 500 +

```{r}
### this is the final list of 500 companies for SDG commitment coding
com500 <- readxl::read_excel(path = paste0(dir.raw, 'UNGSII/Companies in SCR500.xlsx')) %>%
  ## unify the company names
  dplyr::mutate(
    company_name = gsub('Advanced Card Systems', 'Advanced Card Systems Holdings (ACS)', company_name),
    company_name = gsub('Ab Inbev', 'AB InBev', company_name),
    company_name = gsub('Amazon', 'Amazon.co', company_name),
    company_name = gsub('Chiristian Dior', 'Christian Dior', company_name),
    company_name = gsub('Delta Corporation \\(Zumbabwe\\)', 'Delta Corporation Limited \\(Zimbabwe\\)',  company_name),
    company_name = gsub('Emirates Airlines', 'Emirates Group', company_name),
    company_name = gsub('Flextronics International', 'Flex', company_name),
    company_name = gsub('Inditex', 'Industria de Diseno Textil', company_name),
    company_name = gsub('Northrop Gruman', 'Northrop Grumman', company_name),
    company_name = gsub('US Foods Holing', 'US Foods Holding', company_name),
       # company_name = gsub('Sompo Japan Nipponkoa', 'Sompo Holdings', company_name),
    company_name = gsub('Standard Bank Group', 'Standard Bank Group Limited', company_name),
    region = ifelse(company_name=='Emirates Group', 'Asia', region),
    company_name = trimws(company_name),
    region       = trimws(region)
  ) %>% as.data.frame() 


### combine the company list from SCR500 list AND coded data. 
com500_plus <- 
  merge(x = com500, 
        y = com_ls_inData %>% ungroup() %>% dplyr::distinct(Company, Region), 
        by.x = 'company_name', by.y = 'Company', all = T) %>%
  arrange(company_name) %>% ## !is.na(region), 
  dplyr::mutate(
    region = ifelse(company_name == 'Austrian Post', 'Europe', region),
    region = ifelse(company_name == 'Estee Lauder', 'North America',  region),
    region = ifelse(company_name == 'Fluor', 'North America', region),
    region = ifelse(company_name == 'Julius Bär', 'Europe', region),
    region = ifelse(company_name == 'Principal Financial Group', 'North America', region),
    region = ifelse(company_name == 'Prudential Financial', 'North America',  region),
    region = ifelse(company_name == 'Rio Tinto Group', 'Europe',  region),
    region = ifelse(company_name == 'SoftBank Group' ,'Asia',  region),
    region = ifelse(company_name == 'AB Inbev','Europe',  region)
    ) %>%
  arrange(!is.na(region), company_name) %>% 
  as.data.frame()


### --> companies that are not coded in 2017 and 2018 data
com500_notCoded <- com500_plus %>%
  dplyr::filter(is.na(Region))


### --> keep filling the missing info in `region`, by comparing with `Region` column, then remove this column 
com500_plus <- com500_plus %>% dplyr::select(-Region)
```


## * Com final list + Save
```{r}
com_final <- com500_plus %>%
  ## left join with the all companies data table
  left_join(., com700, by = c('company_name'='Company')) %>% 
  dplyr::mutate(
    # company_name = gsub('Chiristian Dior', 'Christian Dior', company_name),
    company_name = gsub('Taiwan Semicondctor Manufacturing', 'Taiwan Semiconductor Manufacturing', company_name)) %>% 
  arrange(!is.na(Country), Country)
  


## --> check on data ----------------------------
# sort(unique(com700$Company))
# str(com700)
# str(com_final)
length(unique(com_final$company_name)) # --> 508 companies
unique(com_final$region)               # -->   5 regions

com_final %>% group_by(company_name) %>% tally() %>% dplyr::filter(n > 1)
length(unique(com_final$Country))      # -->  48 countries



## --> save data ---------------------------------
fname <- paste0(dir.results, 'com_final_500_scr.RData'); 
save(com_final, com700, ctr, ind_levels, ind_labels, file = fname)


fname <- paste0(dir.results, 'com_final_UNGSII.rds'); 
saveRDS(com_final, file = fname)


fname <- paste0(dir.results, 'com_final_500_scr.xlsx')
writexl::write_xlsx(x = com_final, path = fname)

```


#  2. Other datasets

## 2.1 Company info by Zilong

```{r}
### read data from zilong (zl)
xls <- paste0(dir.raw, '/company_info_Zilong/zilong5_zhenghe_0612.xls')
excel_sheets(xls)
sheet <- "Companies"
zl <- readxl::read_excel(path = xls, sheet = sheet) %>% as.data.frame()
nm <- names(zl)
# sort(nm)
# str(zl)

## new name for the cols
nm_new <- nm %>% 
  str_to_lower(.) %>%
  gsub(' |\\-|\\(|\\)', '_', .) %>% ## special strings
  gsub('\\__', '_', .) %>%          ## double underline to single 
  gsub('\\_$', '', .) %>%           ## remove the underline at the end of the string
  gsub('number_of_|\\\n|companies|as_of_3/29/19_', '', .) %>%
  gsub('lndustry', 'industry', .) %>%
  gsub('revenues', 'revenue', .) %>%
  gsub('total_assets\t', 'assets', .) %>%
  gsub('employees', 'employee', .) %>%
  gsub('profits', 'profit', .) %>%
  gsub('headquarters', 'headquarter', .) %>%
  gsub('assets', 'asset', .) %>%
  gsub('net_income', 'income_net', .) %>%
  gsub('operating_income', 'income_operating', .) %>%
  gsub('introduction_fortune', 'website_fortune_intro', .) %>%
  gsub('fortune_global1000', 'fortune_us1000', .) %>%
  gsub('\\$m', '\\_musd', .) %>%  ## million USD
  gsub('\\__', '_', .) %>%        ## double underline to single     
  # sort() %>% 
  str_to_lower(.)
# nm_new
# sort(nm_new)

### rename the df
names(zl) <- nm_new

### by data source
str_subset(string = nm_new, pattern = 'fortune') 
str_subset(string = nm_new, pattern = 'forbes') %>% sort()
str_subset(string = nm_new, pattern = 'wiki') 

### by col info
str_subset(string = nm_new, pattern = 'country')
str_subset(string = nm_new, pattern = 'headquarter') ## no forbes global 2000?
str_subset(string = nm_new, pattern = 'industry')
str_subset(string = nm_new, pattern = 'sector')
str_subset(string = nm_new, pattern = 'profit')
str_subset(string = nm_new, pattern = 'employee')

### separate kaggle's HQ info and left_join to the main data
country_kaggle <- zl %>% 
  dplyr::distinct(id, headquarter_kaggle)

country_kaggle <- data.frame(
  country_kaggle, do.call(rbind, str_split(country_kaggle$headquarter_kaggle,','))) %>%
  select(-headquarter_kaggle)
names(country_kaggle) <- c("id",
                           paste0(c("city", "state", 'country'), "_kaggle"))

zl <- zl %>% left_join(., country_kaggle, by = 'id') %>%
  mutate_if(is.factor, as.character)


### add info from the raw data
com_raw <- df.co2 %>%
  mutate(id = row_number())
# names(com_raw)

com_all <- com_raw %>% 
  left_join(., zl, by= 'id')

# names(com_all)
# str(com_all)


```


### - data cleaning by column
```{r}
### country info ---------------------------------------------------------------
country <- com_all %>% 
  select(matches(match = 'id|name|countr|city|headquarters|tude', ignore.case = T)) %>%
  select(matches(match = 'id|name|countr', ignore.case = T)) %>%
  dplyr::mutate(
    country = ifelse(
      ### decide the info choice based on data quality: Forbes, Fortune, Kaggle
      country_forbes_global2000_2020 != 'NA', country_forbes_global2000_2020, 
      ifelse(
        country_fortune_global500_2019 != 'NA', country_fortune_global500_2019, 
        ifelse(
          country_forbes_global2000_2019 != 'NA', country_forbes_global2000_2019, 
          ifelse(
            country_kaggle != 'NA', country_kaggle, NA
          )
        ))
      ),
    country = trimws(country),
    country = gsub('\\.', '', country),
    country = gsub('US', 'United States', country),
    country = str_to_title(country),
    ) %>%
  select(id, name, country, Country)
  
names(country)


### Industry  ------------------------------------------------------------------
industry <- com_all %>% as.data.frame() %>%
  dplyr::select(matches(match = 'id|name|industry|sector', ignore.case = T)) %>%
  dplyr::mutate(
    industry = ifelse(
      industry_forbes_global2000_2020 != 'NA', industry_forbes_global2000_2020, 
      ifelse(
        industry_fortune_global500_2019 != 'NA', industry_fortune_global500_2019, 
        ifelse(
          industry_wiki != 'NA', industry_wiki, 
          ifelse(
            industry_kaggle != 'NA', industry_kaggle, 
            ifelse(
              industry_fortune_us1000_2018 != 'NA', industry_fortune_us1000_2018,
              ifelse(
                industry_forbes_global2000_2019 != 'NA', industry_forbes_global2000_2019, NA
              )
              ))
          ))
      )) %>%
  dplyr::select(id, name, industry, Industry)

names(industry)


### Revenue/profits  -----------------------------------------------------------
###   may choose profit for use.
# profit = net income
profit <- com_all %>% as.data.frame() %>%
  dplyr::select(matches(match = 'id|name|revenue|profit|income', ignore.case = T)) %>%
  dplyr::mutate(
    profit = ifelse(
      profit_musd_forbes_global2000_2020 != 'NA', profit_musd_forbes_global2000_2020, 
      ifelse(
        profit_musd_fortune_global500_2019 != 'NA', profit_musd_fortune_global500_2019,
        ifelse(
          profit_musd_fortune_us1000_us_2019 != 'NA', profit_musd_fortune_us1000_us_2019,
          ifelse(
            profit_musd_forbes_global2000_2019 != 'NA', profit_musd_forbes_global2000_2019,
            ifelse(
              profit_musd_fortune_us1000_2018 != 'NA', profit_musd_fortune_us1000_2018, NA
            )
          )
          )))) %>%
  dplyr::mutate(profit = as.numeric(profit)) %>%
  dplyr::arrange(!is.na(profit), profit)
  
sort(names(profit))
# str(profit)



### Assets ---------------------------------------------------------------------
asset <- com_all %>% 
  dplyr::select(matches(match = 'id|name|asset', ignore.case = T)) %>%
  dplyr::mutate(
    asset = ifelse(
      asset_musd_forbes_global2000_2019 != 'NA', asset_musd_forbes_global2000_2019, 
      ifelse(
        asset_musd_fortune_global500_2019 != 'NA', asset_musd_fortune_global500_2019, 
        ifelse(
          asset_musd_fortune_us1000_us_2019 != 'NA', asset_musd_fortune_us1000_us_2019,
          ifelse(
            asset_musd_fortune_us1000_2018 != 'NA', asset_musd_fortune_us1000_2018,
            ifelse(
              asset_musd_forbes_global2000_2020 != 'NA', asset_musd_forbes_global2000_2020,
              NA
              # ifelse(
              #   asset_wiki != 'NA', asset_wiki, NA
              # )
            )
          )
        ))
      ),
    asset = as.numeric(asset)
    ) %>%
  dplyr::select(id, name, asset, asset_wiki) %>%
  dplyr::arrange(!is.na(asset), asset)

names(asset)
# str(asset)


### Employees ------------------------------------------------------------------
employee <- com_all %>% as.data.frame() %>%
  dplyr::select(matches(match = 'id|name|employee', ignore.case = T)) %>%
  dplyr::mutate(
    employee_wiki_num   = as.numeric(gsub("\\D", "", employee_wiki)),
    employee_kaggle_num = as.numeric(gsub("\\D", "", employee_kaggle)),
    employee_kaggle_num = ifelse(employee_kaggle_num > 10, employee_kaggle, NA)) %>%
  as.data.frame() %>%
  dplyr::mutate(
    # small number might be wrong for kaggle data
    employee = ifelse(
      employee_forbes_global2000_2019 != 'NA', employee_forbes_global2000_2019,
      ifelse(
        employee_fortune_global500_2019 != 'NA', employee_fortune_global500_2019,
        ifelse(
          employee_fortune_us1000_us_2019 != 'NA', employee_fortune_us1000_us_2019,
          ifelse(
            employee_fortune_us1000_2018 != 'NA', employee_fortune_us1000_2018,
            ifelse(
              employee_forbes_global2000_2020 != 'NA', employee_forbes_global2000_2020,
              ifelse(
                !is.na(employee_wiki_num), employee_wiki_num,
                ifelse(
                  !is.na(employee_kaggle_num), employee_kaggle_num, NA)))))))) %>%
  dplyr::mutate(employee = as.numeric(employee)) %>%
  dplyr::arrange(!is.na(employee), employee)

sort(names(employee))
# str(employee)
# unique(employee$employee)

```




### * geo-coding lat/lon
  1. using info from https://www.forbes.com/global2000/; e.g., Walmart
      - Country/Territory: United States
      - Headquarters:      Bentonville, Arkansas
      
  2. Then, fill data gap for those  that are not included in www.forbes.com
    (1) forbes global2000 (in 2019, I saw you have this data)
    
    (2) https://fortune.com/global500/2020/; e.g., Walmart
      - Country: U.S.
      - Headquarters: Bentonville, Ark. (city, state)
      
    (3) https://fortune.com/global500/2019/; e.g., Walmart
      - HQ Location: Bentonville, Ark. (city, state)
      - (NO Country INFO, SAME AS 2018)
      
    (4) https://en.wikipedia.org/wiki/Walmart (an example)
      - Headquarters:	Bentonville, Arkansas, U.S.
      
  3. Geo-coding and generate lat/lon info for mapping

#### - data cleaning
```{r}
getwd()
xls <- paste0(dir.raw, 'company_info_Zilong/geo_location_coms/geo_location_en_v0906.xlsx')
excel_sheets(xls)
geodf <- readxl::read_excel(path = xls, sheet = 1) %>%
  dplyr::select(ID:lat)
# names(geodf)
# head(geodf,2)

### load the final 500 com list - "com_final"
load('./Data/data_results/com_final_500_scr.RData')
com_final_ctr <- com_final %>%
  dplyr::select(company_name:Country)
geodf500 <- geodf %>%
  ### link with the company info provided by UNGSII, and double-check on the location info (country location)
  merge(x = ., y = com_final, by.x = 'name', by.y = 'company_name', all.y = T)
str(geodf500)

### by manually check the data, we need to revise some of the info
xls <- paste0(dir.raw, 'company_info_Zilong/geo_location_coms/geo_location_en_need_revision_done.xlsx')
geosi <- readxl::read_excel(path = xls, sheet = 1) %>%
  dplyr::select(ID:lat, -ID) 
com_list_to_update  <- unique(geosi$name);  com_list_to_update ### get the list that needs to be updated
### subset the ones that need to be updated
geodf_to_update0 <- geodf500 %>% 
  dplyr::filter(name %in% com_list_to_update | is.na(lat)) %>%
  dplyr::select(name:lat, -ID)
### subset the ones that are correct
geodf_to_update1 <- geodf500 %>% 
  dplyr::filter(!name %in% com_list_to_update & !is.na(lat)) %>%
  dplyr::select(name:lat, -ID)
### update the geo-location df by combining the correct ones and updated ones
geodf500_update <- rbind(geodf_to_update1, geosi) %>%
  distinct(name, .keep_all = T) %>%
  # merge(x = ., y = com_final, by.x = 'name', by.y = 'company_name', all = T) %>%
  arrange(name)

### check if there are missing companies from the SDG coding data (that not included in the 500 list)
### load the average commitments and evenness at company level
load(paste0(dir.results, 'com_cmt_evenness_all.RData'))
### link with the geo-location data
geo_all <- merge(x = geodf500_update, y = com_cmt_evenness_all, by.x = 'name', by.y = 'Company', all = T) %>%
  arrange(!is.na(lat))
### get the list that needs to be updated
geosi2 <- geo_all %>%
  dplyr::filter(is.na(location))
com_list_to_update2  <- unique(geosi2$name);  com_list_to_update2 
### return to the 'data cleaning' section and add these companies  
geodf_to_update2 <- geodf %>% 
  dplyr::filter(name %in% com_list_to_update2) %>%
  dplyr::select(name:lat)%>%
  arrange(name)

### update the geo-location df AGAIN by combining the correct ones and updated ones
geodf500_update <- rbind(geodf_to_update1, geosi, geodf_to_update2) %>%
  distinct(name, .keep_all = T) %>%
  # merge(x = ., y = com_final, by.x = 'name', by.y = 'company_name', all = T) %>%
  arrange(!is.na(location), name)


## save data
f <- paste0(dir.results, 'geodf500_update.rds')
saveRDS(geodf500_update, file = f)
```



#### - map
See `figure_ex6_map_company_commitments.Rmd`


### * revenue
  1. using info from https://www.forbes.com/global2000/
      - Sales: $Billion
  2. Then, fill data gap
    (1) forbes global2000 (in 2019)
    (2) https://fortune.com/global500/2020/; 
      - Fortune: Revenues ($M)
    (3) https://fortune.com/global500/2019/; e.g., Walmart
    (4) https://en.wikipedia.org/
    (5) google
    
  - *Revenue* = sales = total income by sale of goods and services that brefore accounting for any expenses
    GDP = the *revenue* of a country
  - Profit = net income, after accounting for all expenses
```{r}
getwd()
xls <- paste0(dir.raw, 'company_info_Zilong/geo_location_coms/revenue.xlsx')
excel_sheets(xls)
rvn <- readxl::read_excel(path = xls, sheet = 1) %>%
  dplyr::select(1:3)
names(rvn) <- c('ID', 'name', 'revenue_usd_mil') ## million USD

### load the final 500 com list - "com_final"
f <- paste0(dir.results, 'com_final_500_scr.RData')
load(f)
com_final_ctr <- com_final %>%
  dplyr::select(company_name:Country)

### link with the company info provided by UNGSII
rvn500 <- rvn %>%
  merge(x = ., y = com_final, by.x = 'name', by.y = 'company_name', all.y = T) %>%
  arrange(!is.na(revenue_usd_mil), name)

### fill data gap manually 
f <- paste0(dir.raw, 'company_info_Zilong/geo_location_coms/revenue_fillna.xlsx')
writexl::write_xlsx(x = rvn500, path = f)

### update the data
f <- paste0(dir.raw, 'company_info_Zilong/geo_location_coms/revenue_update.xlsx')
rvn500new <- read_excel(path = f, sheet = 1) %>%
  dplyr::mutate(revenue_usd_mil = as.numeric(revenue_usd_mil)) %>%
  arrange(!is.na(revenue_usd_mil), revenue_usd_mil, name)
str(rvn500new)

### total revenue (million USD)
rvn500_total <- sum(rvn500new$revenue_usd_mil); 
print(paste0(round(rvn500_total/1000/1000, digits = 2), ' trillion'))

global_gdp <- 87751541 ## (million USD) in 2019 World bank data
percent(rvn500_total/(global_gdp), accuracy = 0.01) ## 17.43%

# The United States is the world's largest economy with a GDP of approximately $21.43 trillion; 24.42% of the World's GDP
# China is the world's SECOND largest economy with a GDP of approximately $14.34 trillion; 16.34 % of the World's GDP
```



### * employee
  (1) forbes global2000 in 2020 and then 2019
  (2) Fortune in 2020 --> 2019
  (3) Wikipedia
  (4) Google search: "company name, number of employees"
  (5) linkedin
```{r eval=FALSE, include=FALSE}
getwd()
xls <- './data_raw/company_info_Zilong/geo_location_coms/employee.xlsx'
excel_sheets(xls)
emp <- readxl::read_excel(path = xls, sheet = 1) %>%
  dplyr::select(1:3)
names(emp) <- c('ID', 'name', 'employee') ## people

### load the final 500 com list - "com_final"
### link with the company info provided by UNGSII
employee500 <- emp %>%
  merge(x = ., y = com_final, by.x = 'name', by.y = 'company_name', all.y = T) %>%
  arrange(!is.na(employee), name)

### fill data gap manually 
writexl::write_xlsx(x = emp500, path = './data_raw/company_info_Zilong/geo_location_coms/employee500_with_na.xlsx')

### update the data
xls <- './data_raw/company_info_Zilong/geo_location_coms/employee500_with_na_filled.xlsx'
employee500new <- read_excel(path = xls, sheet = 1, trim_ws = T) %>%
  as.data.frame() %>%
  dplyr::mutate(
    employee = as.character(employee),
    employee = trimws(employee),
    employee = as.numeric(gsub("\\D", "", employee))
    ) %>%
  arrange(!is.na(employee), employee, name)
str(employee500new)


### total employees
employee500_total <- sum(employee500new$employee); print(paste0(employee500_total, ' employees, in total'))
global_pop <- 7.674*10^9        ## 2019 World bank data
pop_china  <- 1.397715 * 10^9   ## 2019 World bank data
pop_usa <- 328.239523 *10^6
pop_usa * 0.59765 /10^6         ## Employment to population ratio
pop_usa_employed <- 156.92*10^6

percent(pop_china/(global_pop), accuracy = 0.01)         ## 18.21%
percent(employee500_total/(global_pop), accuracy = 0.01) ## 0.57%
percent(employee500_total/(pop_china), accuracy = 0.01)  ## 3.14%

percent(employee500_total/(pop_usa_employed), accuracy = 0.01)  ## 27.98%
```





## 2.2 The 7 million
```{r eval=FALSE, include=FALSE}
# 7 million info ----------------------------------------------------------
getwd()
dir.7m <- './data_raw/company-dataset/free-7-million-company-dataset'
# com7m <- read.csv(paste0(dir.7m, '/companies_sorted.csv'), 
#                   stringsAsFactors = F)
# save(csv7m, file = paste0(dir.7m, '/companies_sorted.RData'))
load(paste0(dir.7m, '/companies_sorted.RData'))

com7m <- csv7m
### view data
head(com7m)


test <- 
  com7m %>%
  filter(str_detect(name, 'arconic')) ## boeing|

```




