---
title: "Untitled"
author: "Yingjie"
date: "3/26/2020"
output:
  word_document: default
  pdf_document: default
  html_document: default
editor_options: 
  chunk_output_type: inline
---


# Dirs and packages
```{r include=FALSE}
## To clear your environment
remove(list = ls())

## load work dir
source('./Code/_directories.R')

source('./Code/_packages.R')

```

## Merge 'coded data' and 'com info' 

```{r}

### load the coded data: `df1` and df2`
fname <- paste0(dir.results, 'df1_df2.RData'); 
load(fname)


### load the company profile data
fname <- paste0(dir.results, 'com_final_500_scr.RData'); 
load(fname) ## `com_final, com700, ctr, ind_levels, ind_labels`



### add additional company profile to the coded data -------------------------------------
dfcom <- merge(df2, com700, 'Company', all.x = T) %>% 
  arrange(Company, goal) %>%
  dplyr::mutate(
    Company = gsub('Taiwan Semicondctor Manufacturing', 'Taiwan Semiconductor Manufacturing', Company),
    target_id = ifelse(goal_id == 'SDGs'  & is.na(target_id), 'g', target_id),
    target_id = ifelse(goal_id == 'noSDG' & is.na(target_id), 'g', target_id),
    goal_desc = ifelse(goal_id == 'noSDG' & is.na(goal_desc), 'noSDG', goal_desc)
  )

## check NA
dfcom.na <- dfcom %>% dplyr::filter_all(any_vars(is.na(.))) 
df2.na   <- df2   %>% dplyr::filter_all(any_vars(is.na(.))) 
dfcom.na <- dfcom %>% dplyr::select(-target_id) %>%
  dplyr::filter_all(any_vars(is.na(.))) 
cat('There are', length(unique(dfcom.na$Company)), 'missing data!\n\n')



### rename the final dataset
# names(dfcom)
df <- dfcom %>%
  dplyr::select(Company, iso3, goal_id, Target_id, target_id, goal, yr,
                n_statement,
                goal_desc, 
                # Target, SDG, Country,
                ind, Industry, ind_agg, ind_7sys, ind_3,
                Region, Continent) %>%
  arrange(Company, Target_id, yr)
# str(df)

cat('There are', unique(df$Company) %>% length(), 'companies after combining 2017 and 2018 data.')
```



  * get familiar with the data (NO USE)
```{r include=FALSE}
### how to normalize the data ???
df %>% dplyr::filter(yr == 2018) %>%
  ggplot(aes(x=n_statement)) + 
  geom_histogram(binwidth=2) + 
  ylim(0, 150) +
  theme_bw()

df %>% dplyr::filter(yr == 2018) %>%
  ggplot(aes(y=n_statement)) + 
  geom_boxplot() + 
  ylim(0, 50) + theme_bw()

df %>% dplyr::filter(yr == 2018) %>%
  ggplot(aes(x=n_statement)) + 
  geom_density() + theme_bw()


### find the intervals for classifying the raw data
### jenks - will be very slow; quantile - better
nclass = 10
# classint_jk <- classIntervals(df$n_statement,n=nclass, style= "jenks"); classint_jk
classint_qt <- classIntervals(df$n_statement,n=nclass, style="quantile"); classint_qt
pal <- c("red", "blue") #'yellow', 
plot(classint_qt, pal=pal, main="Quantile")

classint    <- classint_qt
brks <- c(unique(as.integer(classint$brk))); brks
seqs <- seq(1, length(brks)-1); seqs

```



### For MS

```{r - Final data}
### the final version of data input for analysis
df <- df %>%
  dplyr::mutate(
    ns = cut(n_statement, breaks = brks, 
             labels = NULL, include.lowest = T, 
             right = F, dig.lab = 3))
unique(df$ns)
unique(df$Company) %>% length() %>%
  cat('\n There are', ., ' companies in the final human-coded data.\n\n')
# str(df)

fname <- paste0(dir.results, 'df.RData'); fname
save(df, file = fname)
load(fname)
```



### Check un-coded companies

```
(318)       (356)
`df17`      `df18`
    \        /
     \      /
      \    /
      `df0` (443) ---> ... ---> `df`
```

  According to the flowchart in section 1.1, there are fewer than 500 companies either in each-year data or the combination. 
  
  We need to fill the gap, either by considering the combination, or only considering the 2018 data. 
  

```{r - match UNGSII 500}

to_use_2018_only <- T
# to_use_2018_only <- F


if (to_use_2018_only == T) {years <- c(2018)} else {years <- c(2017, 2018)}
years_label <- paste(years, collapse = "_"); cat('years_label:', years_label, '\n')

## Here, we use `com_final` to check which company do not have coded data in `df`
##    `com_final` --> 508 companies listed by UNGSII
##    `df` ---------> 443 coded companies

unique(df$Company) %>% length()

com_inData <- df %>% 
  dplyr::filter(yr %in% years) %>%
  ungroup() %>% 
  dplyr::rename(iso3_2 = iso3) %>% 
  dplyr::select(Company, iso3_2, goal_id, yr) %>% ## 443 coded companies
  arrange(desc(yr)) %>%
  dplyr::distinct(Company, .keep_all = TRUE)

unique(com_inData$Company) %>% length()



### which companies do not have coded data? ----------------------------------------------
com_inData_matchUN500 <- 
  merge(x    = com_final %>% ungroup() %>% dplyr::select(1:6, iso3),   ## 508 companies
        y    = com_inData, 
        by.x = 'company_name', 
        by.y = 'Company', 
        all  = T) %>%
  arrange(is.na(goal_id), company_name, iso3, goal_id)


### double check
# ls1 <- com_final$company_name
# ls2 <- com_inData_matchUN500$company_name
# setdiff(ls1, ls2)
# setdiff(ls2, ls1) ## "Taiwan Semicondctor Manufacturing"
```




  The world's 500 largest companies generated USD 32.7 trillion *in revenues* and USD 2.15 trillion in profits in 2018. Together, this year's Fortune Global 500 companies employ 69.3 million people worldwide and are represented by 34 countries.
  
  Fortune Global 500 were ranked by **Revenues**. https://fortune.com/global500/2019/

```{r - match Fortune 500, warning=FALSE}
f <- paste0(dir.results, 'company_Fortune_Global500.RData'); 
load(f) ## `com500ft_ToMatchName`

### merge with Fortune-Global500 to get the ranking
com_inData_matchFortune <- 
  merge(x    = com500ft_ToMatchName,
        y    = com_inData, 
        by.x = 'company_name_tomatch', 
        by.y = 'Company', 
        all  = T) %>%
  arrange(is.na(goal_id), company_name_tomatch, iso3_2, goal_id)
```



```{r - match UNGSII 500 and then Fortune 500, warning=FALSE}
com_inData_matchUN500_Fortune <- 
  merge(x = com_inData_matchUN500 %>% dplyr::select(company_name, Country, goal_id),  
        y = com500ft_ToMatchName, # %>% 
          # dplyr::select(company_name, rank, country) %>% 
          # dplyr::rename(y.rank = rank, y.country = country),
        by.x = 'company_name', 
        by.y = 'company_name_tomatch', 
        all = T) %>%
  arrange(#Rank,is.na(goal_id), iso3, 
          company_name, goal_id) %>%
  as.data.frame()


### filter the rows with NA, and to double-check name match 
com_inData_matchUN500_Fortune19_name <- com_inData_matchUN500_Fortune %>%
  dplyr::filter(is.na(Country)|is.na(country)) %>%
  as.data.frame()


### company that were coded by human and also in the Fortune 500 list --------------------
com_inData_matchUN500_inFortune <- com_inData_matchUN500_Fortune %>%
  dplyr::filter(!is.na(goal_id)) %>%
  dplyr::filter(!is.na(rank2019) | !is.na(rank2018)) %>%
  dplyr::select(-Country, -goal_id, -company_name_Fortune19) %>%
  as.data.frame()
f <- paste0(dir.raw, 'com_list_HumanCoded_inFortune.xlsx'); f
writexl::write_xlsx(x = com_inData_matchUN500_inFortune, path = f)
```




```{r - add missing companies to the list, include=FALSE}

### This depends on which list to use, UNGSII 500 or Fortune 500

### 1. add missing ones according to the UNGSII 500 List ------------------------------------
com_final_naCheckMissing <- com_inData_matchUN500_Fortune %>%
  janitor::clean_names() %>%
  dplyr::filter(is.na(goal_id) &        ## companies that are missing in data
                  !is.na(country)) %>%  ## countries that are in the reference list but not in data
  # dplyr::select(1:4, Rank, country) %>%
  # dplyr::rename(Rank_Fortune = Rank) %>%
  as.data.frame()
skimr::skim(com_final_naCheckMissing)
f <- paste0(dir.raw, 'com_final_naCheckNA_UN500_', years_label, '.xlsx'); f
writexl::write_xlsx(x = com_final_naCheckMissing, path = f)


### --> company list already done
com_added <- readxl::read_excel(path = paste0(dir.raw, 'com_final_naCheckNA_UN500_2018_ManualFillna.xlsx')) %>%
  dplyr::mutate(company_name = trimws(company_name)) %>%
  # dplyr::mutate(
  #   company_name = gsub('Anheuser\\-Busch \\(AB InBev\\)', 'AB InBev', company_name),
  #   company_name = gsub('Flextronics International', 'Flex', company_name),
  #   # company_name = gsub('xxx', 'xxx', company_name),
  #   # company_name = gsub('xxx', 'xxx', company_name),
  #   # company_name = gsub('xxx', 'xxx', company_name),
  # ) %>%
  as.data.frame()






### 2. add missing ones according to the Fortune 500 List -----------------------------------
com_final_naCheckMissing <- com_inData_matchFortune %>%
  dplyr::filter(is.na(goal_id) &        ## companies that are missing in data
                  !is.na(country)) %>%  ## countries that are in the reference list but not in data
  as.data.frame()
# skimr::skim(com_final_naCheckMissing)

com_final_naCheckMissing2 <- com_final_naCheckMissing %>%
  dplyr::mutate(company_name_tomatch = trimws(company_name_tomatch)) %>%
  dplyr::rename(company_name = company_name_tomatch) %>%
  merge(x = ., 
        y = com_added %>% dplyr::select(company_name, iso3), 
        by = 'company_name', all = T) %>%
  dplyr::filter(company_name != "Merck") %>%        ## this one has been added but with the same name in two countries
  dplyr::filter(is.na(iso3)) %>%                    ## remove the companies that have been added via `com_added`
  dplyr::select(-yr, -iso3) %>%                     ## the remaining ones to be added
  arrange(company_name) %>%
  as.data.frame()

f <- paste0(dir.raw, 'com_final_naCheckNA_Fortune_', years_label, '.xlsx'); f
writexl::write_xlsx(x = com_final_naCheckMissing2, path = f)
```


```
  Then, we manually append 
  `com_final_naCheckNA_Fortune_2018.xlsx`
                  |
                  |
                  | (add to)
                  |
                  V
  `com_final_naCheckNA_UN500_2018_ManualFillna.xlsx` 
                  |
                  | (save as ...)
                  |
                  V                             
  `com_final_naCheckNA_UN500_2018_ManualFillna_AddFortune.xlsx`
            (worked on this to fill in more reports)

```


### Data for MS and Text mining

```{r - Data for Text mining}

fname <- paste0(dir.results, 'df.RData'); fname
load(fname)



## selected companies for double-checking ------------------------------------------------
comp_name <- 'Cemex'
df_x <- df %>%
  dplyr::filter(Company %in% c(comp_name))


# comp_name <- 'Apple'
# df_x <- df %>%
#   dplyr::filter(Company %in% c(comp_name))
# 
# 
# comp_name <- 'Pfizer'
# df_x <- df %>%
#   dplyr::filter(Company %in% c(comp_name))


### save to local, and compare to the text mining approach 
fname <- paste0(dir.tm, 'df_', comp_name, '_reference.xlsx'); fname
writexl::write_xlsx(x = df_x, path = fname)

### report pdf: 
### - https://investor.apple.com/investor-relations/default.aspx#tabs_content--2019
### - https://s2.q4cdn.com/470004039/files/doc_financials/2018/q4/10-K-2018-(As-Filed).pdf

```


