---
title: "Company info"
author: "Yingjie Li"
date: "6/11/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---



# Dirs and packages
```{r include=FALSE}
### To clear your environment 
remove(list = ls())
## set work dir
path <- rstudioapi::getSourceEditorContext()$path
dir  <- dirname(rstudioapi::getSourceEditorContext()$path); dir
setwd(dir)

dir.raw     <- paste0(dir, '/data_raw')
dir.results <- paste0(dir, '/data_results')
dir.figures <- paste0(dir, '/figures'); dir.figures


source('./Code/_packages.R')
```




# 1. Company info from UNGSII
```{r}
## company info
xls <- paste0(dir.raw, '/Yingjie_Companies_190930_updateYL.xlsx')
excel_sheets(xls)
sheet <- "Companies"
df.co <- readxl::read_excel(path = xls, sheet = sheet) 
names(df.co)
head(df.co,2)

### cleaning data --------------------------------------------------------------
names(df.co) <- c("Company", 'Industry', 'Industry2', 
                  "Country", 'Continent', 
                  "Location",  "name_specifc", "ISIN")
df.co <- df.co %>% ## create a new name col for the country
  as.data.frame() %>%
  mutate(Country = gsub(' in general', '', Country)) %>%
  dplyr::select(-c(Industry2, Location))

### detect rows containing NA values in any column 
df.co %>% filter_all(any_vars(is.na(.))) 
n.industry <- unique(df.co$Industry); #n.industry
print(paste0('There are total ', length(n.industry), ' industries.'))


### number of countries by industry --------------------------------------------
ls_industry <- df.co %>%
  group_by(Industry) %>% tally() %>% arrange(n)
## write to local and tidy this list
library(writexl)
# writexl::write_xlsx(x = ls_industry, path = './data_raw/_ls_industry.xlsx')


### read in again after cleaning up Industry info ----------------------------
df.industry <- 
  readxl::read_excel(path = paste0(dir.raw,'/_ls_industry_manualTidy.xlsx')) %>%
  dplyr::select(Industry, ind_agg) %>%
  dplyr::mutate(ind_agg = str_to_title(ind_agg))
unique(df.industry$ind_agg)


df.co2 <- merge(df.co, df.industry, by = 'Industry', all.x = T)

df.co2 %>%
  group_by(ind_agg) %>% tally() %>% arrange(n) %>%
  ggplot() +
  geom_col(aes(x= reorder(ind_agg, n), y = n)) +
  coord_flip() + theme_bw()
print(paste0('There are total ', length(unique(df.co2$ind_agg)), ' industries.'))
```


#  2. Other datasets
## 2.1 Company info by Zilong
```{r}
### read data from zilong (zl)
xls <- paste0(dir.raw, '/company_info_Zilong/zilong5_zhenghe_0612.xls')
excel_sheets(xls)
sheet <- "Companies"
zl <- readxl::read_excel(path = xls, sheet = sheet) %>% as.data.frame()
nm <- names(zl)
sort(nm)
# str(zl)

## new name for the cols
nm_new <- nm %>% 
  str_to_lower(.) %>%
  gsub(' |\\-|\\(|\\)', '_', .) %>% ## special strings
  gsub('\\__', '_', .) %>%          ## double underline to single 
  gsub('\\_$', '', .) %>%           ## remove the underline at the end of the string
  gsub('number_of_|\\\n|companies|as_of_3/29/19_', '', .) %>%
  gsub('lndustry', 'industry', .) %>%
  gsub('revenues', 'revenue', .) %>%
  gsub('total_assets\t', 'assets', .) %>%
  gsub('employees', 'employee', .) %>%
  gsub('profits', 'profit', .) %>%
  gsub('headquarters', 'headquarter', .) %>%
  gsub('assets', 'asset', .) %>%
  gsub('net_income', 'income_net', .) %>%
  gsub('operating_income', 'income_operating', .) %>%
  gsub('introduction_fortune', 'website_fortune_intro', .) %>%
  gsub('fortune_global1000', 'fortune_us1000', .) %>%
  gsub('\\$m', '\\_musd', .) %>%  ## million USD
  gsub('\\__', '_', .) %>%        ## double underline to single     
  # sort() %>% 
  str_to_lower(.)
nm_new
sort(nm_new)

### rename the df
names(zl) <- nm_new

### by data source
str_subset(string = nm_new, pattern = 'fortune') 
str_subset(string = nm_new, pattern = 'forbes') %>% sort()
str_subset(string = nm_new, pattern = 'wiki') 

### by col info
str_subset(string = nm_new, pattern = 'country')
str_subset(string = nm_new, pattern = 'headquarter') ## no forbes global 2000?
str_subset(string = nm_new, pattern = 'industry')
str_subset(string = nm_new, pattern = 'sector')
str_subset(string = nm_new, pattern = 'profit')
str_subset(string = nm_new, pattern = 'employee')

### separate kaggle's HQ info and left_join to the main data
country_kaggle <- zl %>% 
  dplyr::distinct(id, headquarter_kaggle)

country_kaggle <- data.frame(
  country_kaggle, do.call(rbind, str_split(country_kaggle$headquarter_kaggle,','))) %>%
  select(-headquarter_kaggle)
names(country_kaggle) <- c("id",
                           paste0(c("city", "state", 'country'), "_kaggle"))

zl <- zl %>% left_join(., country_kaggle, by = 'id') %>%
  mutate_if(is.factor, as.character)


### add info from the raw data
com_raw <- df.co2 %>%
  mutate(id = row_number())
names(com_raw)

com_all <- com_raw %>% 
  left_join(., zl, by= 'id')

names(com_all)
str(com_all)


```


### - data cleaning by column
```{r}
### country info ---------------------------------------------------------------
country <- com_all %>% 
  select(matches(match = 'id|name|countr|city|headquarters|tude', ignore.case = T)) %>%
  select(matches(match = 'id|name|countr', ignore.case = T)) %>%
  dplyr::mutate(
    country = ifelse(
      ### decide the info choice based on data quality: Forbes, Fortune, Kaggle
      country_forbes_global2000_2020 != 'NA', country_forbes_global2000_2020, 
      ifelse(
        country_fortune_global500_2019 != 'NA', country_fortune_global500_2019, 
        ifelse(
          country_forbes_global2000_2019 != 'NA', country_forbes_global2000_2019, 
          ifelse(
            country_kaggle != 'NA', country_kaggle, NA
          )
        ))
      ),
    country = trimws(country),
    country = gsub('\\.', '', country),
    country = gsub('US', 'United States', country),
    country = str_to_title(country),
    ) %>%
  select(id, name, country, Country)
  
names(country)


### Industry  ------------------------------------------------------------------
industry <- com_all %>% as.data.frame() %>%
  dplyr::select(matches(match = 'id|name|industry|sector', ignore.case = T)) %>%
  dplyr::mutate(
    industry = ifelse(
      industry_forbes_global2000_2020 != 'NA', industry_forbes_global2000_2020, 
      ifelse(
        industry_fortune_global500_2019 != 'NA', industry_fortune_global500_2019, 
        ifelse(
          industry_wiki != 'NA', industry_wiki, 
          ifelse(
            industry_kaggle != 'NA', industry_kaggle, 
            ifelse(
              industry_fortune_us1000_2018 != 'NA', industry_fortune_us1000_2018,
              ifelse(
                industry_forbes_global2000_2019 != 'NA', industry_forbes_global2000_2019, NA
              )
              ))
          ))
      )) %>%
  dplyr::select(id, name, industry, Industry)

names(industry)


### Revenue/profits  -----------------------------------------------------------
###   may choose profit for use.
# profit = net income
profit <- com_all %>% as.data.frame() %>%
  dplyr::select(matches(match = 'id|name|revenue|profit|income', ignore.case = T)) %>%
  dplyr::mutate(
    profit = ifelse(
      profit_musd_forbes_global2000_2020 != 'NA', profit_musd_forbes_global2000_2020, 
      ifelse(
        profit_musd_fortune_global500_2019 != 'NA', profit_musd_fortune_global500_2019,
        ifelse(
          profit_musd_fortune_us1000_us_2019 != 'NA', profit_musd_fortune_us1000_us_2019,
          ifelse(
            profit_musd_forbes_global2000_2019 != 'NA', profit_musd_forbes_global2000_2019,
            ifelse(
              profit_musd_fortune_us1000_2018 != 'NA', profit_musd_fortune_us1000_2018, NA
            )
          )
          )))) %>%
  dplyr::mutate(profit = as.numeric(profit)) %>%
  dplyr::arrange(!is.na(profit), profit)
  
sort(names(profit))
# str(profit)



### Assets ---------------------------------------------------------------------
asset <- com_all %>% 
  dplyr::select(matches(match = 'id|name|asset', ignore.case = T)) %>%
  dplyr::mutate(
    asset = ifelse(
      asset_musd_forbes_global2000_2019 != 'NA', asset_musd_forbes_global2000_2019, 
      ifelse(
        asset_musd_fortune_global500_2019 != 'NA', asset_musd_fortune_global500_2019, 
        ifelse(
          asset_musd_fortune_us1000_us_2019 != 'NA', asset_musd_fortune_us1000_us_2019,
          ifelse(
            asset_musd_fortune_us1000_2018 != 'NA', asset_musd_fortune_us1000_2018,
            ifelse(
              asset_musd_forbes_global2000_2020 != 'NA', asset_musd_forbes_global2000_2020,
              NA
              # ifelse(
              #   asset_wiki != 'NA', asset_wiki, NA
              # )
            )
          )
        ))
      ),
    asset = as.numeric(asset)
    ) %>%
  dplyr::select(id, name, asset, asset_wiki) %>%
  dplyr::arrange(!is.na(asset), asset)

names(asset)
# str(asset)


### Employees ------------------------------------------------------------------
employee <- com_all %>% as.data.frame() %>%
  dplyr::select(matches(match = 'id|name|employee', ignore.case = T)) %>%
  dplyr::mutate(
    employee_wiki_num   = as.numeric(gsub("\\D", "", employee_wiki)),
    employee_kaggle_num = as.numeric(gsub("\\D", "", employee_kaggle)),
    employee_kaggle_num = ifelse(employee_kaggle_num > 10, employee_kaggle, NA)) %>%
  as.data.frame() %>%
  dplyr::mutate(
    # small number might be wrong for kaggle data
    employee = ifelse(
      employee_forbes_global2000_2019 != 'NA', employee_forbes_global2000_2019,
      ifelse(
        employee_fortune_global500_2019 != 'NA', employee_fortune_global500_2019,
        ifelse(
          employee_fortune_us1000_us_2019 != 'NA', employee_fortune_us1000_us_2019,
          ifelse(
            employee_fortune_us1000_2018 != 'NA', employee_fortune_us1000_2018,
            ifelse(
              employee_forbes_global2000_2020 != 'NA', employee_forbes_global2000_2020,
              ifelse(
                !is.na(employee_wiki_num), employee_wiki_num,
                ifelse(
                  !is.na(employee_kaggle_num), employee_kaggle_num, NA)))))))) %>%
  dplyr::mutate(employee = as.numeric(employee)) %>%
  dplyr::arrange(!is.na(employee), employee)

sort(names(employee))
# str(employee)
# unique(employee$employee)

```

### * geo-coding lat/lon
  1. using info from https://www.forbes.com/global2000/; e.g., Walmart
      - Country/Territory: United States
      - Headquarters:      Bentonville, Arkansas
  2. Then, fill data gap for those  that are not included in www.forbes.com
    (1) forbes global2000 (in 2019, I saw you have this data)
    (2) https://fortune.com/global500/2020/; e.g., Walmart
      - Country: U.S.
      - Headquarters: Bentonville, Ark. (city, state)
    (3) https://fortune.com/global500/2019/; e.g., Walmart
      - HQ Location: Bentonville, Ark. (city, state)
      - (NO Country INFO, SAME AS 2018)
    (4) https://en.wikipedia.org/wiki/Walmart (an example)
      - Headquarters:	Bentonville, Arkansas, U.S.
  3. Geo-coding and generate lat/lon info for mapping

#### - data cleaning
```{r}
getwd()
xls <- './data_raw/zilong/geo_location_coms/geo_location_en_v0906.xlsx'
excel_sheets(xls)
geodf <- readxl::read_excel(path = xls, sheet = 1) %>%
  dplyr::select(ID:lat)
# names(geodf)
# head(geodf,2)

### load the final 500 com list - "com_final"
load('./data_raw/com_final_500_scr.RData')
com_final_ctr <- com_final %>%
  dplyr::select(company_name:Country)
geodf500 <- geodf %>%
  ### link with the company info provided by UNGSII, and double-check on the location info (country location)
  merge(x = ., y = com_final, by.x = 'name', by.y = 'company_name', all.y = T)
str(geodf500)

### by manually check the data, we need to revise some of the info
xls <- './data_raw/zilong/geo_location_coms/geo_location_en_need_revision_done.xlsx'
geosi <- readxl::read_excel(path = xls, sheet = 1) %>%
  dplyr::select(ID:lat, -ID) 
com_list_to_update  <- unique(geosi$name);  com_list_to_update ### get the list that needs to be updated
### subset the ones that need to be updated
geodf_to_update0 <- geodf500 %>% 
  dplyr::filter(name %in% com_list_to_update | is.na(lat)) %>%
  dplyr::select(name:lat, -ID)
### subset the ones that are correct
geodf_to_update1 <- geodf500 %>% 
  dplyr::filter(!name %in% com_list_to_update & !is.na(lat)) %>%
  dplyr::select(name:lat, -ID)
### update the geo-location df by combining the correct ones and updated ones
geodf500_update <- rbind(geodf_to_update1, geosi) %>%
  distinct(name, .keep_all = T) %>%
  # merge(x = ., y = com_final, by.x = 'name', by.y = 'company_name', all = T) %>%
  arrange(name)

### check if there are missing companies from the SDG coding data (that not included in the 500 list)
### load the average commitments and evenness at company level
load(paste0(dir.results, 'com_cmt_evenness_all.RData'))
### link with the geo-location data
geo_all <- merge(x = geodf500_update, y = com_cmt_evenness_all, by.x = 'name', by.y = 'Company', all = T) %>%
  arrange(!is.na(lat))
### get the list that needs to be updated
geosi2 <- geo_all %>%
  dplyr::filter(is.na(location))
com_list_to_update2  <- unique(geosi2$name);  com_list_to_update2 
### return to the 'data cleaning' section and add these companies  
geodf_to_update2 <- geodf %>% 
  dplyr::filter(name %in% com_list_to_update2) %>%
  dplyr::select(name:lat)%>%
  arrange(name)

### update the geo-location df AGAIN by combining the correct ones and updated ones
geodf500_update <- rbind(geodf_to_update1, geosi, geodf_to_update2) %>%
  distinct(name, .keep_all = T) %>%
  # merge(x = ., y = com_final, by.x = 'name', by.y = 'company_name', all = T) %>%
  arrange(!is.na(location), name)
```



#### - map
```{r}
library(sf)
library(ggrepel)
library(rnaturalearthdata)
library(rnaturalearth)
library(sf)
shp <- ne_countries(scale = 'medium', type = 'countries', returnclass = 'sf') %>%
  dplyr::select(name, type, iso_a3, economy, income_grp) %>%
  dplyr::filter(name != 'Antarctica')

geodf500_update1 <- geodf500_update %>%
  dplyr::filter(!is.na(lat)) %>%
  # dplyr::select(name:Country) %>% 
  mutate(lat1 = case_when(
    str_detect(lat, "S") ~ as.numeric(as.character(gsub('°S', '', lat)))*(-1),
    TRUE ~ as.numeric(as.character(gsub('°N', '', lat)))
  )) %>% 
  mutate(lon1 = case_when(
    str_detect(lon, "W") ~ as.numeric(gsub('°W', '', lon))*(-1),
    TRUE ~ as.numeric(gsub('°E', '', lon))
  )) %>%
  ### some locations are the same, and here we make a small adjustment to the lat/lon to avoid overlaps
  ### the result look not change much - may not useful
  # dplyr::mutate(
  #   i = runif(n = nrow(.), min= -0.5, max = 0.5),
  #   j = runif(n = nrow(.), min= -0.5, max = 0.5),
  #   lat2 = lat1 + i,
  #   lon2 = lon1 + j
  #   ) %>%
  arrange(!is.na(lat1)) 
geodf_sf <- st_as_sf(geodf500_update1, coords = c("lon1", "lat1"), remove = F, crs = 4326)


### Link geo-location with commitments and evenness data -------------------------------------------------------------
### load the average commitments and evenness at company level
load(paste0(dir.results, 'com_cmt_evenness_all.RData'))
### link with the geo-location data
geo_all <- merge(x = geodf_sf, y = com_cmt_evenness_all, by.x = 'name', by.y = 'Company', all = T) %>%
  arrange(!is.na(lat1))
### get the list that needs to be updated
geosi2 <- geo_all %>%
  dplyr::filter(is.na(location))
com_list_to_update2  <- unique(geosi2$name);  com_list_to_update2 
### return to the 'data cleaning' section and add these companies
###
### plot commitment and evenness at company level
map_com <- ggplot() +
  geom_sf(data = shp, fill = 'gray90', color='gray70', size = 0.1) +
  geom_sf(data = geo_all, aes(size = cmt_mean, color = (evenness)), alpha = 0.6) +
  scale_size_continuous(range = c(0.1, 5)) +
  # scale_color_continuous(direction = -1) +
  # scale_color_continuous(trans = 'reverse') +
  scale_color_viridis(option = "D", direction = 1, na.value = "grey50")+
  #edit legends
  guides(
    #reverse color order (higher value on top)
    color = guide_colorbar(reverse = F),
    #reverse size order (higher diameter on top) 
    size = guide_legend(reverse = TRUE))+
  # geom_text_repel(data = geodf500_test, aes(x = lon1, y = lat1, label = name)) +
  labs(color = "Evenness", size = 'Number of \ncommitments') +
  theme_bw() +
  theme_ns+
  theme(
    legend.position = c(0.12, 0.4),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    # panel.border = element_rect(colour = 'transparent'),
    panel.border = element_blank()); map_com
  

### save as jpg
fname <- paste0(dir.figures, '/company_location_map.jpg');fname
ggsave(fname, plot = last_plot(), width = width_2col, 
       height = width_2col/2.2, units = unit_ns, dpi = 1200)

```



```{r}
zoom_to <- c(5.38, 52.52)  # EU
zoom_level <- 3
lon_span <- 360 / 2^zoom_level
lat_span <- 180 / 2^zoom_level
lon_bounds <- c(zoom_to[1] - lon_span / 2, zoom_to[1] + lon_span / 2)
lat_bounds <- c(zoom_to[2] - lat_span / 2, zoom_to[2] + lat_span / 2)

map_com +
  geom_sf(data = st_sfc(st_point(zoom_to), crs = 4326), color = 'transparent', size = 0.1) +
  coord_sf(xlim = lon_bounds, ylim = lat_bounds) +
  theme(legend.position = "none", 
        panel.border = element_rect(colour = "black", fill=NA, size=.5))
### save as jpg
fname <- paste0(dir.figures, '/company_location_map_EU.jpg');fname
ggsave(fname, plot = last_plot(), 
       width = width_2col/2.2, 
       height = width_2col/2.2, units = unit_ns, dpi = 1200)


zoom_to <- c(126.9780, 37.5665) ## Seoul
zoom_to <- c(-90.8033, 40.5428) ## Pennsylvania in US
lon_bounds <- c(zoom_to[1] - lon_span / 2, zoom_to[1] + lon_span / 2)
lat_bounds <- c(zoom_to[2] - lat_span / 2, zoom_to[2] + lat_span / 2)
map_com +
  geom_sf(data = st_sfc(st_point(zoom_to), crs = 4326), color = 'transparent', size = 0.1) +
  coord_sf(xlim = lon_bounds, ylim = lat_bounds) +
  theme(legend.position = "none", 
        panel.border = element_rect(colour = "black", fill=NA, size=.5))
### save as jpg
fname <- paste0(dir.figures, '/company_location_map_asia.jpg');fname
ggsave(fname, plot = last_plot(), 
       width = width_2col/2.2, 
       height = width_2col/2.2, units = unit_ns, dpi = 1200)
```







### * revenue
  1. using info from https://www.forbes.com/global2000/
      - Sales: $Billion
  2. Then, fill data gap
    (1) forbes global2000 (in 2019)
    (2) https://fortune.com/global500/2020/; 
      - Fortune: Revenues ($M)
    (3) https://fortune.com/global500/2019/; e.g., Walmart
    (4) https://en.wikipedia.org/
    (5) google
    
  - *Revenue* = sales = total income by sale of goods and services that brefore accounting for any expenses
    GDP = the *revenue* of a country
  - Profit = net income, after accounting for all expenses
```{r}
getwd()
xls <- './data_raw/zilong/geo_location_coms/revenue.xlsx'
excel_sheets(xls)
rvn <- readxl::read_excel(path = xls, sheet = 1) %>%
  dplyr::select(1:3)
names(rvn) <- c('ID', 'name', 'revenue_usd_mil') ## million USD

### load the final 500 com list - "com_final"
load('./data_raw/com_final_500_scr.RData')
com_final_ctr <- com_final %>%
  dplyr::select(company_name:Country)

### link with the company info provided by UNGSII
rvn500 <- rvn %>%
  merge(x = ., y = com_final, by.x = 'name', by.y = 'company_name', all.y = T) %>%
  arrange(!is.na(revenue_usd_mil), name)

### fill data gap manually 
writexl::write_xlsx(x = rvn500, path = './data_raw/zilong/geo_location_coms/revenue_fillna.xlsx')

### update the data
xls <- './data_raw/zilong/geo_location_coms/revenue_update.xlsx'
rvn500new <- read_excel(path = xls, sheet = 1) %>%
  dplyr::mutate(revenue_usd_mil = as.numeric(revenue_usd_mil)) %>%
  arrange(!is.na(revenue_usd_mil), revenue_usd_mil, name)
str(rvn500new)

### total revenue (million USD)
rvn500_total <- sum(rvn500new$revenue_usd_mil); print(paste0(round(rvn500_total/1000/1000, digits = 2), ' trillion'))
global_gdp <- 87751541 ## (million USD) in 2019 World bank data
percent(rvn500_total/(global_gdp), accuracy = 0.01) ## 17.43%

# The United States is the world's largest economy with a GDP of approximately $21.43 trillion; 24.42% of the World's GDP
# China is the world's SECOND largest economy with a GDP of approximately $14.34 trillion; 16.34 % of the World's GDP
```



### * employee
  (1) forbes global2000 in 2020 and then 2019
  (2) Fortune in 2020 --> 2019
  (3) Wikipedia
  (4) Google search: "company name, number of employees"
  (5) linkedin
```{r}
getwd()
xls <- './data_raw/zilong/geo_location_coms/employee.xlsx'
excel_sheets(xls)
emp <- readxl::read_excel(path = xls, sheet = 1) %>%
  dplyr::select(1:3)
names(emp) <- c('ID', 'name', 'employee') ## people

### load the final 500 com list - "com_final"
### link with the company info provided by UNGSII
employee500 <- emp %>%
  merge(x = ., y = com_final, by.x = 'name', by.y = 'company_name', all.y = T) %>%
  arrange(!is.na(employee), name)

### fill data gap manually 
writexl::write_xlsx(x = emp500, path = './data_raw/zilong/geo_location_coms/employee500_with_na.xlsx')

### update the data
xls <- './data_raw/zilong/geo_location_coms/employee500_with_na_filled.xlsx'
employee500new <- read_excel(path = xls, sheet = 1, trim_ws = T) %>%
  as.data.frame() %>%
  dplyr::mutate(
    employee = as.character(employee),
    employee = trimws(employee),
    employee = as.numeric(gsub("\\D", "", employee))
    ) %>%
  arrange(!is.na(employee), employee, name)
str(employee500new)


### total employees
employee500_total <- sum(employee500new$employee); print(paste0(employee500_total, ' employees, in total'))
global_pop <- 7.674*10^9        ## 2019 World bank data
pop_china  <- 1.397715 * 10^9   ## 2019 World bank data
pop_usa <- 328.239523 *10^6
pop_usa * 0.59765 /10^6         ## Employment to population ratio
pop_usa_employed <- 156.92*10^6

percent(pop_china/(global_pop), accuracy = 0.01)         ## 18.21%
percent(employee500_total/(global_pop), accuracy = 0.01) ## 0.57%
percent(employee500_total/(pop_china), accuracy = 0.01)  ## 3.14%

percent(employee500_total/(pop_usa_employed), accuracy = 0.01)  ## 27.98%
```





## 2.2 The 7 million
```{r eval=FALSE, include=FALSE}
# 7 million info ----------------------------------------------------------
getwd()
dir.7m <- './data_raw/company-dataset/free-7-million-company-dataset'
# com7m <- read.csv(paste0(dir.7m, '/companies_sorted.csv'), 
#                   stringsAsFactors = F)
# save(csv7m, file = paste0(dir.7m, '/companies_sorted.RData'))
load(paste0(dir.7m, '/companies_sorted.RData'))

com7m <- csv7m
### view data
head(com7m)


test <- 
  com7m %>%
  filter(str_detect(name, 'arconic')) ## boeing|

```




