---
title: "Text_mining"
author: "Yingjie"
date: "6/17/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

Last update: 11/17/2022

# Directories and packages

```{r include=FALSE}
### To clear your environment 
remove(list = ls())

library(dplyr)
library(stringr)

# ## devtools is required
# library(devtools)
# install_github("dasonk/docstring")
library(docstring)

```


# SDG search terms


  Make a list of keywords for SDGs.

|SDG_id       |SDG_keywords     |
|SDG1_1       |keywords here    |

  These SDG search terms can be *direct mention*, such as "SDG 1", "SDG 2", "SDG 1.2", "SDG 1.a", or *indirect mention*.  

  This collection includes terms that are directly related to SDGs, i.e., if companies specifically mention SDG ids (e.g., 'SDG 13'), or the target or indicator ids (e.g., SDG 13.1.a). 
  
  
```{r - 1. Collection - direct commit}

script_file <- './code/helper_SDG_search_terms.R' ## the 2nd version

source(file = script_file)

## combine 2 levels of key words together
SDG_keys   <- rbind(goal_keys, target_keys)
SDG_ls_str <- SDG_keys$SDG_id %>% as.character(); SDG_ls_str

## name it as the 'directly' keywords
SDG_keys_drc <- SDG_keys
```





 This collection includes terms that are *indirectly* related to SDGs, i.e., the terms are constructed based on the alignment to the description and meanings of each SDG or Target. 
  
```{r - 2. Collection - indirect commit}

### get the list of all the 'indirect' keywords and bind these together in a dataframe
SDG_ls_str <- ls(pattern = "SDG[0-9].*") %>% sort(); SDG_ls_str

# SDG_ls_str <- grep("['xyzw]", SDG_ls_str, value = TRUE, invert = TRUE) # invert = TRUE means to return the values that were not matched.
# SDG_ls_str

SDG_keys <- data.frame()  

for (i in 1:length(SDG_ls_str) ) {
  # print(i)
  sdg_i_str <- SDG_ls_str[i]
  sdg_i_obj <- get(sdg_i_str)
  df_i <- data.frame(SDG_id       = sdg_i_str, 
                     SDG_keywords = sdg_i_obj)
  SDG_keys <- rbind(SDG_keys, df_i) %>%
    dplyr::mutate(SDG_id       = as.character(SDG_id),
                  SDG_keywords = as.character(SDG_keywords))
}


SDG_keys_indrc <- SDG_keys %>%
  as.data.frame() %>%
  arrange(SDG_id) %>%
  dplyr::mutate(SDG_id2 = gsub('_x.*|_y.*|_z.*|_w.*', '', SDG_id)) %>%
  group_by(SDG_id2) %>%
  ## here we keep the separated search terms (e.g., SDG11_1_x, SDG11_1_y), but removed the combined search terms (e.g., SDG11_1, which is a combination of SDG11_1_x and SDG11_1_y)
  dplyr::mutate(n = n(),                               ## count the number of the same target
                m = ifelse(SDG_id2 == SDG_id, 1, 0),   ## if the original name is the same as the new cleaned name
                filter = case_when(n==1 & m==1 ~ 1,    ## use a filter to remove if (n>1 and the names are the same) 
                                   n >1 & m==1 ~ 0,
                                   TRUE ~ 1)) %>%
  dplyr::select(SDG_id, SDG_id2, n, m, filter, everything()) %>%
  # dplyr::filter(filter == 1) %>%    ## changed on 2/28/2022
  dplyr::select(-n, -m, -filter) %>%
  dplyr::select(-SDG_id) %>%
  dplyr::rename(SDG_id = SDG_id2) %>%
  as.data.frame()
```






```{r - 3. Collection - both}

SDG_keys_drc$match_tpye   <- 'direct'
SDG_keys_indrc$match_tpye <- 'indirect'

SDG_keys <- rbind(SDG_keys_drc, SDG_keys_indrc)



## Save to database --------------------------------------------------------------------------------

### 1. for this project
f <- paste0(dir.tm, 'database/', 'SDG_keys.RData'); f
save(SDG_keys_drc, SDG_keys_indrc, SDG_keys, file = f)

### 1.1. save as rds
f <- paste0(dir.tm, 'database/', 'SDG_keys.rds'); f
saveRDS(SDG_keys, file = f)


### 2. save to `SDG_TM` for R package development
fname <- paste0(dirname(getwd()), '/SDG_TM/data/SDG_keys.RData'); fname
save(SDG_keys, file = fname)

### 3. for R package development
fname <- paste0('./Code/SDGdetector/data/', 'SDG_keys.RData'); fname
save(SDG_keys, file = fname)
```

