---
title: "Text_mining"
author: "Yingjie"
date: "6/17/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---


# Directories and packages

```{r include=FALSE}
### To clear your environment 
remove(list = ls())

## set work dir
path <- rstudioapi::getSourceEditorContext()$path
dir  <- dirname(rstudioapi::getSourceEditorContext()$path); dir
setwd(dir)
getwd()
dirname(dir)
setwd(dirname(dir))
getwd()

# directories for Yingjie
  dir.reports <- './Data/data_TextMining/annual_reports/'
  dir.results <- './Data/data_results/'
  dir.figures <- './Data/figures/';      dir.figures

# directories for Veronica
  # dir.reports <- '../Data/data_TextMining/annual_reports/' # VF added another '.'
  # dir.results <- '../Data/data_results/'                   # VF added another '.'
  # dir.figures <- '../Data/figures/';      dir.figures      # VF added another '.'

# load packages
  source('./Code/_packages.R')

  library(tm)        # text mining: readPDF(), Corpus()
  library(tidyverse) # piping and wrangling
  library(tabulizer) # importing PDFs
  #library(remotes)  # installing from remote repositories
```


# Data imports

## Convert a PDF to text format

### Read in files

  Option #1: using `tm::readPDF`

```{r}

pdf <- paste0(dir.reports, 'pdf_coded_human/', 'CEMEX--IntegratedReport2018.pdf'); pdf
# pdf <- paste0(dir.reports, 'Apple--10-K-2018-(As-Filed).pdf'); pdf
# pdf <- paste0(dir.reports, 'Pfizer--2018-Financial-Report.pdf'); pdf # not readable or editable
# pdf <- paste0(dir.reports, 'Pfizer--Financial-Report-2017.pdf'); pdf
# pdf <- paste0(dir.reports, 'Pfizer--Proxy2019__2018 Financial Report.pdf'); pdf




# read <- tm::readPDF(control = list(text = "-layout"))
# document <- tm::Corpus(URISource(pdf), readerControl = list(reader = read))
# doc <- content(document[[1]])
# head(doc)
# 
# page_breaks <- grep("f", doc)
# doc[page_breaks[1]]
# 
# 
# doc_txt <- read.delim(file = paste0(dir.reports, 'CEMEX--IntegratedReport2018.txt'))
# doc2 <- Corpus(doc_txt)
# doc_txt[1]
```


  Option #2: using `pdftools::pdf_text()`
  We will **not** be using this, since it finds less words and also doesn't work well with columns. 

```{r eval=FALSE, include=FALSE}
### test code 
# get encoding 
  # txt1 <- pdftools::pdf_text(pdf)
  # readr::guess_encoding(txt1) #It's UTF-8

# read file and format
  txt1 <- pdftools::pdf_text(pdf) %>%
          paste(sep = " ") %>%
          stringr::str_replace_all(fixed("\n"), " ") %>% # erase new lines
          stringr::str_replace_all(fixed("\r"), " ") %>% # carriage return
          stringr::str_replace_all(fixed("\t"), " ") %>% # erase tabs
          stringr::str_replace_all(fixed("\""), " ") %>%
          paste(sep = " ", collapse = " ") %>%
          stringr::str_squish() %>%
          stringr::str_replace_all("- ", "") # incomplete words continuing to next line

# get word count
  cat('Total words from `pdftools`:',sapply(strsplit(txt1, " "), length))
```


  Option #3: The 3rd way to read pdf using `tabulizer::extract_text()`.
  This package can better deal with PDF format with multiple columns. 

```{r}

# if (!require("remotes")) {
#     install.packages("remotes")
# }
# remotes::install_github(c("ropensci/tabulizerjars", "ropensci/tabulizer"), INSTALL_opts = "--no-multiarch")

# get encoding 
  # txt2 <- tabulizer::extract_text(file = pdf)
  # readr::guess_encoding(txt2) #It's UTF-8

txt2 <- tabulizer::extract_text(file = pdf) %>%
  iconv("UTF8", "ASCII", "") %>% # change encoding
  
  # gsub("\\n", " ", .) %>% # erase new lines
  # gsub("\\r", " ", .) %>% # erase carriage return
  # gsub("\\t", " ", .) %>% # erase tabs
  # gsub("\"", " ", .) %>%  # erase "
  # gsub("  ", " ", .) %>%  # erase repeated whitespace
  # gsub("- ", "", .) %>%   # fix incomplete words continuing to next line
  # paste(sep = " ", collapse = " ")
  
  stringr::str_replace_all(fixed("\n"), " ") %>% # erase new lines
  stringr::str_replace_all(fixed("\r"), " ") %>% # erase carriage return
  stringr::str_replace_all(fixed("\t"), " ") %>% # erase tabs
  stringr::str_replace_all(fixed("\""), " ") %>% # erase "
  paste(sep = " ", collapse = " ") %>%
  stringr::str_squish() %>%             # remove leading & trailing whitespace, and repeated whitespace inside a string
  stringr::str_replace_all("- ", "")    # fix incomplete words continuing to next line
  

### change encoding is needed to fix the encoding problems of punctuation in a sentence --> 'This plan is designed to fortify our company<U+9225><U+6A9A> position as a leading global building materials company.'

# get count of words
  cat('Total words from `tabulizer`:', sapply(strsplit(txt2, " "), length))
```



We will us `tabulizer` since it gives us more words and is cleaner!

```{r}
# cleaned .txt as input for analysis 
  txt <- txt2
```


### Organizing files: find, rename and copy and paste to another directory in batch

```{r}
# renaming company PDF file to company name only
company_name <- str_split(string = basename(pdf), pattern = "--", n = 2) %>% unlist(); 
company_name <- company_name[1]; company_name
TXTname <- paste0(dir.reports, 'txt_cleaned/', company_name, '.txt'); TXTname
   
# writeLines(txt, TXTname)
```



## For-loop all PDFs
  
  Conversion to text --> and save .txt with name from list and move to another folder. 
  
```{r}
### test code
# dirpath <- dir.reports


# Custom function
convertpdf2txt <- function(dirpath){
  files <- list.files(dirpath, pattern = '*.pdf$', ignore.case = T, full.names = T); files
  for (pdf in files) {
    txt <- tabulizer::extract_text(file = pdf) %>%
      iconv("UTF8", "ASCII", "") %>% # change encoding
      paste(sep = " ") %>%
      stringr::str_replace_all(fixed("\n"), " ") %>% # erase new lines
      stringr::str_replace_all(fixed("\r"), " ") %>% # erase carriage return
      stringr::str_replace_all(fixed("\t"), " ") %>% # erase tabs
      stringr::str_replace_all(fixed("\""), " ") %>% # erase "
      paste(sep = " ", collapse = " ") %>%
      stringr::str_squish() %>%             # remove leading & trailing whitespace, and repeated whitespace inside a string
      stringr::str_replace_all("- ", "")    # fix incomplete words continuing to next line

    ### renaming company PDF file to company name only
    ### save .txt files to another folder. 
    company_name <- str_split(string = basename(pdf), pattern = "--", n = 2) %>% unlist()
    TXTname <- paste0(dir.reports, 'txt_cleaned/', company_name[1], '.txt'); print(TXTname)
    writeLines(txt, TXTname)
    }
}

### test code
# convertpdf2txt(dirpath = dir.reports)
```


# Text mining

## Text file formatting 

  Option #1: Convert text to corpus for keyword matching.

```{r}
# convert text to corpus

# delete empty rows (or vectors within lists, however they're called)

# Convert text into a large paragraph (goal: to bring incomplete sentence lines together)
  # flatten list? Corpus is in list format
  # unlist() might be the function?
```

  Option #2: format corpus where each sentence is a row. 

```{r}

# this requires pattern searching where every sentence has to end with a period (.) ----------------
  # --- limitations/problems for: figure text, bullet points, anything without a period.


## remove words that repeatedly appear in the text.  
noise_text <- paste('1 Company Overview 2 How We Create Value 3 Our Performance 4 Governance 5 Results in Detail 6 About this ReportContents',
                    '2018 CEMEX INTEGRATED REPORT',
                    sep = '|')
txt <- txt %>%
  stringr::str_replace_all(noise_text, ".")

## separate the large character chunk to short sentences by '.' (period), ';' (semicolon), ':' (colon), and '/ ' (slash with space)
# txt_sentence <- unlist(strsplit(txt, split = "\\. |\\; |\\/ |\\: |\\, ")) %>% trimws() ## with ',' (comma)
txt_sentence <- unlist(strsplit(txt, split = "\\. |\\; |\\/ |\\: ")) %>% trimws()      ## without ',' (comma)


# get structure
str(txt_sentence)

## to inspect row 100
txt_sentence[100]

  
## work in df --------------------------------------------------------------------------------------
txt_sentence_df <- data.frame(statement = txt_sentence) %>%
  dplyr::mutate(id = row.names(.) %>% as.numeric(),
                statement = as.character(statement)) %>%
  # dplyr::filter(nchar(statement) > 5) %>% # remove non-sentences or sentence with few words
  as.data.frame()

## write to xlsx for inspection 
fname <- paste0(dir.reports, 'txt_sentence_df_inspection.xlsx'); fname
writexl::write_xlsx(txt_sentence_df, fname, )

```



## SDG search terms

  Make a list of keywords for SDGs.

|SDG_id       |SDG_keywords     |
|SDG1_1       |keywords here    |

  These SDG search terms can be *direct mention*, such as "SDG 1", "SDG 2", "SDG 1.2", "SDG 1.a", or *indirect mention*.  

```{r - Load the database}
fname <- paste0('./Data/data_TextMining/database/', 'SDG_keys.RData'); fname
load(fname) ## --> SDG_keys_drc, SDG_keys_indrc, SDG_keys

```

 



## To detect  

  To match the keywords to each corpus and format results

  Add columns to see how many have comments using these terms.
  Here are the options:
  1. for every row in the corpus (ideally only 1 sentence in each row), have a column 1-17 and 1/0 or y/n if matching the SDG.
    - this would be a for-loop and i 1:17 is linked to the columns being filled
  2. for entire corpus, extract rows (ideally only 1 sentence at a time) that match only 1 SDG.
    - this would be a for-loop and i 1:17 is a new vector to be added to a list (17 of them)

**Format 1**
```
|row number|sentence                    |SDGs_detected       |
|1         |we need to eradicate poverty|SDG1, SDG2          | 
.
.
|1000      |we are talking getting rich |SDG1, SDG17         |
```

**Format 2**
```
|row number|sentence                    |SDG1       |SDG2       |...        |SDG17    |
|1         |we need to eradicate poverty|1          |0          |...        |         |
.
.
|1000      |we are talking getting rich |0          |0          |...        |0        |
```  

```{r - Detect SDGs}
# THIS CODE IS TO IDENTIFY MATCHING ROWS, BUT IT DOES NOT EXTRACT SENTENCES
# in the original dataframe, if it matches, then in a new column, say yes; if not, say no.


code <- txt_sentence_df %>% 
  dplyr::mutate(#match   = 0,      
                sdgs    = '', ## for later use, to append data to this column
                n_total = 0,
                sdgs_n  = '')


for (i in 1:nrow(SDG_keys)){                ## Loop all SDG indicators
    sdg_i_str <- SDG_keys$SDG_id[i]         ## get the SDG id name
    sdg_i_obj <- SDG_keys$SDG_keywords[i]   ## get the corresponding SDG search term list
    
    print(sdg_i_str)
    # print(sdg_i_obj)
    
    code <-  code %>%
      as.data.frame() %>%
      
      ## at the sentence level - count once if goals/targets are mentioned -------------------------
      dplyr::mutate(
        match = ifelse(
          grepl(pattern = sdg_i_obj, x = statement, ignore.case = T, perl = T), 1, 0))  %>% ## yes-1 or no-0 if they match
      dplyr::mutate(sdgs = ifelse(match > 0, paste0(sdgs, ',', sdg_i_str), sdgs)) %>%
      
      ## at the sentence level - count the times of all the mentions -------------------------------
      dplyr::mutate(
        n       = str_count(string = statement, regex(pattern = sdg_i_obj, ignore_case = T)),
        n_total = n_total + n,
        sdgs_n  = ifelse(n > 0, paste0(sdgs_n, ',', sdg_i_str, '-', n), sdgs_n)
        ) %>%
      as.data.frame()
}



coded <- code %>%
  # sort from most SDG hits to least (or, none)
  arrange(desc(nchar(sdgs)), id)


sum(coded$n)
sum(coded$n_total)
```


  At the **sentence** level - detect if a subject country or region is mentioned. 
  
```{r - Detect region names}

source('./Code/function_detect_region.R')

coded_region <- coded

coded_region <- detect_region(data = coded_region, text_column = 'statement')

```



  At the **paragraph** level - detect if a subject country or region is mentioned. 
  
  We treat 10 sentences before and 10 sentences after a focus sentence as a approximate paragragh here.  
  
```{r - Detect region names - in paragraph}

## create a separate data frame
coded_para <- coded_region
coded_para$para <- ''


## aggregate sentences to paragraph level ----------------------------------------------------------
nmax <- nrow(coded_para)

for (i in 1:nmax) {
  
  ## - for the first 10 sentences, we only append 10 sentences after them 
  if(i <= 10){
    para = paste(
      coded_para$statement[i], 
      coded_para$statement[i+1], coded_para$statement[i+2], coded_para$statement[i+3], coded_para$statement[i+4], coded_para$statement[i+5],
      coded_para$statement[i+6], coded_para$statement[i+7], coded_para$statement[i+8], coded_para$statement[i+9], coded_para$statement[i+10], 
      sep = '. ')} 
  
  ## - for the last 10 sentences, we only append 10 sentences before them
  else if (i > nmax - 10) {
    para = paste(
      coded_para$statement[i-10], coded_para$statement[i-9], coded_para$statement[i-8], coded_para$statement[i-7], coded_para$statement[i-6],
      coded_para$statement[i-5],  coded_para$statement[i-4], coded_para$statement[i-3], coded_para$statement[i-2], coded_para$statement[i-1],
      coded_para$statement[i],
      sep = '. ')} 
  
  ## - for all other cases, we append both 10 sentences before and 10 after 
  else {
    para = paste(
      coded_para$statement[i-10], coded_para$statement[i-9], coded_para$statement[i-8], coded_para$statement[i-7], coded_para$statement[i-6],
      coded_para$statement[i-5],  coded_para$statement[i-4], coded_para$statement[i-3], coded_para$statement[i-2], coded_para$statement[i-1],
      coded_para$statement[i], 
      coded_para$statement[i+1], coded_para$statement[i+2], coded_para$statement[i+3], coded_para$statement[i+4], coded_para$statement[i+5],
      coded_para$statement[i+6], coded_para$statement[i+7], coded_para$statement[i+8], coded_para$statement[i+9], coded_para$statement[i+10],
      sep = '. ')}
  
  
  # coded_para <- coded_para %>% dplyr::mutate(para = para)
  
  coded_para$para[i] <- para
}

# writexl::write_xlsx(coded_para, path = 'test.xlsx') ## --> works well




## detect region names at para level ---------------------------------------------------------------

coded_para <- coded_para %>%
  dplyr::rename(region_sent = region)

coded_para <- detect_region(data = coded_para, text_column = 'para') %>%
  dplyr::rename(region_para = region)
  
```


```{r - Test Count matches}

## text data
coded_count <- txt_sentence_df %>%
  dplyr::mutate(n = 0)


## Keywords list in a vector
## --> take this as an example 
k_ls <- strsplit(x = SDG13_general, split = '\\|') %>% unlist(); k_ls


## Loop and count matches for each keyword
sdg_i_str <- 'SDG13_general'
# k <- 'climat'

for (k in k_ls){                
    print(k)
    
    coded_count <- coded_count %>%
      as.data.frame() %>%
      dplyr::mutate(
        n_k    = str_count(string = statement, regex(pattern = k, ignore_case = T)),
        n      = n + n_k,
        sdgs_n = ifelse(n > 0, paste0(sdg_i_str, '-', n), '')
        ) %>%
      arrange(desc(n)) %>%
      as.data.frame()
}



sum(coded_count$n, na.rm = T)
```






## To Inspect 

  Inspect and tune mining results
  
  Manual edits?? Go back to the SDG keyword strings and edit there first. The duplicate SDGs should be the ones that are inspected to make sure that keywords are being used correctly. But overlap is okay if the sentences actually do talk about >1 SDG.

```{r - formatted xlsx}
### save all the hits to xlsx for easier inspection. 
writexl::write_xlsx(x = coded, path = './Data/data_TextMining/coded.xlsx')


### inspect/extract rows where there are more than one SDG hits. 
coded_check <- coded %>%
  dplyr::filter(nchar(sdgs) > 12) %>% # inspect > 2 SDGs
  as.data.frame()



### format the data to inspect by SDG --------------------------------------------------------------
coded_xls <- coded %>%
  dplyr::select(statement, sdgs) %>%
  dplyr::mutate(sdg = gsub(pattern = 'general', 'g', sdgs, perl = T),      ## replace 'general' with "g"
                sdg = gsub(pattern = '_[0-9a-z]{1,2}', '', sdg, perl = T), ## to get the SDG ids from target names
                sdg = gsub(pattern = '^,', '', sdg))                       ## remove the starting comma


for (i in 1:nrow(coded_xls)) {
  ## to get a list of unique SDGs
  s <- coded_xls$sdg[i] %>% strsplit(x = ., split = ',') %>% unlist() %>% unique()
  print(s)
  coded_xls$sdg_u[i] = paste(s, collapse = ',')
  
}


### --> to put 17 SDGs in columns 
#### 1. add a column with a list of 17 SDGs
coded_xls1 <- coded_xls %>%
  dplyr::mutate(test = paste('SDG', seq(1,17), collapse = ',', sep = ''))


#### 2. split the column to multiple
library(splitstackshape)
coded_xls2 <- cSplit(indt = coded_xls1, splitCols = 'test', sep = ",", direction = "wide", drop = T) %>%
  dplyr::rename(id = sdg) %>%
  dplyr::mutate(id = row_number()) ## v  = sdg_u %>% strsplit(., ',')


#### 3. Each `SDG` in a column, if match, return 1, otherwise 0
names(coded_xls2)

coded_xls3 <- coded_xls2 %>%
  gather(key = 'sdg', value = 'sdg_v', test_01:test_17) %>%
  dplyr::mutate(flag = ifelse(str_detect(string = sdg_u, pattern = paste0(sdg_v, '\\b')), 1, 0)) %>%
  dplyr::select(-sdg_v) %>%
  spread(key = 'sdg', value = 'flag') %>%
  dplyr::rename(SDG_target = sdgs) %>%
  dplyr::select(-sdg_u, -id) %>%
  as.data.frame()

## rename the column names
names(coded_xls3) <- c("Statement", "SDG_target", paste0('SDG', seq(1,17)))

writexl::write_xlsx(coded_xls3, path = paste0('./Data/data_TextMining/coded_Cemex_inspection.xlsx'))
```








## Final result

  Format to match the UNGSII dataset.
  
```
|company name| SDG ID| n_statements|

```

```{r - Stats and plot}
# get sums for each SDG
  # colSums(corpus$SDG1)


# coded_sdgs <- dplyr::pull(coded, sdgs)   ## the same as below one
coded_sdgs <- as.vector(unlist(coded['sdgs'])) %>%
  paste(sep = " ", collapse = " ")
# coded_sdgs


### table formatting ---------------------------------------------------------------------------------
coded_sdgs <- unlist(strsplit(coded_sdgs, split = "\\,")) %>% trimws();
  
coded_sdgs_df <- as.data.frame(table(coded_sdgs)) %>%
  dplyr::filter(coded_sdgs != '') %>%
  separate(col = coded_sdgs, into = c('goal', 'target_id'), sep = '_', remove = F) %>%
  dplyr::mutate(goal_id   = as.numeric(gsub("\\D", "", goal)),
                target_id = gsub('^.{3}', "", coded_sdgs)) %>%
  arrange(goal_id, target_id) %>%
  dplyr::select(1:2, goal_id, everything()) %>%
  dplyr::rename(n_statements = Freq)


coded_sdgs_df %>%
  ggplot(aes(x = fct_rev(coded_sdgs))) +
  geom_col(aes(y = n_statements), alpha = 0.6) +
  geom_text(aes(y = n_statements, label = n_statements), size = 5, color = 'red') +
  facet_wrap(~goal, scales = 'free_y') +
  coord_flip() +
  theme_bw() +
  ylab('Number of SDG statements') + xlab('')
### --> this figure only presents what were detected, but some SDGs without match won't be shown. 


### Force to list all 17 SDGs and 169 Targets ------------------------------------------------------
source('./Code/helper_UN_SDG_Target_list.R') ## --> ls_un_id; goals_ls

goals_df <- ls_un_id %>%
  dplyr::select(goalname, target_id_un, target_id_un2) %>%
  # group_by(goalname) %>%
  # arrange(goalname, target_id_un2) %>%
  dplyr::mutate(target_id_un = gsub('\\.', '_', target_id_un),
                target_id_un = paste0('SDG', target_id_un)) %>%
  dplyr::mutate(id = row_number()) %>%
  dplyr::mutate(target_id_un = factor(target_id_un, levels = unique(target_id_un)),
                target_id_un = reorder(target_id_un, id)) %>%
  as.data.frame()

### merge data 
coded_sdgs_df_format <- merge(coded_sdgs_df, goals_df, 
                        by.x = c('goal', 'coded_sdgs'), by.y = c('goalname', 'target_id_un'), all = T) %>%
  dplyr::mutate(goal = factor(goal, levels = goals_ls)) %>%
  arrange(goal, id) %>%
  dplyr::mutate(id = row_number()) %>%
  dplyr::mutate(coded_sdgs = gsub('general', 'g', coded_sdgs),
                coded_sdgs = factor(coded_sdgs, levels = unique(coded_sdgs)),
                coded_sdgs = reorder(coded_sdgs, id)) %>%
  as.data.frame()

str(coded_sdgs_df_format)

### plot
coded_sdgs_df_format %>%
  ggplot(aes(x = fct_rev(coded_sdgs))) +
  geom_col(aes(y = n_statements), alpha = 0.6) +
  geom_text(aes(y = n_statements, label = n_statements), size = 5, color = 'red') +
  facet_wrap(~goal, scales = 'free_y', ncol = 6) +
  coord_flip() +
  theme_bw() +
  ylab('Number of SDG statements') + xlab('')
fname <- paste0('./Data/data_TextMining/text_mining_figs/', company_name, '_coded_machine_update', '.jpg'); fname
ggsave(filename = fname, plot = last_plot(), width = 16, height = 9, units = 'in', dpi = 300)
```




```{r - Compare with UNGSII}
# company_name <- 'CEMEX'
xls <- paste0('./Data/data_TextMining/df_', company_name, '_reference.xlsx'); xls
human <- readxl::read_excel(xls) 

cols_selected <- names(human)[1:6]; cols_selected


human_format <- human %>%  
  ### some duplicated Target ids ---
  ungroup() %>%
  group_by(Company, iso3, goal_id, Target_id, target_id, goal) %>%
  dplyr::summarise(n_statements = sum(n_statement, na.rm = T)) %>%
  dplyr::filter(goal_id != 'SDGs') %>%
  dplyr::mutate(target = gsub('\\.', '_', Target_id),
                target = paste0('SDG', target)) %>%
  ### link with all SDG and targets
  merge(., goals_df,
        by.x = c('goal', 'target'), by.y = c('goalname', 'target_id_un'), all = T) %>%
  dplyr::mutate(goal = factor(goal, levels = goals_ls)) %>%
  arrange(goal, id) %>%
  dplyr::mutate(id = row_number()) %>%
  # arrange(goal, id) %>%
  dplyr::mutate(target = factor(target, levels = unique(target)),
                target = reorder(target, id)) %>%
  as.data.frame()

human_format %>%
  ggplot(aes(x = fct_rev(target))) +
  geom_col(aes(y = n_statements), alpha = 0.6) +
  geom_text(aes(y = n_statements, label = n_statements), size = 5, color = 'red') +
  facet_wrap(~goal, scales = 'free_y', ncol = 6) +
  coord_flip() +
  theme_bw() +
  theme(strip.background = element_rect(fill="orange")) +
  ylab('Number of SDG statements') + xlab('')
fname <- paste0('./Data/data_TextMining/text_mining_figs/', company_name, '_coded_human', '.jpg'); fname
ggsave(filename = fname, plot = last_plot(), width = 16, height = 9, units = 'in', dpi = 300)
```



```{r - ?}
# get sums for each SDG
  # colSums(corpus$SDG1)


# coded_sdgs <- dplyr::pull(coded, sdgs)   ## the same as below one
coded_sdgs <- as.vector(unlist(coded['sdgs_n'])) %>%
  paste(sep = " ", collapse = " ")

# coded_sdgs


# table formatting ---------------------------------------------------------------------------------
coded_sdgs <- unlist(strsplit(coded_sdgs, split = "\\,")) %>% trimws();
  
coded_sdgs_df <- as.data.frame(table(coded_sdgs)) %>%
  dplyr::filter(coded_sdgs != '') %>%
  separate(col = coded_sdgs, into = c('goal', 'target_id'), sep = '_', remove = F) %>%
  dplyr::mutate(goal_id   = as.numeric(gsub("\\D", "", goal)),
                target_id = gsub('^.{3}', "", coded_sdgs)) %>%
  separate(col = target_id, into = c('target_id', 'target_n'), sep = '-', remove = F) %>%
  dplyr::mutate(target_n = as.numeric(target_n),
                n_total  = Freq * target_n) %>%
  arrange(goal_id, target_id) %>%
  group_by(goal, goal_id, target_id) %>%
  dplyr::summarise(n_statements = sum(n_total, na.rm = T))  %>%

  # dplyr::select(1:2, goal_id, everything()) %>%
  # dplyr::rename(n_statements = n_total) %>%
  as.data.frame()

sum(coded_sdgs_df$n_statements)

coded_sdgs_df %>%
  ggplot(aes(x = fct_rev(target_id))) +
  geom_col(aes(y = n_statements), alpha = 0.6) +
  geom_text(aes(y = n_statements + 2, label = n_statements), size = 5, color = 'red') +
  facet_wrap(~goal, scales = 'free_y') +
  coord_flip() +
  theme_bw()
```








# --------------------------------------------------------------------------------------------------
# SI - helper code

## matching keywords and putting a word in a column.

```{r eval=FALSE, include=FALSE}
# make list of search terms
  cat_list <- c("management","managed","protected_areas",
                "reintroduction_","wilderness_areas","fallow_land",
                "forest_distance","forest_presence","habitat_filter",
                "Native_American","nature_reserves","non-hunting",
                "urban_forest","regulated_areas","introduction_locus",
                "advisories"
                )

# search and append
  vars.list.shorter$category <- ifelse(grepl(paste0(cat_list, collapse = "|"),
                                             vars.list.shorter$variable),
                                      'management/interventions',
                                      vars.list.shorter$category)
  
# inspect
  summary(as.factor(vars.list.shorter$category))
  
# get count of NAs remaining
  sum(is.na(vars.list.shorter$category))
```





## experimental stuff 

Example of a near/2 where we just want 2 words before and 2 words after the keyword.
We can use this for later. For example, trying to find specific mention of SDG1 and the terms mentioned around it.
Extract two words around the key words in both directions

```{r eval=FALSE, include=FALSE}
### USE THIS TO CLEAN UP SENTENCES 
# remove stopwords (on, the, at, etc.) from comments
  # grab stopword list from tm package
      stopwords_regex = paste(stopwords('en'), collapse = '\\b|\\b')
      stopwords_regex = paste0('\\b', stopwords_regex, '\\b')
      
  # remove stopwords
    #DOC_SI$shorter = str_replace_all(DOC_SI$keywords,stopwords_regex,'') #error
    DOC_SI$comments <- sapply(DOC_SI$comments,
                                function(x) {gsub(stopwords_regex,"",x)})
    
    

matching <- c('li', 'yi', 'ji') 
    
# empty vector
ls <- list();

# for-loop to create search pattern list
for (i in 1:length(matching)){
  
  # number of words left and right of keyword
  lookaround <- 2
  # pattern to search
    pattern <- paste0("([[a-z']]+ ){0,", lookaround, "}",
                      paste(matching[i], collapse = '|'),
                      "( [[a-z']]+){0,", lookaround, "}")
    print(pattern)
  # add to list
    ls[[i]] <- pattern
}
# combine
patterns <- do.call(rbind,ls)



# assign to object
pattern <- paste0(patterns,collapse = "|")
pattern

# add to dataframe
DOC_SI$keywords <- str_extract_all(DOC_SI$comments,
                              pattern=regex(pattern,
                                            ignore_case = TRUE,
                                            skip_word_none=TRUE #ignore punctuation
                              ),
                              "\\w+" #match any word character
                              )
```




```{r TEST look around, eval=FALSE, include=FALSE}
t <- 'SDG 13.1 is one of the targets under SDG'
word1 <- 'SDG'
word2 <- '13'
str <- as.character('\\W+(?:\\w+\\W+)')
# p <- '\bword1\W+(?:\w+\W+){1,6}?word2\b'
pat <- paste0('\b', word1, str, '{0,6}', word2, '\b') ## at least 1 word between “word1” and “word2”, and allow at most 3 words.
# pat <- '(?i)(?:\b(SDG))\\W+(?:\\w+\\W+){0,5}?\b(13)\b.*'
pat <- '(?<=SDG)\\s(?:\\w+\\s){0,2}(?=13)'
pat <- '(?<=SDG)\\W+(?:\\w+\\s\\S){0,2}(?=13)'

# (?i)(?:\b(tree)\b)(?:(?!\n)\W)+(?:\w+\W+){0,5}?\b(house)\b.*
pat
regex(pat)


grepl(pattern = regex(pat, ignore.case = TRUE), x = t, ignore.case = T, perl = T)


library(dplyr)
library(stringr)
dataframe <- data_frame(mytext = c('SD is pretty SDG my only 13',
                                   'SD is pretty SDG my only one 13',
                                   'but sometimes SDG13 is bad as well',
                                   'but sometimes sdg 13 is',
                                   'SDG one two three, SDG 13.1',
                                   'sdg13',
                                   'this is SDG13',
                                   'SDG 13'))

# dataframe
dataframe %>%  mutate(mycount = str_count(mytext, pattern = regex(pattern = pat, ignore_case = TRUE)))

```




## Keywords and corpus
```{r keywords, eval=FALSE, include=FALSE}
library(SnowballC) ## wordStem function
## We use the wordStem function of the SnowballC package that has support for the English language. This function reduces a word or a vector of words to its radical (common base form). 
stemmed_keyword1 <- wordStem("basic service", language = "english"); stemmed_keyword1
stemmed_keyword2 <- wordStem("housing", language = "english");       stemmed_keyword2
keywords <- paste(stemmed_keyword1, stemmed_keyword2, sep = '|'); keywords



text_example <- c("i am member of the XYZ association",
    "apply for our open associate position", 
    "xyz memorial lecture takes place on wednesday", 
    "vote for the most popular lecturer")

library(tm)
# Step 1: Create corpus
t <- data.frame(text_example) %>%
  mutate(doc_id = row.names(.), 
         text = text_example) %>%
  select(-1)
corpus.copy <- corpus <- tm::Corpus(DataframeSource(t))


# Step 3: Stem words in the corpus
corpus.temp <- tm_map(corpus, stemDocument, language = "english")  

inspect(corpus.temp)

# Step 4: Complete the stems to their original form
corpus.final <- tm_map(corpus.temp, stemCompletion, dictionary = corpus.copy)  

inspect(corpus.final)
```


```{r mining sentences, eval=FALSE, include=FALSE}
### example #1 -------------------------------------------------------------------------------------
text <- unlist(strsplit(text_example, split = "\\.|\\,|;")) %>% trimws(); text
text[grep(pattern = keywords, x = text, ignore.case = T)]
```





```{r NLP, eval=FALSE, include=FALSE}
### example #2 -------------------------------------------------------------------------------------
library(NLP)
library(openNLP)
library(SnowballC) ## wordStem function
## convert the text to a string. This is necessary because the openNLP package works with the String type.
text_example <- as.String(text_example)
text_example
## Next, we use the openNLP package to generate a sentence annotator that computes the annotations through a sentence detector
sent_annotator <- Maxent_Sent_Token_Annotator(); sent_annotator
annotation <- annotate(text_example, sent_annotator)
## Next, through the notes made in the text, we can extract the sentences. 
splited_text <- text_example[annotation]
splited_text

## Next, we use the grep function of the base package R to find the sentences that contain the keywords we are looking for. 
sentence_index <- grep(pattern = keywords, x = splited_text, ignore.case = T)
#output
splited_text[sentence_index]
```

