---
title: "Text_mining"
author: "Yingjie"
date: "6/17/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---


# Directories and packages

```{r include=FALSE}
### To clear your environment 
remove(list = ls())

## set work dir
path <- rstudioapi::getSourceEditorContext()$path
dir  <- dirname(rstudioapi::getSourceEditorContext()$path); dir
setwd(dir)
getwd()
dirname(dir)
setwd(dirname(dir))
getwd()

# directories for Yingjie
  dir.reports <- './Data/data_TextMining/annual_reports/'
  dir.results <- './Data/data_results/'
  dir.figures <- './Data/figures/'
  dirpath     <- './Data/data_TextMining/annual_reports/pdf_coded_human/'

# directories for Veronica
  # dir.reports <- '../Data/data_TextMining/annual_reports/' # VF added another '.'
  # dir.results <- '../Data/data_results/'                   # VF added another '.'
  # dir.figures <- '../Data/figures/';      dir.figures      # VF added another '.'

# load packages
  source('./Code/_packages.R')

  library(tm)        # text mining: readPDF(), Corpus()
  library(tidyverse) # piping and wrangling
  library(tabulizer) # importing PDFs
  #library(remotes)  # installing from remote repositories
```


## Helper data
```{r - UN SGD target list}
source('./Code/helper_UN_SDG_Target_list.R') ## --> ls_un_id; goals_ls

goals_df <- ls_un_id %>%
  dplyr::select(goalname, target_id_un, target_id_un2) %>%
  # group_by(goalname) %>%
  # arrange(goalname, target_id_un2) %>%
  dplyr::mutate(target_id_un = gsub('\\.', '_', target_id_un),
                target_id_un = paste0('SDG', target_id_un)) %>%
  dplyr::mutate(id = row_number()) %>%
  dplyr::mutate(target_id_un = factor(target_id_un, levels = unique(target_id_un)),
                target_id_un = reorder(target_id_un, id)) %>%
  as.data.frame()

## save to `SDG_TM` for R package development
fname <- paste0(dirname(getwd()), '/SDG_TM/data/goals_df.RData'); fname
save(goals_df, file = fname)
```



# Data imports

## PDF to clean TXT
  
  Conversion to text --> and save .txt with name from list and move to another folder. 
  
```{r eval=FALSE, include=FALSE}

### Custom function
convertpdf2txt <- function(dirpath){
  files <- list.files(dirpath, pattern = '*.pdf$', ignore.case = T, full.names = T); files
  for (pdf in files) {
    
    ## --> read and clean the pdf ---------------------------------------------------------------- #
    txt <- tabulizer::extract_text(file = pdf) %>%
      iconv("UTF8", "ASCII", "") %>% # change encoding
      paste(sep = " ") %>%
      stringr::str_replace_all(fixed("\n"), " ") %>% # erase new lines
      stringr::str_replace_all(fixed("\r"), " ") %>% # erase carriage return
      stringr::str_replace_all(fixed("\t"), " ") %>% # erase tabs
      stringr::str_replace_all(fixed("\""), " ") %>% # erase "
      paste(sep = " ", collapse = " ") %>%
      stringr::str_squish() %>%             # remove leading & trailing whitespace, and repeated whitespace inside a string
      stringr::str_replace_all("- ", "")    # fix incomplete words continuing to next line
    
    ## --> get company name 
    company_name <- str_split(string = basename(pdf), pattern = "--", n = 2) %>% unlist()
    
    ## --> save as local TXT file 
    # TXTname <- paste0(dirpath, company_name[1], '.txt'); print(TXTname)
    # writeLines(txt, TXTname)
    ## --> save as r data 
    fname <- paste0(dirpath, 'TXT/', company_name[1], '.RData'); print(fname)
    save(txt, file = fname)
    
    ## --> text to DF ---------------------------------------------------------------------------- #
    # separate the large character chunk to short sentences by
    #    '.' (period), ';' (semicolon), ':' (colon), and '/ ' (slash with space)
    txt_sentence <- unlist(strsplit(txt, split = "\\. |\\; |\\/ |\\: ")) %>% trimws()      ## without ',' (comma)
    txt_sentence_df <- data.frame(statement = txt_sentence) %>%
      dplyr::mutate(id = row.names(.) %>% as.numeric(),
                    statement = as.character(statement)) %>%
      as.data.frame()
    ## --> save as r data
    fname <- paste0(dirpath, 'DF/',  company_name[1], '.RData'); print(fname)
    save(txt_sentence_df, file = fname)
    }
}

### test code
convertpdf2txt(dirpath = dirpath)
```




# 1. Load cleaned data

  This requires pattern searching where every sentence has to end with a period (.) 
  Limitations/problems for: figure text, bullet points, anything without a period.

```{r}
dirpath <- './Data/data_TextMining/annual_reports/pdf_coded_human/'

## 1. load the `txt` data
# ls <- list.files(path = paste0(dirpath, 'TXT/'), pattern = '*.RData$', ignore.case = T, full.names = T); ls


## 2. load the `txt to df` data
ls <- list.files(path = paste0(dirpath, 'DF/'), pattern = '*.RData$', ignore.case = T, full.names = T); ls

# f <- ls[1]
# load(f)

```



# 2. SDG search terms

  This collection includes terms that are *directly* related to SDGs, i.e., if companies specifically mention SDG ids (e.g., 'SDG 13'), or the target or indicator ids (e.g., SDG 13.1.a). 
  
|SDG_id       |SDG_keywords     |
|SDG1_1       |keywords here    |
  
```{r - Collection - direct commit}
source('./Code/helper_SDG_search_terms.R')

SDG_keys <- rbind(goal_keys, target_keys)

SDG_ls_str <- SDG_keys$SDG_id %>% as.character(); SDG_ls_str

```



  This collection includes terms that are *indirectly* related to SDGs, i.e., the terms are constructed based on the alignment to the description and meanings of each SDG or Target. 
  
```{r - Collection - indrect commit}
source('./Code/helper_SDG_search_terms.R')

### bind these vectors and make it a dataframe to work from ----------------------------------------
SDG_ls_str <- ls(pattern = "SDG[0-9].*") %>% sort(); SDG_ls_str

SDG_ls_str <- grep("['xyzw]", SDG_ls_str, value = TRUE, invert = TRUE) # invert = TRUE means to return the values that were not matched.
SDG_ls_str

SDG_keys <- data.frame()  

for (i in 1:length(SDG_ls_str) ) {
  # print(i)
  sdg_i_str <- SDG_ls_str[i]
  sdg_i_obj <- get(sdg_i_str)
  df_i <- data.frame(SDG_id       = sdg_i_str, 
                     SDG_keywords = sdg_i_obj)
  SDG_keys <- rbind(SDG_keys, df_i) %>%
    dplyr::mutate(SDG_id       = as.character(SDG_id),
                  SDG_keywords = as.character(SDG_keywords))
}

fname <- paste0('./Data/', 'SDG_keys.RData'); fname
save(SDG_keys, file = fname)


## save to `SDG_TM` for R package development
fname <- paste0(dirname(getwd()), '/SDG_TM/data/SDG_keys.RData'); fname
save(SDG_keys, file = fname)
```




# 3. Code TM  

  To match the keywords to each corpus and format results

  Add columns to see how many have comments using these terms.
  Here are the options:
  1. for every row in the corpus (ideally only 1 sentence in each row), have a column 1-17 and 1/0 or y/n if matching the SDG.
    - this would be a for-loop and i 1:17 is linked to the columns being filled
  2. for entire corpus, extract rows (ideally only 1 sentence at a time) that match only 1 SDG.
    - this would be a for-loop and i 1:17 is a new vector to be added to a list (17 of them)

## To code
```{r - Function 1 - code}

## 1. This function will be used to identify matches ############################################# #

# THIS CODE IS TO IDENTIFY MATCHING ROWS, BUT IT DOES NOT EXTRACT SENTENCES
# in the original dataframe, if it matches, then in a new column, say yes; if not, say no.

func_tm_code <- function(txt_sentence_df) {
  
  code <- txt_sentence_df %>% 
    dplyr::mutate(#match   = 0,      
                  sdgs    = '', ## for later use, to append data to this column
                  n_total = 0,
                  sdgs_n  = '')
  
  for (i in 1:nrow(SDG_keys)){                ## all SDG indicators
      sdg_i_str <- SDG_keys$SDG_id[i]         ## the SDG id name
      sdg_i_obj <- SDG_keys$SDG_keywords[i]   ## the corresponding SDG search term list
      
      print(sdg_i_str)
      # print(sdg_i_obj)
      
      code <- code %>% as.data.frame() %>%
        ## at the sentence level - count once ----------------------
        dplyr::mutate(
          match = ifelse(
            grepl(pattern = sdg_i_obj, x = statement, ignore.case = T, perl = T), 1, 0))  %>% ## yes-1 or no-0 if they match
        dplyr::mutate(sdgs = ifelse(match > 0, paste0(sdgs, ',', sdg_i_str), sdgs)) %>%
        
        ## at the sentence level - count all matches ---------------
        dplyr::mutate(
          n       = str_count(string = statement, regex(pattern = sdg_i_obj, ignore_case = T)),
          n_total = n_total + n,
          sdgs_n  = ifelse(n > 0, paste0(sdgs_n, ',', sdg_i_str, '-', n), sdgs_n)) %>%
        as.data.frame()
  }
  
  
  ### sort from most SDG hits to least (or, none)
  coded <- code %>% arrange(desc(nchar(sdgs)), id)
  
  ### save all the hits to xlsx for easier inspection. 
  # fname <- paste0(dirpath, 'DF_coded/', com_name, '_coded.xlsx'); fname
  # writexl::write_xlsx(x = coded, path = fname)
  fname <- paste0(dirpath, 'DF_coded/', com_name, '_coded.csv'); fname
  readr::write_csv(x = coded, file = fname)
  fname <- paste0(dirpath, 'DF_coded/', com_name, '_coded.RData'); fname
  save(coded, file = fname)
  
  return(coded)

}
```




  To Inspect 

  Inspect and tune mining results
  
  Manual edits?? Go back to the SDG keyword strings and edit there first. The duplicate SDGs should be the ones that are inspected to make sure that keywords are being used correctly. But overlap is okay if the sentences actually do talk about >1 SDG.
```{r}

```




```{r - Function 2 - format results}

func_format <- function(coded) {
  
  ### --> pull out the column with coded results
  # coded_sdgs <- dplyr::pull(coded, sdgs)   ## the same as below one
  coded_sdgs <- as.vector(unlist(coded['sdgs'])) %>%
    paste(sep = " ", collapse = " ")
  # coded_sdgs
  
  
  ### --> format it as a DF 
  coded_sdgs <- unlist(strsplit(coded_sdgs, split = "\\,")) %>% trimws();
    
  coded_sdgs_df <- as.data.frame(table(coded_sdgs)) %>%
    dplyr::filter(coded_sdgs != '') %>%
    separate(col = coded_sdgs, into = c('goal', 'target_id'), sep = '_', remove = F) %>%
    dplyr::mutate(goal_id   = as.numeric(gsub("\\D", "", goal)),
                  target_id = gsub('^.{3}', "", coded_sdgs)) %>%
    arrange(goal_id, target_id) %>%
    dplyr::select(1:2, goal_id, everything()) %>%
    dplyr::rename(n_statements = Freq)
  
  
  
  ### --> The above data only presents what were detected, but some SDGs without match won't be shown. 
  ### --> Force to list all 17 SDGs and 169 Targets

  
  ### --> merge data 
  coded_sdgs_df_format <- merge(coded_sdgs_df, goals_df, 
                          by.x = c('goal', 'coded_sdgs'), by.y = c('goalname', 'target_id_un'), all = T) %>%
    dplyr::mutate(goal = factor(goal, levels = goals_ls)) %>%
    arrange(goal, id) %>%
    dplyr::mutate(id = row_number()) %>%
    dplyr::mutate(coded_sdgs = gsub('general', 'g', coded_sdgs),
                  coded_sdgs = factor(coded_sdgs, levels = unique(coded_sdgs)),
                  coded_sdgs = reorder(coded_sdgs, id)) %>%
    as.data.frame()
  
  # str(coded_sdgs_df_format)
  return(coded_sdgs_df_format)

}

```



## Batch run
```{r}

dfs <- data.frame()

for (f in ls) {
  # print(f)
  com_name <- gsub('\\.RData', '', basename(f)); print(com_name)
  load(f)

  coded <- func_tm_code(txt_sentence_df = txt_sentence_df)

  d <- func_format(coded = coded)
  d$company = com_name

  dfs <- rbind(dfs, d)

}


### save all the hits to xlsx for easier inspection. 
fname <- paste0(dirpath, 'DF_coded_results/coded_dfs.xlsx');  fname
writexl::write_xlsx(x = dfs, path = fname)
fname <- paste0(dirpath, 'DF_coded_results/coded_dfs.RData'); fname
save(dfs, file = fname)
```





# 4. Compare to Human

## machine-coded 

aggregate
```{r}

## load data
fname <- paste0(dirpath, 'DF_coded_results/coded_dfs.RData'); fname
load(fname)

## machine-coded data
dfs_m <- dfs %>%
  dplyr::rename(target = coded_sdgs)


## company list
com_ls <- unique(dfs_m$company); com_ls

```





## human coded at UNGSII
```{r }

## human-coded data
fname <- paste0(dir.results, 'df.RData'); fname
load(fname)

dfs_human <- df

names(dfs_h)


## a subset of data
# company_name <- 'Cemex'
# xls <- paste0('./Data/data_TextMining/df_', company_name, '_reference.xlsx'); xls
# human <- readxl::read_excel(xls) 
# cols_selected <- names(human)[1:6]; cols_selected


dfs_h <- dfs_human %>%  
  dplyr::filter(Company %in% com_ls) %>%
  ### some duplicated Target ids ------------------------------
  ungroup() %>%
  group_by(Company, iso3, goal_id, Target_id, goal) %>%
  dplyr::summarise(n_statements = sum(n_statement, na.rm = T)) %>%
  dplyr::filter(goal_id != 'SDGs') %>%
  dplyr::mutate(target = gsub('\\.', '_', Target_id),
                target = paste0('SDG', target)) %>%
  ### link with all SDG and targets ---------------------------
  merge(., goals_df,
        by.x = c('goal', 'target'), by.y = c('goalname', 'target_id_un'), all = T) %>%
  dplyr::mutate(goal = factor(goal, levels = goals_ls)) %>%
  arrange(goal, id) %>%
  dplyr::mutate(id = row_number()) %>%
  # arrange(goal, id) %>%
  dplyr::mutate(target = factor(target, levels = unique(target)),
                target = reorder(target, id)) %>%
  dplyr::rename_all(tolower) %>%
  as.data.frame()
```


## compare
```{r}
names(dfs_m)
names(dfs_h_format)


dfs_m_format <- dfs_m %>% 
  dplyr::select(company, goal, target, n_statements) %>%
  group_by(company, goal, target) %>%
  dplyr::summarise(n = sum(n_statements, na.rm = T))%>%
  dplyr::mutate(coder = 'machine')

dfs_h_format <- dfs_h %>% 
  dplyr::select(company, goal, target, n_statements) %>%
  group_by(company, goal, target) %>%
  dplyr::summarise(n = sum(n_statements, na.rm = T)) %>%
  dplyr::mutate(coder = 'human')

dfs_2 <- rbind(dfs_m_format, dfs_h_format) %>%
  dplyr::filter(!is.na(company))
```





```{r - target level}
dfs_2_w <- dfs_2 %>%
  dplyr::filter(str_detect(target, '_g', negate = T)) %>%  ## remove SDG general 
  spread(key = 'coder', value = 'n')


### plot correlation 
dfs_2_w %>%
  ggplot(aes(x = human, y = machine, color = company)) +
  geom_point(show.legend = F) +
  geom_smooth(method = 'loess', formula = y~x, show.legend = F) +
  scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
                labels = trans_format("log10", math_format(10^.x))) +
  scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
                labels = trans_format("log10", math_format(10^.x))) +
  facet_wrap(~company, scales = 'free') +
  theme_bw()


fname <- paste0('./Data/data_TextMining/text_mining_figs/', 'compare_human_machine_target1.png'); fname
ggsave(filename = fname, plot = last_plot(), width = 12, height = 9, units = 'in', dpi = 300)

```



```{r - goal level}

dfs_2_w_goal <- dfs_2 %>%
  dplyr::filter(str_detect(target, '_g', negate = T)) %>%  ## remove SDG general 
  ungroup() %>%
  group_by(company, goal, coder) %>%
  dplyr::summarise(n = sum(n, na.rm = T)) %>%
  spread(key = 'coder', value = 'n') %>%
  as.data.frame()


### plot correlation 
dfs_2_w_goal %>%
  ggplot(aes(x = human, y = machine, color = company)) +
  geom_point(show.legend = F) +
  geom_smooth(method = 'loess', formula = y~x, show.legend = F) +
  scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
                labels = trans_format("log10", math_format(10^.x))) +
  scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
                labels = trans_format("log10", math_format(10^.x))) +
  geom_abline(slope = 1, linetype = 'dashed', color = 'red', size = 1, show.legend = F) +
  facet_wrap(~company, scales = 'free') +
  theme_bw()

fname <- paste0('./Data/data_TextMining/text_mining_figs/', 'compare_human_machine_goal_log.png'); fname
ggsave(filename = fname, plot = last_plot(), width = 12, height = 9, units = 'in', dpi = 300)
```





```{r - single company}
company_name <- 'Cemex'

### machine ----------------------------------------
dfs_m %>%
  dplyr::filter(company == company_name) %>%
  dplyr::filter(str_detect(target, '_g', negate = T)) %>%  ## remove SDG general 
  ggplot(aes(x = fct_rev(target))) +
  geom_col(aes(y = n_statements), alpha = 0.6) +
  geom_text(aes(y = n_statements, label = n_statements), size = 5, color = 'red') +
  facet_wrap(~goal, scales = 'free_y', ncol = 6) +
  coord_flip() +
  theme_bw() +
  # ggtitle(company_name) +
  ylab('Number of SDG statements') + xlab('')
fname <- paste0('./Data/data_TextMining/text_mining_figs/', company_name, '_coded_machine1.png'); fname
ggsave(filename = fname, plot = last_plot(), width = 16, height = 9, units = 'in', dpi = 300)



### human ------------------------------------------
dfs_h %>%
  dplyr::filter(company == company_name) %>%
  ggplot(aes(x = fct_rev(target))) +
  geom_col(aes(y = n_statements), alpha = 0.6) +
  geom_text(aes(y = n_statements, label = n_statements), size = 5, color = 'red') +
  facet_wrap(~goal, scales = 'free_y', ncol = 6) +
  coord_flip() +
  theme_bw() +
  # ggtitle(company_name) +
  theme(strip.background = element_rect(fill="orange")) +
  ylab('Number of SDG statements') + xlab('')
fname <- paste0('./Data/data_TextMining/text_mining_figs/', company_name, '_coded_human1.png'); fname
# ggsave(filename = fname, plot = last_plot(), width = 16, height = 9, units = 'in', dpi = 300)
```









```{r - ?}
# get sums for each SDG
  # colSums(corpus$SDG1)


# coded_sdgs <- dplyr::pull(coded, sdgs)   ## the same as below one
coded_sdgs <- as.vector(unlist(coded['sdgs_n'])) %>%
  paste(sep = " ", collapse = " ")

# coded_sdgs


# table formatting ---------------------------------------------------------------------------------
coded_sdgs <- unlist(strsplit(coded_sdgs, split = "\\,")) %>% trimws();
  
coded_sdgs_df <- as.data.frame(table(coded_sdgs)) %>%
  dplyr::filter(coded_sdgs != '') %>%
  separate(col = coded_sdgs, into = c('goal', 'target_id'), sep = '_', remove = F) %>%
  dplyr::mutate(goal_id   = as.numeric(gsub("\\D", "", goal)),
                target_id = gsub('^.{3}', "", coded_sdgs)) %>%
  separate(col = target_id, into = c('target_id', 'target_n'), sep = '-', remove = F) %>%
  dplyr::mutate(target_n = as.numeric(target_n),
                n_total  = Freq * target_n) %>%
  arrange(goal_id, target_id) %>%
  group_by(goal, goal_id, target_id) %>%
  dplyr::summarise(n_statements = sum(n_total, na.rm = T))  %>%

  # dplyr::select(1:2, goal_id, everything()) %>%
  # dplyr::rename(n_statements = n_total) %>%
  as.data.frame()

sum(coded_sdgs_df$n_statements)

coded_sdgs_df %>%
  ggplot(aes(x = fct_rev(target_id))) +
  geom_col(aes(y = n_statements), alpha = 0.6) +
  geom_text(aes(y = n_statements + 2, label = n_statements), size = 5, color = 'red') +
  facet_wrap(~goal, scales = 'free_y') +
  coord_flip() +
  theme_bw()
```
