---
title: "Text_mining"
author: "Yingjie"
date: "6/17/2021"
output: html_document
editor_options: 
  chunk_output_type: inline
---


# Dir and packages

```{r include=FALSE}
### To clear your environment 
remove(list = ls())

## set work dir
getwd()

# directories
source('./Code/_directories.R')

# load packages
source('./Code/_packages.R')

library(tm)        # text mining: readPDF(), Corpus()
library(tabulizer) # importing PDFs

## for parallel computing
library(parallel)
library(doParallel)
library(foreach)
  
today <- format(Sys.time(), "%Y%m%d_%H%M"); today
```



## Input and output directories

### Original project 

```{r}

## input directory of the downloaded PDF data
dir_pdf <- paste0(dir.reports, 'pdf_coded_human/')



## output directory of the converted PDF data
dir_txt <- paste0(dir.reports, 'pdf_coded_human/DF/')           #' not using `tokenize_sentences()`
dir_txt <- paste0(dir.reports, 'pdf_coded_human/DF_tokenize/')

```



### SSFP project 

```{r}
## 
dir_ssfp <- 'G:/Shared drives/gdrive/_paper/SDGs/SDGs_Corporations_g/'
  
dir_pdf <- paste0(dir_ssfp, 'data/', 'data_pdf_Edmund')
dir_txt <- paste0(dir_ssfp, 'data/', 'data_pdf_Edmund/DF_tokenize/')

```


# PDF to clean TXT
  
  Conversion to text --> and save .txt with name from list and move to another folder. 
  
  (1) get the list of the downloaded PDFs. 
  

## PDF data
  
```{r - 356 company}

## read the company information list from XLS file. 
f <- paste0(dir.raw, "com_list_HumanCoded_URL.xlsx")
com_download <- readxl::read_excel(f) %>%
  dplyr::filter(str_starts(string = url_collection, pattern = "NA", negate = T))
com_download_ls <- unique(com_download$Company)


## get the PDF names of all the downloaded company 
files <- list.files(dir_pdf, pattern = '*.pdf$', ignore.case = T, full.names = T, recursive = F); #files
com_name_ls <- gsub("\\--.*", "", basename(files))

cat('There are', length(files), "PDF reports.\n"); ## 356


## identify the difference between the two list -- in case any reports are missing
a <- com_download_ls
b <- com_name_ls
setdiff(a, b)
setdiff(b, a)
union(setdiff(a,b), setdiff(b,a)) %>% sort()
```


```{r - 146 not human-coded, eval=FALSE, include=FALSE}

### for the not-human-coded PDF
files <- list.files(path = paste0(dir.reports, 'pdf_not_coded'), 
                    pattern = '*.pdf$', ignore.case = T, full.names = T, recursive = F); #files
com_name_ls <- gsub("\\--.*", "", basename(files))

cat('\n There are', length(files), "PDF reports.") ## 146 --> 394


### count how many companies have more than one documents --------------------------------
n_unique <- com_name_ls %>% unique() %>% length() 
cat('\n There are', n_unique, 'unique companies.')

cat('\n There are', (length(files)-n_unique), 'unique companies.')
```


## Batch convert PDF to text sentences
  
```{r - Batch Convert, eval=FALSE, include=FALSE}

### Custom function
source('./code/function_pdf2text.R') # `pdf2text`


## initially, this is blank
company_name_checker <- '' 

### loop all the PDF ---------------------------------------------------------------------
for (pdf in files) {
  
  ## --> get company name 
  company_name <- str_split(string = basename(pdf), pattern = "--", n = 2) %>% unlist()
  company_name <- company_name[1]
  print(company_name)

  
  ## --> read and clean the pdf ---------------------------------------------------------#
  txt_sentence_df <- 
    # pdf2text(pdf) %>%             # update on 5/19/2022
    pdf2text_tokenize(pdf) %>%    # update on 5/19/2025
    ## remove sentences that are too short
    dplyr::filter(nchar(statement) > 5) %>%
    ## replace the company names to avoid string mismatch
    dplyr::mutate(statement = gsub(pattern = paste0("\\b", company_name, "\\b"), "This company", statement)) %>%
    ## again, exclude sentences that are too short
    dplyr::filter(nchar(statement) > 5) %>%
    
    ## remove sentences that have too many short words, likely due to format issues
    dplyr::filter(short_word_count < 500) %>%
    
    ## remove repeated sentences, most of which come from 'Header' and 'Footer', adding many noise and computation pressure
    dplyr::distinct(statement, .keep_all = T) %>%
    as.data.frame()
  
  
  ## --> if new file is for the same company, then append the data
  if (company_name == company_name_checker) {
    cat('\t More than one, need to append data.\t\t', company_name, '\n') 
    txt_sentence_df <- rbind(txt_sentence_df, txt_sentence_df_forAppend)
  } else {
    txt_sentence_df <- txt_sentence_df
  }
  
  
  ## --> save as R data
  fname <- paste0(dir_txt,  company_name[1], '.RData'); print(fname)
  save(txt_sentence_df, file = fname)
  
  
  ## --> save as CSV data
  fname <- paste0(dir_txt,  company_name[1], '.csv'); print(fname)
  readr::write_csv(txt_sentence_df, file = fname)

  
  ## --> update the PDF list, if error occurs
  remove <- pdf
  files  <- setdiff(files, remove)
  company_name_checker      <- company_name     ## keep this information for checking the next loop
  txt_sentence_df_forAppend <- txt_sentence_df  ## keep this data in case we need to append the multiple files for 1 company
  
  
  ## --> To clear up the memory
  # gc()
}

```


**To-do**: (if any files failed - need to re-process these files)
  "Kia Motors"
  
  ## cannot open compressed file
  "Koç Holding"           
  "Société Générale"
  





```{r - Make a copy to project dir, eval=FALSE, include=FALSE}
# ## for data 1
# files <- list.files(path = paste0(dir.reports, 'pdf_coded_human/DF'), pattern = '*.RData$', full.names = T); #files
# toDir <- gsub('D:/_papers/SDGs/SDGs_Corporations/', './', files); #toDir
# file.copy(from = files, to = toDir, overwrite = T, copy.date = T)
# 
# 
# ## for data 2
# files <- list.files(path = paste0(dir.reports, 'pdf_not_coded/DF'), pattern = '*.RData$', full.names = T); #files
# toDir <- gsub('D:/_papers/SDGs/SDGs_Corporations/', './', files); #toDir
# file.copy(from = files, to = toDir, overwrite = T, copy.date = T)
```

