---
title: "Text_mining"
author: "Yingjie"
date: "6/17/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---


# Dir and packages

```{r include=FALSE}
### To clear your environment 
remove(list = ls())

## set work dir
path <- rstudioapi::getSourceEditorContext()$path
dir  <- dirname(rstudioapi::getSourceEditorContext()$path); dir
setwd(dir)
getwd()
dirname(dir)
setwd(dirname(dir))
getwd()

# directories for Yingjie
  dir.reports <- './Data/data_TextMining/annual_reports/'
  dir.results <- './Data/data_results/'
  dir.figures <- './Data/figures/'
  dirpath     <- './Data/data_TextMining/annual_reports/pdf_coded_human/'

# directories for Veronica
  # dir.reports <- '../Data/data_TextMining/annual_reports/' # VF added another '.'
  # dir.results <- '../Data/data_results/'                   # VF added another '.'
  # dir.figures <- '../Data/figures/';      dir.figures      # VF added another '.'

# load packages
  source('./Code/_packages.R')

  library(tm)        # text mining: readPDF(), Corpus()
  library(tidyverse) # piping and wrangling
  library(tabulizer) # importing PDFs
  #library(remotes)  # installing from remote repositories
  
today <- format(Sys.time(), "%Y%m%d_%H%M"); today
```


## Helper data
```{r - UN SGD target list}
source('./Code/helper_UN_SDG_Target_list.R') ## --> ls_un_id; goals_ls

goals_df <- ls_un_id %>%
  dplyr::select(goalname, target_id_un, target_id_un2) %>%
  # group_by(goalname) %>%
  # arrange(goalname, target_id_un2) %>%
  dplyr::mutate(target_id_un = gsub('\\.', '_', target_id_un),
                target_id_un = paste0('SDG', target_id_un)) %>%
  dplyr::mutate(id = row_number()) %>%
  dplyr::mutate(target_id_un = factor(target_id_un, levels = unique(target_id_un)),
                target_id_un = reorder(target_id_un, id)) %>%
  as.data.frame()

## save to `SDG_TM` for R package development
fname <- paste0(dirname(getwd()), '/SDG_TM/data/goals_df.RData'); fname
save(goals_df, file = fname)
```



# 1. PDF to clean TXT
  
  Conversion to text --> and save .txt with name from list and move to another folder. 
  
  (1) get the list of the downloaded PDFs. 
```{r}
## read the company information list from XLS file. 
com_download <- readxl::read_excel("./Data/data_TextMining/com_list_HumanCoded_URL.xlsx") %>%
  dplyr::filter(str_starts(string = url, pattern = "NA", negate = T))
com_download_ls <- unique(com_download$Company)


## get the PDF names of all the downloaded company 
files <- list.files(dirpath, pattern = '*.pdf$', ignore.case = T, full.names = T, recursive = F); #files
com_name_ls <- gsub("\\--.*", "", basename(files))

cat('There are', length(files), "PDF reports.");


## identify the difference between the two list
a <- com_download_ls
b <- com_name_ls
setdiff(a, b)
setdiff(b, a)
union(setdiff(a,b), setdiff(b,a)) %>% sort()
```



  (2) Convert each PDF to text format
```{r eval=FALSE, include=FALSE}

### Custom function
source('./Code/function_pdf2text.R') # `pdf2text`



### loop all the PDF
for (pdf in files) {
  
  ## --> get company name 
  company_name <- str_split(string = basename(pdf), pattern = "--", n = 2) %>% unlist()
  company_name <- company_name[1]
  print(company_name)
  
  ## --> read and clean the pdf ---------------------------------------------------------------- #
  txt_sentence_df <- pdf2text(filename = pdf) %>%
    ## remove sentences that are too short
    dplyr::filter(nchar(statement) > 5) %>% 
    ## replace the company names to avoid string mismatch 
    dplyr::mutate(statement = gsub(pattern = paste0("\\b", company_name, "\\b"), "XXXNAME", statement)) %>%
    ## again, exclude sentences that are too short
    dplyr::filter(nchar(statement) > 5) %>% 
    ## remove repeated sentences, most of which come from 'Header' and 'Footer', adding many noise and computation pressure
    dplyr::distinct(statement, .keep_all = T) %>%
    as.data.frame()
  
  ## --> save as r data
  fname <- paste0(dirpath, 'DF/',  company_name[1], '.RData'); print(fname)
  save(txt_sentence_df, file = fname)
  
  ## --> update the PDF list, if error occurs
  remove <- pdf
  files <- setdiff(files, remove)
  
  ## --> To clear up the memory
  gc()
}

```



  (3) Run this chunk if any files failed - need to re-read in the list. 

```{r eval=FALSE, include=FALSE}
# files_todo <- c()

files_todo <- c(
  "Akzo Nobel"
  # "Aegon" ## need to use "https://smallpdf.com/unlock-pdf" to unlock this file. 
  # "Assicurazioni Generali",
  # "Associated British Foods",
  # "Banpu",
  # "BCE",
  # "Caixa Bank",
  # "Capricorn Investment Group", "Cardinal Health", "Colgate-Palmolive", "Commonwealth Bank of Australia", 
  # "Minas Buenaventura", "Deutsche Telekom", "Gerdau", "Hermes", "Hindustan Unilever", "Julius"
  )


for (i in files_todo) {
  pdf <- list.files(dirpath, pattern = i, ignore.case = T, full.names = T, recursive = F); print(pdf)
  
  ## --> get company name 
  company_name <- str_split(string = basename(pdf), pattern = "--", n = 2) %>% unlist()
  company_name <- company_name[1]
  print(company_name)
  
  ## --> read and clean the pdf ---------------------------------------------------------------- #
  txt_sentence_df <- pdf2text(filename = pdf)
  
  ## --> save as r data
  fname <- paste0(dirpath, 'DF/',  company_name[1], '.RData'); print(fname)
  save(txt_sentence_df, file = fname)
  
  ## --> update the PDF list, if error occurs
  remove <- pdf
  files <- setdiff(files, remove)
  
  ## --> To clear up the memory
  gc()
  
}

```






# 2. Detect SDGs  

  To match the keywords to each corpus and format results

  The analysis will return the number of commitments to different SDGs by sentence. This requires pattern searching where every sentence has to end with a period (.). Limitations/problems for: figure text, bullet points, anything without a period.
  

## 2.1. Load cleaned reports

  **Choose one of the following as input**

```{r - 350 + reports with human data, eval=FALSE, include=FALSE}
dir_input <- './Data/data_TextMining/annual_reports/pdf_coded_human/'

## 1. load the `txt` data
# ls <- list.files(path = paste0(dir_input, 'TXT/'), pattern = '*.RData$', ignore.case = T, full.names = T); ls

## 2. load the `txt to df` data
ls <- list.files(path = paste0(dir_input, 'DF/'), pattern = '*.RData$', ignore.case = T, full.names = T); #ls

cat('There are', ls %>% length(), 'corporate reports were converted.')
```



```{r - Test on top 20, eval=FALSE, include=FALSE}
ls[1]
fname <- paste0('./Data/data_TextMining/database/', 'ls_com_top20.RData'); fname
load(fname)
selected <- paste(ls_com_top20, collapse = "|")

ls <- str_subset(string = ls, pattern = selected)
ls <- ls[1:10]
```



```{r - 100 + reports without human data, eval=FALSE, include=FALSE}
dir_input <- paste0(dir.reports, "pdf_not_coded/"); dir_input
ls  <- list.files(path = paste0(dir_input, 'DF/'), pattern = '*.RData$', ignore.case = T, full.names = T); #ls

cat('There are', ls %>% length(), 'corporate reports were converted.')
```










## 2.2. Load SDG search terms

  These SDG search terms can be *direct mention*, such as "SDG 1", "SDG 2", "SDG 1.2", "SDG 1.a", or *indirect mention*.  

```{r}
fname <- paste0('./Data/data_TextMining/database/', 'SDG_keys.RData'); fname
load(fname) ## --> SDG_keys_drc, SDG_keys_indrc, SDG_keys

```


  

## 2.3. To detect 

  For every row in the corpus (ideally only 1 sentence in each row), have a column 1-17 and 1/0 or y/n if matching the SDG. This would be a for-loop and i 1:17 is linked to the columns being filled
    
```{r - run, eval=FALSE, include=FALSE}
## load the function
source('./Code/function_sdg_detector.R') ## `sdg_detector()`

## loop data
for (f in ls) {
  print(f)
  # ## --> get company name
  company_name <- gsub(".RData", "", basename(f)); print(company_name)
  df <- get(load(f))
  
  coded <- sdg_detector(df = df)
  
  ### save all the hits to xlsx for easier inspection. 
  # fname <- paste0(dir_input, 'DF_coded/', company_name, '_coded.xlsx'); fname
  # writexl::write_xlsx(x = coded, path = fname)
  # fname <- paste0(dir_input, 'DF_coded/', company_name, '_coded.csv'); fname
  # readr::write_csv(x = coded, file = fname)
  fname <- paste0(dir_input, 'DF_coded/', company_name, '_coded.RData'); fname
  save(coded, file = fname)
  
  ## --> To clear up the memory for next loop
  gc()
}

```





```{r - run - parallel}
## load the function
source('./Code/function_sdg_detector.R') ## `sdg_detector()`

## set up parallel
library(parallel)
library(doParallel)
library(foreach)
detectCores()
detectCores(logical = FALSE)  ## Same answer as before on some systems?
## returns the number of available hardware threads, and if it is FALSE, returns the number of physical cores
n_cores <- detectCores(logical = TRUE)  
n_cores
cl <- makeCluster(n_cores-1)  
doParallel::registerDoParallel(cl)   # use multicore, set to the number of our cores

## get the total number of data files
n <- length(ls); n

## run parallel
system.time({
  foreach (i=1:n, .packages = c("dplyr", "stringr")) %dopar% {
    f <- ls[i]; #f
    ## --> get company name
    company_name <- gsub(".RData", "", basename(f)); print(company_name)
    df <- get(load(f))
    
    coded <- sdg_detector(df = df)

    fname <- paste0(dir_input, 'DF_coded/', company_name, '_coded.RData'); #fname
    save(coded, file = fname)
    
    ## --> To clear up the memory for next loop
    gc()
  }
})


## When you're done, clean up the cluster
stopImplicitCluster()
```



  To Inspect 

  Inspect and tune mining results
  
  Manual edits. Go back to the SDG keyword strings and edit there first. The duplicate SDGs should be the ones that are inspected to make sure that keywords are being used correctly. But overlap is okay if the sentences actually do talk about >1 SDG.
```{r}

```



## 2.4. Format results
```{r - function}

func_format <- function(coded) {
  
  ### --> pull out the column with coded results
  # coded_sdgs <- dplyr::pull(coded, sdgs)   ## the same as below one
  coded_sdgs <- as.vector(unlist(coded['sdgs'])) %>%
    paste(sep = " ", collapse = " ")
  # coded_sdgs
  
  
  ### --> format it as a DF 
  coded_sdgs <- unlist(strsplit(coded_sdgs, split = "\\,")) %>% trimws();
    
  coded_sdgs_df <- as.data.frame(table(coded_sdgs)) %>%
    dplyr::filter(coded_sdgs != '') %>%
    separate(col = coded_sdgs, into = c('goal', 'target_id'), sep = '_', remove = F) %>%
    dplyr::mutate(goal_id   = as.numeric(gsub("\\D", "", goal)),
                  target_id = gsub('^.{3}', "", coded_sdgs)) %>%
    arrange(goal_id, target_id) %>%
    dplyr::select(1:2, goal_id, everything()) %>%
    dplyr::rename(n_statements = Freq)
  
  
  
  ### --> The above data only presents what were detected, but some SDGs without match won't be shown. 
  ### --> Force to list all 17 SDGs and 169 Targets

  
  ### --> merge data 
  coded_sdgs_df_format <- merge(coded_sdgs_df, goals_df, 
                          by.x = c('goal', 'coded_sdgs'), by.y = c('goalname', 'target_id_un'), all = T) %>%
    dplyr::mutate(goal = factor(goal, levels = goals_ls)) %>%
    arrange(goal, id) %>%
    dplyr::mutate(id = row_number()) %>%
    dplyr::mutate(coded_sdgs = gsub('general', 'g', coded_sdgs),
                  coded_sdgs = factor(coded_sdgs, levels = unique(coded_sdgs)),
                  coded_sdgs = reorder(coded_sdgs, id)) %>%
    as.data.frame()
  
  # str(coded_sdgs_df_format)
  return(coded_sdgs_df_format)

}

```




```{r - run}
ls <- list.files(path = paste0(dir_input, 'DF_coded/'), pattern = '*.RData$', ignore.case = T, full.names = T); ls

cat('There are', ls %>% length(), 'corporate reports were CODED.')

dfs <- data.frame()

for (f in ls) {
  # print(f)
  com_name <- gsub('\\.RData|_coded', '', basename(f)); print(com_name)
  load(f) ## all coded reports were named "coded" as Rdata

  d <- func_format(coded = coded)
  d$company = com_name
  d <- d %>% dplyr::select(company, everything())

  dfs <- rbind(dfs, d)
}

n <- unique(dfs$company) %>% length(); n

### save all the hits to xlsx for easier inspection. 
fname <- paste0(dir_input, 'DF_coded_results/coded_dfs_', n, '.xlsx');  fname
writexl::write_xlsx(x = dfs, path = fname)
fname <- paste0(dir_input, 'DF_coded_results/coded_dfs_', n, '.RData'); fname
save(dfs, file = fname)
```





# 3. Compare Machine to Human

