---
title: "Text_mining"
author: "Yingjie"
date: "6/17/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---


# Dir and packages

```{r include=FALSE}
### To clear your environment 
remove(list = ls())

## set work dir
path <- rstudioapi::getSourceEditorContext()$path
dir  <- dirname(rstudioapi::getSourceEditorContext()$path); dir
setwd(dir)
getwd()
dirname(dir)
setwd(dirname(dir))
getwd()

# directories for Yingjie
  source('./Code/_directories.R')
  dirpath_pdf <- paste0(dir.reports, 'pdf_coded_human/')


# load packages
  source('./Code/_packages.R')

  library(tm)        # text mining: readPDF(), Corpus()
  
  ## for parallel computing
  library(parallel)
  library(doParallel)
  library(foreach)
  
  
# Robust check and install for SDGdetector
if (!requireNamespace("SDGdetector", quietly = TRUE)) {
  message("Installing 'SDGdetector' from GitHub...")
  
  # Check and install remotes if needed
  if (!requireNamespace("remotes", quietly = TRUE)) {
    install.packages("remotes")
  }

  # Install from GitHub
  remotes::install_github("Yingjie4Science/SDGdetector")
} else {
  message("'SDGdetector' is already installed.")
}
library(SDGdetector)
  
today <- format(Sys.time(), "%Y%m%d_%H%M"); today

## load the function
source('./Code/function_sdg_detector.R') ## `sdg_detector()`
```




# 1. PDF to cleaned TXT

  This was processed in a separate script. 



# 2. Detect SDGs  

  To match the keywords to each corpus and format results

  The analysis will return the number of commitments to different SDGs by sentence. This requires pattern searching where every sentence has to end with a period (.). 
  
  Limitations/problems for: figure text, bullet points, anything without a period.
  

## 2.1. Load cleaned reports

  **Choose one of the following as input**

```{r - 350 + reports with human data}

dir_input <- dirpath_pdf

## 1. load the `txt` data
# ls <- list.files(path = paste0(dir_input, 'TXT/'), pattern = '*.RData$', ignore.case = T, full.names = T); ls

## 2. load the `txt to df` data
ls <- list.files(path = paste0(dir_input, 'DF/'), pattern = '*.RData$', ignore.case = T, full.names = T); #ls

cat('There are', ls %>% length(), 'corporate reports were converted.') ## 352
```





```{r - Test on top 10, eval=FALSE, include=FALSE}
# ls[1]
# fname <- paste0('./Data/data_TextMining/database/', 'ls_com_top20.RData'); fname
# load(fname)
# selected <- paste(ls_com_top20, collapse = "|")
# 
# ls <- str_subset(string = ls, pattern = selected)
# ls <- ls[1:10]


## a few more
ls.my <- c(
  'Schneider Electric', 'BNP Paribas', "Grupo Financiero Banorte",
  'Cemex',
  'Industria de Diseno Textil',
  
  'Total',
  "Valeo", 'Legrand', "Banco Bilbao Vizcaya Argenaria", 
  'Akzo Nobel',
  
  "Vivendi",
  "Diageo", 'Mondi', 'Volvo', 
  'Access Bank',
  
  'Bayer',
  'Sanofi', 'Pfizer', "Toyota Motor", "Danone",
  
  "CMPC Empresas", 'Roche Group', "BASF", "Novartis",
  "Grindrod Limited"
  )
ls.my <- list.files(path = paste0(dir_input, 'DF/'), pattern = paste0(ls.my, collapse = "|"), ignore.case = T, full.names = T)


## final list for coding
# ls <- c(ls.my)
# ls
```


```{r eval=FALSE, include=FALSE}
d2 = setdiff(ls, ls.my)
d2

ls <- d2
```




```{r - 300 + reports without human data, eval=FALSE, include=FALSE}
## 2022-04-01: 146 + reports without human data
## 2022-06-01: 391 reports without human data (use Fortune 500)

dir_input <- paste0(dir.reports, "pdf_not_coded/"); dir_input
ls  <- list.files(path = paste0(dir_input, 'DF/'), pattern = '*.RData$', ignore.case = T, full.names = T); #ls

cat('There are', ls %>% length(), 'corporate reports were converted.') ## 146 => 389
```





## 2.2. Load SDG search terms

  These SDG search terms can be *direct mention*, such as "SDG 1", "SDG 2", "SDG 1.2", "SDG 1.a", or *indirect mention*.  

```{r}

fname <- paste0(dir.tm, 'database/', 'SDG_keys.RData'); fname
load(fname) ## --> SDG_keys_drc, SDG_keys_indrc, SDG_keys

```


  

## 2.3. To detect 

  For every row in the corpus (ideally only 1 sentence in each row), have a column 1-17 and 1/0 or y/n if matching the SDG. This would be a for-loop and i 1:17 is linked to the columns being filled
    
    
  * The following is not in use
  
```{r eval=FALSE, include=FALSE}

## loop data
for (f in ls) {
  print(f)
  # ## --> get company name
  company_name <- gsub(".RData", "", basename(f)); print(company_name)
  df <- get(load(f))
  
  coded <- sdg_detector(df = df)
  
  ### save all the hits to xlsx for easier inspection. 
  # fname <- paste0(dir_input, 'DF_coded/', company_name, '_coded.xlsx'); fname
  # writexl::write_xlsx(x = coded, path = fname)
  # fname <- paste0(dir_input, 'DF_coded/', company_name, '_coded.csv'); fname
  # readr::write_csv(x = coded, file = fname)
  fname <- paste0(dir_input, 'DF_coded/', company_name, '_coded.RData'); fname
  save(coded, file = fname)
  
  ## --> To clear up the memory for next loop
  gc()
}

```



### - run parallel - SDGDetector

```{r eval=FALSE, include=FALSE}

## set up parallel
library(parallel)
library(doParallel)
library(foreach)

detectCores()
detectCores(logical = FALSE)  ## Same answer as before on some systems?
## returns the number of available hardware threads, and if it is FALSE, returns the number of physical cores
n_cores <- detectCores(logical = TRUE)  
n_cores
cl <- makeCluster(n_cores-1)  
doParallel::registerDoParallel(cl)   # use multicore, set to the number of our cores

## get the total number of data files
n <- length(ls); n

## run parallel
system.time({
  foreach (i=1:n, .packages = c("dplyr", "stringr")) %dopar% {
    f <- ls[i]; #f
    ## --> get company name
    company_name <- gsub(".RData", "", basename(f)); print(company_name)
    df <- get(load(f))
    
    coded <- sdg_detector(df = df)

    fname <- paste0(dir_input, 'DF_coded/', company_name, '_coded.RData'); #fname
    save(coded, file = fname)
    
    ## --> To clear up the memory for next loop
    # gc()
  }
})


## When you're done, clean up the cluster
stopImplicitCluster()
```




### - run parallel - txt2sdg

```{r}

## install the package if not already installed
if (!requireNamespace("text2sdg", quietly = TRUE)) {
  if (!requireNamespace("devtools", quietly = TRUE)) {
    install.packages("devtools")
  }
  devtools::install_github("dwulff/text2sdg")
} else {
  message("Package 'text2sdg' is already installed.")
}
library(text2sdg)


# ensemble approach
hits = detect_sdg(texts)

f <- ls[1]; f

## --> get company name
company_name <- gsub(".RData", "", basename(f)); print(company_name)
df <- get(load(f))


##' 
##' 1. using `sdgdetector`
##' 
coded1 <- sdg_detector(df = df)
coded3 <- sdg_detector(df = df) ### change grepl() to str_detect() in the function
# coded1 <- SDGdetector(x = df, col = 'statement')



##' 
##' 2. using `text2sdg`
##' 
coded2 <- detect_sdg(df$statement)


# extract systems hits
coded2_attr <- attr(coded2, "system_hits")

# fname <- paste0(dir_input, 'DF_coded/', company_name, '_coded.RData'); #fname
# save(coded, file = fname)
    
```




  To Inspect 

  Inspect and tune mining results
  
  Manual edits. Go back to the SDG keyword strings and edit there first. The duplicate SDGs should be the ones that are inspected to make sure that keywords are being used correctly. But overlap is okay if the sentences actually do talk about >1 SDG.
  
```{r}

```


