---
title: "Text_mining"
author: "Yingjie"
date: "6/17/2021"
output: html_document
editor_options: 
  chunk_output_type: inline
---


# Dir and packages

```{r include=FALSE}
### To clear your environment 
remove(list = ls())


# directories for Yingjie
  source('./Code/_directories.R')
  dir.tm.data <- paste0(dir.reports, 'pdf_coded_human/')
  dir.tm.fig  <- paste0(dir.figures, 'figure_tm/')

# directories for Veronica
  # dir.reports <- '../Data/data_TextMining/annual_reports/' # VF added another '.'
  # dir.results <- '../Data/data_results/'                   # VF added another '.'
  # dir.figures <- '../Data/figures/';      dir.figures      # VF added another '.'

# load packages
  source('./Code/_packages.R')

  library(tm)        # text mining: readPDF(), Corpus()
  library(tidyverse) # piping and wrangling
  library(tabulizer) # importing PDFs
  #library(remotes)  # installing from remote repositories
  
  library(hydroGOF)  ## for `rmse`
  
today <- format(Sys.time(), "%Y%m%d_%H%M"); today
ymd   <- format(Sys.time(), "%Y%m%d"); ymd
```


## Helper data
```{r - UN SGD target list}
source('./Code/helper_UN_SDG_Target_list.R') ## --> ls_un_id; goals_ls

goals_df <- ls_un_id %>%
  dplyr::select(goalname, target_id_un, target_id_un2) %>%
  # group_by(goalname) %>%
  # arrange(goalname, target_id_un2) %>%
  dplyr::mutate(target_id_un = gsub('\\.', '_', target_id_un),
                target_id_un = paste0('SDG', target_id_un)) %>%
  dplyr::mutate(id = row_number()) %>%
  dplyr::mutate(target_id_un = factor(target_id_un, levels = unique(target_id_un)),
                target_id_un = reorder(target_id_un, id)) %>%
  as.data.frame()

## save to `SDG_TM` for R package development
fname <- paste0(dirname(getwd()), '/SDG_TM/data/goals_df.RData'); fname
save(goals_df, file = fname)
```

```{r - colors}
getwd()
source('./code/function_UN_SDG_logo_color.R')
color_hex
```







# 3. Compare Machine to Human

## Data

### 1. machine-coded results
```{r}
## load data
ls_f <- list.files(path = paste0(dir.tm.data, 'DF_coded_results'), pattern = 'RData$', full.names = T); ls_f
tail(ls_f, n = 1)
load(tail(ls_f, n = 1)) ## load the latest/last data

## machine-coded data
dfs_m <- dfs %>%
  dplyr::rename(target = coded_sdgs)


## company list
com_ls <- unique(dfs_m$company); #com_ls
cat('There are', com_ls %>% length(), 'companies.')
```





### 2. human-coded results by UNGSII
```{r }
fname <- paste0(dir.results, 'df.RData'); fname
load(fname)
dfs_h <- df %>%
  dplyr::filter(yr == 2018)
names(dfs_h)

cat('There are', unique(dfs_h$Company) %>% length(), 'companies.')

## a subset of data
# company_name <- 'Cemex'
# xls <- paste0('./Data/data_TextMining/df_', company_name, '_reference.xlsx'); xls
# human <- readxl::read_excel(xls) 
# cols_selected <- names(human)[1:6]; cols_selected


dfs_h <- dfs_h %>%  
  dplyr::filter(Company %in% com_ls) %>%
  ### some duplicated Target ids ------------------------------
  ungroup() %>%
  group_by(Company, iso3, goal_id, Target_id, goal) %>%
  dplyr::summarise(n_statements = sum(n_statement, na.rm = T)) %>%
  dplyr::filter(goal_id != 'SDGs') %>%
  dplyr::mutate(target = gsub('\\.', '_', Target_id),
                target = paste0('SDG', target)) %>%
  ### link with all SDG and targets ---------------------------
  merge(., goals_df,
        by.x = c('goal', 'target'), by.y = c('goalname', 'target_id_un'), all = T) %>%
  dplyr::mutate(goal = factor(goal, levels = goals_ls)) %>%
  arrange(goal, id) %>%
  dplyr::mutate(id = row_number()) %>%
  # arrange(goal, id) %>%
  dplyr::mutate(target = factor(target, levels = unique(target)),
                target = reorder(target, id)) %>%
  dplyr::rename_all(tolower) %>%
  as.data.frame()


## data description
## - which companies have the most SDG commitments? 
dfs_h_desc <- dfs_h %>%
  dplyr::filter(str_detect(target, '_g', negate = T)) %>%  
  group_by(company) %>%
  dplyr::summarise(n = sum(n_statements, na.rm = T)) %>%
  arrange(desc(n)) %>%
  as.data.frame()

## - the list of companies with no more than 20 commitments
ls_com_fewCmt <- dfs_h_desc %>%
  dplyr::filter(n<=100, !is.na(company)) %>%  
  as.data.frame()
ls_com_fewCmt <- unique(ls_com_fewCmt$company)


## - the top 20
ls_com_top20 <- dfs_h_desc %>% slice(1:25) %>% dplyr::select(1) %>% unlist() %>% unname(); ls_com_top20

fname <- paste0(dir.tm, 'database/', 'ls_com_top20.RData'); fname
save(ls_com_top20, file = fname)
```


## Compare

```{r include=FALSE}
### plot correlation 
library(ggpmisc)  ## for `stat_poly_eq`
library(hydroGOF)  ## for `rmse`

formula <- y ~ x  ## needed for ggpmisc's equation and R2 text
# myformat <- "Intercept: %s\nSlope: %s\nR²: %s"
myformat <- "Slope: %s\nR²: %s"  ##not sure how to extract slope
myformat <- "R²: %s"
```


```{r - data}
names(dfs_m)
names(dfs_h)


dfs_m_format <- dfs_m %>% 
  dplyr::select(company, goal, target, n_statements) %>%
  group_by(company, goal, target) %>%
  dplyr::summarise(n = sum(n_statements, na.rm = T))%>%
  dplyr::mutate(coder = 'machine')

dfs_h_format <- dfs_h %>% 
  dplyr::select(company, goal, target, n_statements) %>%
  group_by(company, goal, target) %>%
  dplyr::summarise(n = sum(n_statements, na.rm = T)) %>%
  dplyr::mutate(coder = 'human')

dfs_2 <- rbind(dfs_m_format, dfs_h_format) %>%
  dplyr::filter(!is.na(company))



## data in a wide format
dfs_2w_targ <- dfs_2 %>%
  ## remove SDG general 
  dplyr::filter(str_detect(target, '_g', negate = T)) %>%  
  spread(key = 'coder', value = 'n') %>%
  dplyr::group_by(company) %>%
  dplyr::mutate(RMSE = round(hydroGOF::rmse(obs = human, sim = machine, na.rm=TRUE), 3)) %>%
  ungroup() %>%
  as.data.frame()



## aggregate the coded results to the 'Goal' level
dfs_2w_goal <- dfs_2 %>%
  ## remove SDG general
  dplyr::filter(str_detect(target, '_g', negate = T)) %>%
  ungroup() %>%
  group_by(company, goal, coder) %>%
  dplyr::summarise(n = sum(n, na.rm = T)) %>%
  spread(key = 'coder', value = 'n') %>%
  as.data.frame()
# factor(dfs_2w_goal$goal)
```


```{r - R2 overall}
## function 
# rsq <- function (x, y) cor(x, y) ^ 2
# rsq <- function(x, y) summary(lm(y~x, na.action=na.omit))$r.squared # na.exclude
rsq <- function(x, y) summary(lm(y~x, na.action=na.exclude))$r.squared # 

## input data
df <- dfs_2w_targ %>% dplyr::filter(!company %in% ls_com_fewCmt)
# df <- dfs_2w_goal %>% dplyr::filter(!company %in% ls_com_fewCmt)

r2 <- rsq(x = df$human, y = df$machine) %>% round(., digits = 2); r2 ## 0.56
```




  First, we tested the alignment of the coded results between by human and machine at company level. 
```{r - R2 - by company}
## input data
df <- dfs_2w_targ %>% dplyr::filter(!company %in% ls_com_fewCmt)
# df <- dfs_2w_goal %>% dplyr::filter(!company %in% ls_com_fewCmt)
df <- dfs_2w_targ %>% dplyr::filter(company %in% ls_com_top20) 

## a new dataframe
r2_bycom <- data.frame()

## loop each 
for (com in com_ls) {
  # print(com)
  c <- df %>%
    dplyr::filter(company == com)
  
  ## if the results by human are all NA, then, assign 'NA' value to its R2. 
  count_nonNA <- sum(!is.na(c$human)); count_nonNA
  
  c2 <- c %>%
    dplyr::mutate(r2 = ifelse(
      count_nonNA > 0, rsq(x = human, y = machine) %>% round(., digits = 2), NA)) %>%
    distinct(company, r2) %>%
    as.data.frame()
  r2_bycom <- rbind(r2_bycom, c2)
}

r2_bycom <- r2_bycom %>% arrange(r2)
hist(r2_bycom$r2)


ls_com_smallR2 <- r2_bycom$company[1:25]; ls_com_smallR2
```




```{r - R2 - by goal}

## input data
df <- dfs_2w_targ %>% dplyr::filter(!company %in% ls_com_fewCmt)
# df <- dfs_2w_goal %>% dplyr::filter(!company %in% ls_com_fewCmt)
df <- dfs_2w_targ %>% dplyr::filter(!company %in% ls_com_smallR2)

ls <- df %>% dplyr::filter(!is.na(goal)) %>% distinct(goal) %>% unlist(); ls

## a new dataframe
r2_bygoal <- data.frame()

## loop each
for (i in ls) {
  # print(i)
  c <- df %>% dplyr::filter(goal == i) 
  
  ## if the results by human are all NA, then, assign 'NA' value to its R2. 
  count_nonNA <- sum(!is.na(c$human)); count_nonNA
  
  c2 <- c %>%
    dplyr::mutate(r2 = ifelse(
      count_nonNA > 0, rsq(x = human, y = machine) %>% round(., digits = 2), NA)) %>%
    distinct(goal, r2) %>%
    as.data.frame()
  r2_bygoal <- rbind(r2_bygoal, c2)
}

r2_bygoal <- r2_bygoal %>% arrange(r2)
hist(r2_bygoal$r2)




g_goal <- dfs_2w_goal %>%
  dplyr::filter(!is.na(goal)) %>%
  ggplot(aes(x = human, y = machine)) +
  geom_point(aes(color = goal, alpha = company), show.legend = F) +
  # geom_text(aes(label = goal, color = goal), nudge_x = -2, nudge_y = -25, show.legend = F) +
  scale_colour_manual(values = color_hex) +
  geom_smooth(method = 'lm', formula = y~x, show.legend = F) +
  stat_poly_eq(
    formula = formula, output.type = "numeric",
    aes(label = sprintf(myformat, formatC(stat(r.squared), format = 'f', digits = 2))),
    label.x.npc = "left", label.y.npc = 0.95, color = 'black')+
  geom_abline(slope = 1, linetype = 'dashed', color = 'gray', size = 1, show.legend = F) +
  facet_wrap(~goal, scales = 'free') +
  theme_bw()
fname <- paste0(dir.tm.fig, 'H_M_byGoal_', ymd, '.png'); fname
# ggsave(filename = fname, plot = g_goal, width = 12, height = 9, units = 'in', dpi = 300)


dfs_2w_targ %>%
  dplyr::filter(!is.na(goal), !is.na(target)) %>%
  ggplot(aes(x = human, y = machine, group = goal)) +
  geom_point(aes(color = goal), show.legend = F) +
  scale_colour_manual(values = color_hex) +
  geom_smooth(method = 'lm', formula = y~x, show.legend = F) +
  stat_poly_eq(
    formula = formula, output.type = "numeric",
    aes(label = sprintf(myformat, formatC(stat(r.squared), format = 'f', digits = 2))),
    label.x.npc = "left", label.y.npc = 0.95, color = 'black')+
  geom_abline(slope = 1, linetype = 'dashed', color = 'gray', size = 1, show.legend = F) +
  facet_wrap(~goal, scales = 'free') +
  theme_bw()

fname <- paste0(dir.tm.fig, 'H_M_byTarget_', ymd, '.png'); fname
ggsave(filename = fname, plot = last_plot(), width = 12, height = 9, units = 'in', dpi = 300)
```



*Test interactive figures*
```{r eval=FALSE, include=FALSE}
library(plotly)
ggplotly(g_goal) + theme(legend.position='none')
```


```{r eval=FALSE, include=FALSE}
library(ggiraph)

my_gg <- dfs_2w_goal %>%
  dplyr::filter(!is.na(goal)) %>%
  ggplot(aes(x = human, y = machine)) +
  geom_point_interactive(aes(color = goal), show.legend = F) +
  # geom_text(aes(label = goal, color = goal), nudge_x = -2, nudge_y = -25, show.legend = F) +
  scale_colour_manual(values = color_hex) +
  geom_smooth_interactive(method = 'lm', formula = y~x, show.legend = F) +
  stat_poly_eq(
    formula = formula, output.type = "numeric",
    aes(label = sprintf(myformat, formatC(stat(r.squared), format = 'f', digits = 2))),
    label.x.npc = "left", label.y.npc = 0.95, color = 'black')+
  geom_abline_interactive(slope = 1, linetype = 'dashed', color = 'gray', size = 1, show.legend = F) +
  facet_wrap(~goal, scales = 'free') +
  theme_bw()
girafe(code = print(my_gg) )

```




```{r - Plot at target level}

### 1. take the raw value
dfs_2w_targ %>%
  ## random sample 10 companies 
  dplyr::filter(company %in% sample(x = com_ls, size = 10)) %>%
  dplyr::mutate(goal_id = (gsub("SDG", "", target))) %>%
  ggplot(aes(x = human, y = machine, color = company, group = company)) +
  geom_point(show.legend = F) +
  geom_text(aes(label = goal_id), 
            # hjust=-0.20, vjust=-0.2,
            nudge_x = -2, nudge_y = -25, color = 'black', size = 2,
            show.legend = F) +
  geom_smooth(method = 'lm', formula = y~x, show.legend = F) +
  # stat_poly_eq(
  #   aes(label = paste(..eq.label.., ..rr.label.., sep = "*\",\"~~~")),  ## paste0("RMSE==", RMSE)  ## sep = "*\",\"~~~"
  #   label.x.npc = "left", label.y.npc = 0.95, color = 'black',
  #   formula = formula, parse = TRUE, size = 3) + 

  stat_poly_eq(
    formula = formula, output.type = "numeric",
    aes(label = sprintf(myformat,
                        # formatC(stat(coef.ls)[[x]][[2, "Estimate"]]),   ## , format = 'f', digits = 2
                        formatC(stat(r.squared), format = 'f', digits = 2))),
    label.x.npc = "left", label.y.npc = 0.95, color = 'black')+
  
  geom_abline(slope = 1, linetype = 'dashed', color = 'gray', size = 1, show.legend = F) +
  facet_wrap(~company, scales = 'free') +
  theme_bw()

fname <- paste0(dir.tm.fig, 'H_M_target_raw_', today, '.png'); fname
ggsave(filename = fname, plot = last_plot(), width = 12, height = 9, units = 'in', dpi = 300)



### 2. take the log value
# dfs_2w_targ %>%
#   ggplot(aes(x = human, y = machine, color = company)) +
#   geom_point(show.legend = F) +
#   geom_smooth(method = 'lm', formula = y~x, show.legend = F) +
#   scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
#                 labels = trans_format("log10", math_format(10^.x))) +
#   scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
#                 labels = trans_format("log10", math_format(10^.x))) +
#   facet_wrap(~company, scales = 'free') +
#   theme_bw()
# 
# fname <- paste0('./Data/data_TextMining/text_mining_figs/', 'H_M_target_log_', today, '.png'); fname
# ggsave(filename = fname, plot = last_plot(), width = 12, height = 9, units = 'in', dpi = 300)




```



```{r - Plot at goal level}

### plot correlation 
### --> 1. input raw data
dfs_2w_goal %>%
  ## random sample 10 companies 
  # dplyr::filter(company %in% sample(x = com_ls, size = 10)) %>%
  ## plot the top 20 companies 
  dplyr::filter(company %in% ls_com_top20) %>% ## 
  dplyr::mutate(company = factor(company, levels = ls_com_top20)) %>% ## 
  dplyr::mutate(goal_id = as.numeric(gsub("\\D", "", goal))) %>%
  ggplot(aes(x = human, y = machine)) + # color = company
  geom_point(aes(color = goal), show.legend = F) +
  geom_text(aes(label = goal_id, color = goal), 
            # hjust=-0.20, vjust=-0.2,
            nudge_x = -2, nudge_y = -25, 
            show.legend = F) +
  scale_colour_manual(values = color_hex) +
  geom_smooth(method = 'lm', formula = y~x, show.legend = F) +
  stat_poly_eq(
    formula = formula, output.type = "numeric",
    aes(label = sprintf(myformat, formatC(stat(r.squared), format = 'f', digits = 2))),
    label.x.npc = "left", label.y.npc = 0.95, color = 'black')+
  geom_abline(slope = 1, linetype = 'dashed', color = 'gray', size = 1, show.legend = F) +
  facet_wrap(~company, scales = 'free') +
  theme_bw()
fname <- paste0(dir.tm.fig, 'H_M_goal_byComp_', today, '.png'); fname
ggsave(filename = fname, plot = last_plot(), width = 10, height = 10, units = 'in', dpi = 300)


### --> 2. input log data
# dfs_2w_goal %>%
#   ggplot(aes(x = human, y = machine, color = company)) +
#   geom_point(show.legend = F) +
#   geom_smooth(method = 'lm', formula = y~x, show.legend = F) +
#   scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
#                 labels = trans_format("log10", math_format(10^.x))) +
#   scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
#                 labels = trans_format("log10", math_format(10^.x))) +
#   geom_abline(slope = 1, linetype = 'dashed', color = 'gray', size = 1, show.legend = F) +
#   facet_wrap(~company, scales = 'free') +
#   theme_bw()
# 
# fname <- paste0('./Data/data_TextMining/text_mining_figs/', 'H_M_goal_byComp_log_', today, '.png'); fname
# ggsave(filename = fname, plot = last_plot(), width = 12, height = 9, units = 'in', dpi = 300)
```




## Inspection and validation

  * check the alignment with human-coded results in *H_M_goal_byComp_yymmdd_hhmm.png* under the folder `text_mining_figs`;
  
  * look into the companies whose "R2" is low, and the specific SDG with large errors;
  
  * run code bellow to inspect which goal or target contributed to the large errors;
    - compare the plots by machine-coder and by human-coder (plots under the folder `text_mining_figs`)
    - inspect the spreadsheet (*inspect_XXX.xlsx*) under `coded_inspection` folder (Filters the sdg and inspect the text)
    - may test specific search string in *test_pattern_grepl.Rmd*
  
  * revise the CodeBook accordingly if necessary
  
  * revise the keywords database in *R* and update to *GitHub*
  
  * re-run text mining 
    - start with one report for a quick test
    - then another trial test on 10 report; if no obvious large error, then
    - run code on all the report data
  

```{r - Single company, eval=FALSE, include=FALSE}
# company_name <- 'Cemex'
# company_name <- '3M'
# company_name <- 'Akzo Nobel'
# company_name <- 'Access Bank'
# company_name <- "Alibaba"                  ## 16
# company_name <- "Banco Bilbao Vizcaya Argenaria"
# company_name <- 'BASF'
# company_name <- 'BNP Paribas'
# company_name <- 'Bayer'                    ## 3.6, 3.8, 3.b wrong by human
# company_name <- "Reliance Industries"
# company_name <- "Bank Mandiri"
# company_name <- "British American Tobacco" ## 3
# company_name <- "Cemex"
# company_name <- "CMPC Empresas"


# company_name <- "Diageo"
# company_name <- 'Legrand'
# company_name <- "Novartis"


# company_name <- "Grupo Financiero Banorte" ## in total 42 "innov*" in the pdf report, how can they get 242 SDG9_5?; for SDG11_5, only 22 "safe" words

# company_name <- "Pfizer"

# company_name <- "Roche Group"
# company_name <- 'Sanofi'
# company_name <- 'Toyota Motor'
# company_name <- "Total"
company_name <- "Vivendi"
# company_name <- "Valeo"


### other test -----------
# company_name <- "Austrian Post"
# company_name <- "AXA"
# company_name <- "CITIC Group"
# company_name <- "Denso"
# company_name <- "Banpu"
# company_name <- "BMW"
# company_name <- "Deutsche Telekom"
# company_name <- "Astra Zeneca"



### machine ----------------------------------------
g_m <- dfs_2w_targ %>%
  dplyr::mutate(n = machine, n = ifelse(n ==0, NA, n)) %>%
  dplyr::filter(company == company_name) %>%
  dplyr::filter(str_detect(target, '_g', negate = T)) %>%  ## remove SDG general 
  ggplot(aes(x = fct_rev(target))) +
  geom_col(aes(y = n), alpha = 0.6) +
  geom_text(aes(y = n, label = n), size = 5, color = 'red') +
  facet_wrap(~goal, scales = 'free_y', ncol = 6) +
  coord_flip() +
  theme_bw() +
  ggtitle(company_name) +
  ylab('Number of SDG statements') + xlab('')
fname <- paste0(dir.tm.fig, 'Test_', company_name, '_M_', today, '.png'); fname
ggplot2::ggsave(filename = fname, plot = g_m, width = 16, height = 9, units = 'in', dpi = 300)



### human ------------------------------------------
g_h <- dfs_2w_targ %>%
  dplyr::mutate(n = human) %>%
  dplyr::filter(company == company_name) %>%
  ggplot(aes(x = fct_rev(target))) +
  geom_col(aes(y = n), alpha = 0.6) +
  geom_text(aes(y = n, label = n), size = 5, color = 'red') +
  facet_wrap(~goal, scales = 'free_y', ncol = 6) +
  coord_flip() +
  theme_bw() +
  ggtitle(company_name) +
  theme(strip.background = element_rect(fill="orange")) +
  ylab('Number of SDG statements') + xlab('')
fname <- paste0(dir.tm.fig, 'Test_', company_name, '_H_', 
                # today, 
                '.png'); fname
ggsave(filename = fname, plot = g_h, width = 16, height = 9, units = 'in', dpi = 300)



### to screen the coded data for refining --------
f <- list.files(path = paste0(dir.tm.data, 'DF_coded'), pattern = company_name, full.names = T); f
load(f) ## `coded`
fname <- paste0('./Data/data_TextMining/coded_inspection/inspect_', company_name, '.xlsx'); fname
writexl::write_xlsx(x = coded, path = fname)
```





  .............. THE END .................
  
  
  
  
  
  
```{r eval=FALSE, include=FALSE}
# get sums for each SDG
  # colSums(corpus$SDG1)


# coded_sdgs <- dplyr::pull(coded, sdgs)   ## the same as below one
coded_sdgs <- as.vector(unlist(coded['sdgs_n'])) %>%
  paste(sep = " ", collapse = " ")

# coded_sdgs


# table formatting ---------------------------------------------------------------------------------
coded_sdgs <- unlist(strsplit(coded_sdgs, split = "\\,")) %>% trimws();
  
coded_sdgs_df <- as.data.frame(table(coded_sdgs)) %>%
  dplyr::filter(coded_sdgs != '') %>%
  separate(col = coded_sdgs, into = c('goal', 'target_id'), sep = '_', remove = F) %>%
  dplyr::mutate(goal_id   = as.numeric(gsub("\\D", "", goal)),
                target_id = gsub('^.{3}', "", coded_sdgs)) %>%
  separate(col = target_id, into = c('target_id', 'target_n'), sep = '-', remove = F) %>%
  dplyr::mutate(target_n = as.numeric(target_n),
                n_total  = Freq * target_n) %>%
  arrange(goal_id, target_id) %>%
  group_by(goal, goal_id, target_id) %>%
  dplyr::summarise(n_statements = sum(n_total, na.rm = T))  %>%

  # dplyr::select(1:2, goal_id, everything()) %>%
  # dplyr::rename(n_statements = n_total) %>%
  as.data.frame()

sum(coded_sdgs_df$n_statements)

coded_sdgs_df %>%
  ggplot(aes(x = fct_rev(target_id))) +
  geom_col(aes(y = n_statements), alpha = 0.6) +
  geom_text(aes(y = n_statements + 2, label = n_statements), size = 5, color = 'red') +
  facet_wrap(~goal, scales = 'free_y') +
  coord_flip() +
  theme_bw()
```
