---
title: "Text_mining"
author: "Yingjie"
date: "01/23/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---


  This script aims to produce randomly selected reports (25%) and text lines (200 rows per report) to validate the text mining results. 
  

# Directories and packages

```{r include=FALSE}
### To clear your environment 
# remove(list = ls())

## set work dir
getwd()

# directories for Yingjie
  dir.reports <- './Data/data_tm/annual_reports/'
  dir.results <- './Data/data_results/'
  dir.figures <- './Data/figures/'
  dir.tm      <- './Data/data_tm/annual_reports/pdf_coded_human/'

# load packages
  source('./Code/_packages.R')

  library(tm)        # text mining: readPDF(), Corpus()
  library(dplyr) # piping and wrangling
  # library(tabulizer) # importing PDFs
  #library(remotes)  # installing from remote repositories
  # install.packages("metagear_0.7.tar.gz", repos = "http://cran.us.r-project.org", type = "source", dependencies = TRUE)
  library(metagear)  # for `effort_distribute()`
  
today <- format(Sys.time(), "%Y%m%d_%H%M"); today
ymd   <- format(Sys.time(), "%Y%m%d"); ymd

```



# Data input

## Helper data
```{r}
source('./Code/helper_UN_SDG_Target_list.R') ## --> ls_un_id; goals_ls

fname <- paste0(dirname(getwd()), '/SDG_TM/data/goals_df.RData'); fname
load(fname)
```


## List of the 25% reports
```{r}

## 1. load the reports with human-coded results
ls1 <- list.files(path = paste0(dir.reports, 'pdf_coded_human/DF_coded/'), pattern = '*.RData$', ignore.case = T, full.names = T); 
# ls1
cat('There are', ls1 %>% length(), 'corporate reports were coded')



## 2. load the reports without human-coded results
ls2 <- list.files(path = paste0(dir.reports, 'pdf_not_coded/DF_coded/'), pattern = '*.RData$', ignore.case = T, full.names = T); 
# ls2
cat('There are', ls2 %>% length(), 'corporate reports were coded')


ls <- c(ls1, ls2)

## get company name list 
# ls[] <- sapply(X = ls, FUN = basename)
# ls[] <- sapply(X = ls, function(x) gsub('.RData', '', as.character(x))) 
# ls
 

set.seed(123)
samp <- sample(x = ls, size = length(ls)*0.25, replace = F)
# samp
cat('There are', samp %>% length(), 'corporates were SELECTED for screening')
```




## 100 lines from each report with machine-coded results

  - 70 lines of sentences with coded data
  - 30 lines of sentences without coded data (to reduce coders' workload to identify SDGs)
  
```{r}
### load the function 
source('./Code/function_format_coded.R')


ls  <- samp
dfs <- data.frame()
pcts<- c()
row_total <- c()

for (f in ls) {
  # print(f)
  com_name <- gsub('\\.RData|_coded', '', basename(f)); print(com_name)
  load(f) ## all coded reports were named "coded" as Rdata
  
  ## % of not coded rows for each report
  pct <- (coded %>% dplyr::filter(nchar(sdgs) > 3) %>% nrow())/(coded %>% dplyr::filter(nchar(sdgs) < 3) %>% nrow())
  cat('There are', pct %>% scales::percent(), 'of the rows were labeled.')
  pcts <- c(pcts, pct)
  row_total <- c(row_total, nrow(coded))
  
  ## 70 rows with coded info
  coded_sample1 <- coded %>% 
    dplyr::filter(nchar(sdgs) > 3)       %>% ## with coded info
    dplyr::filter(nchar(statement) > 20) %>% ## remove sentences that are too short
    as.data.frame()
  n_in_case <- nrow(coded_sample1)           ## in case some dataframes have less coded info
  coded_sample1 <- coded_sample1 %>%
    dplyr::sample_n(., size = ifelse(n_in_case >= 70, 70, n_in_case))  %>%
    dplyr::mutate(company = com_name)    %>%
    dplyr::select(company, everything())
  
  ## 30 rows without coded info
  coded_sample0 <- coded %>% 
    dplyr::filter(nchar(sdgs) < 3)       %>%
    dplyr::filter(nchar(statement) > 20) %>% ## remove sentences that are too short
    dplyr::sample_n(., 30, replace = F)  %>%
    dplyr::mutate(company = com_name)    %>%
    dplyr::select(company, everything())
  
  dfs <- rbind(dfs, coded_sample1, coded_sample0)
}

n <- unique(dfs$company) %>% length(); n



### The distribution of the number of rows in each report
hist(row_total)
summary(row_total)
sum(row_total)*4*0.001/3 ## 16 H


### The distribution of the percentage of rows with SDGs labels. 
hist(pcts)


### save all the hits to xlsx for easier inspection. 
fname <- paste0(dirname(dir.reports), '/coded_validation_coder/screening_dfs_', n, '.xlsx');  fname
writexl::write_xlsx(x = dfs, path = fname)
fname <- paste0(dirname(dir.reports), '/coded_validation_coder/screening_dfs_', n, '.RData'); fname
save(dfs, file = fname)
```



## Format the samples for human coders

   - add additional columns for coders
   - duplicate the rows with multiple SDGs identified

```{r}
fname <- paste0(dirname(dir.reports), '/coded_validation_coder/planA/screening_dfs_', n, '.RData'); fname
load(fname)
names(dfs)

dfs_format <- dfs %>%
  dplyr::select(company, id, everything()) %>%
  dplyr::select(-n_total, -sdgs_n)         %>%
  dplyr::rename(sdg_by_machine = sdgs)     %>%
  dplyr::arrange(desc(nchar(sdg_by_machine)))  %>%
  dplyr::mutate(
    statement = str_to_sentence(statement),
    statement = trimws(statement),
    correct_or_not = "", 
    which_target_ifnot = "", 
    coder_notes = "")

### duplicate the rows with multiple SDGs identified
dfs_format1 <- dfs_format %>%
  dplyr::mutate(sdg_by_machine = gsub('^\\,', '', sdg_by_machine)) 

dfs_format2 <- data.frame()

for (i in 1:nrow(dfs_format1)) {
  
  ## 0. get one row 
  d <- dfs_format1[i, ]
  n <- nchar(d$sdg_by_machine) ## if n > 0, there are SDGs were detected for this row

  if (n>0) {
    ## 1. split the multiple sdgs into multiple columns
    d1 <- data.frame(d, do.call(rbind, str_split(d$sdg_by_machine, ','))) 
    
    ## 2. gather the multiple columns with SDGs into one column and remove duplicated ones
    d2 <- d1 %>% gather(key = "id2", value = "target_by_machine", 8:ncol(.)) %>%
      dplyr::distinct(target_by_machine, .keep_all = T) %>%
      dplyr::filter(str_detect(string = target_by_machine, pattern = "general", negate = T)) %>%
      dplyr::select(company, id, statement, target_by_machine, everything()) %>%
      dplyr::select(-sdg_by_machine, -id2) %>%
      as.data.frame()
  } else {
    d2 <- d %>% dplyr::rename(target_by_machine = sdg_by_machine)
  }
  
  dfs_format2 <- rbind(dfs_format2, d2)
}

```



## Generate spreadsheets for each coder

  - Arrange the text rows by SDGs, so that it is easier for coders to focus on one SDG a time. 
  - distribute tasks
  
```{r echo=FALSE, warning=FALSE}
dfs_format3 <- dfs_format2 %>%
  # arrange(nchar(statement)) %>%  ## to inspect short sentences
  group_by(statement) %>%
  arrange(target_by_machine) %>%
  as.data.frame()

n_novalue <- dfs_format3 %>% dplyr::filter(nchar(target_by_machine) < 3) %>% nrow(); n_novalue
n_value   <- dfs_format3 %>% dplyr::filter(nchar(target_by_machine) > 3) %>% nrow(); n_value

nrow(dfs_format3)
(n_value+n_novalue)

percent_rows <- (n_value/(n_value+n_novalue)) %>% scales::percent()
cat(percent_rows, 'of the selected samples have machine-coded info.')



## split the workload -------------------------------------
n_coders = 4

### 1. split the rows with coded info
dfs_task1 <- dfs_format3 %>%
  dplyr::filter(nchar(target_by_machine) > 3) %>%
  as.data.frame()

dir_eff <- paste0(dirname(dir.reports), '/coded_validation_coder/split1');  dir_eff
file.remove(list.files(path = dir_eff, full.names = TRUE))

##' `effort_distribute()`: Randomly distributes screening tasks evenly or unevenly across multiple team members. 
##'   It populates this effort in a data frame column that includes this screening work (e.g., ABSTRACTS and TITLES).
metagear::effort_distribute(aDataFrame = dfs_task1, 
                            initialize = TRUE, 
                            reviewers = paste0('coder', seq(1:n_coders)), 
                            save_split = TRUE, 
                            directory  = dir_eff)




### 2. split the rows without coded info
dfs_task0 <- dfs_format3 %>%
  dplyr::filter(nchar(target_by_machine) < 3) %>%
  as.data.frame()
dir_eff <- paste0(dirname(dir.reports), '/coded_validation_coder/split0');  dir_eff
file.remove(list.files(path = dir_eff, full.names = TRUE))
metagear::effort_distribute(dfs_task0, initialize = T, 
                  reviewers = paste0('coder', seq(1:n_coders)), 
                  save_split = TRUE, 
                  directory  = dir_eff)


### 3. combine the two and save as xlsx
for (i in 1:n_coders) {
  # print(i)
  
  ### for rows without coded info
  dir_eff <- paste0(dirname(dir.reports), '/coded_validation_coder/split0');  dir_eff
  f <- list.files(dir_eff, pattern = paste0("effort_coder", i), full.names = T); f
  df0 <- read_csv(file = f) %>% dplyr::select(-INCLUDE)
  
  ### for rows with coded info
  dir_eff <- paste0(dirname(dir.reports), '/coded_validation_coder/split1');  dir_eff
  f <- list.files(dir_eff, pattern = paste0("effort_coder", i), full.names = T); f
  df1 <- read_csv(file = f) %>% dplyr::select(-INCLUDE)
  
  ### combine
  df <- rbind(df1, df0)
  cat('There are', nrow(df), "rows for coder", i)
  
  ### save to file
  f <- paste0(dirname(dir.reports), '/coded_validation_coder/screening_effort_coder', i, '.xlsx');  f
  writexl::write_xlsx(x = df, path = f)
}

```



