---
title: "Text_mining"
author: "Yingjie"
date: "01/23/2022"
output: html_document
editor_options: 
  chunk_output_type: inline
---


  This script aims to produce randomly selected reports (25%) and text lines (200 rows per report) to validate the text mining results. 
  

# Directories and packages

```{r include=FALSE}
### To clear your environment 
remove(list = ls())

## set work dir
getwd()

# directories for Yingjie
  dir.reports <- './Data/data_tm/annual_reports/'
  dir.results <- './Data/data_results/'
  dir.figures <- './Data/figures/'
  dir.tm      <- './Data/data_tm/annual_reports/pdf_coded_human/'

# load packages
  source('./Code/_packages.R')

  library(tm)        # text mining: readPDF(), Corpus()
  library(dplyr) # piping and wrangling
  # library(tabulizer) # importing PDFs
  #library(remotes)  # installing from remote repositories
  library(metagear)  # for `effort_distribute()`
  
today <- format(Sys.time(), "%Y%m%d_%H%M"); today
ymd   <- format(Sys.time(), "%Y%m%d"); ymd

```



# Data input

## Helper data
```{r}
source('./Code/helper_UN_SDG_Target_list.R') ## --> ls_un_id; goals_ls

fname <- paste0(dirname(getwd()), '/SDG_TM/data/goals_df.RData'); fname
load(fname)
```




## List of all the coded reports
```{r}

## 1. load the reports with human-coded results
ls1 <- list.files(path = paste0(dir.reports, 'pdf_coded_human/DF_coded/'), pattern = '*.RData$', ignore.case = T, full.names = T); 
# ls1
cat('There are', ls1 %>% length(), 'corporate reports were coded')



## 2. load the reports without human-coded results
ls2 <- list.files(path = paste0(dir.reports, 'pdf_not_coded/DF_coded/'), pattern = '*.RData$', ignore.case = T, full.names = T); 
# ls2
cat('There are', ls2 %>% length(), 'corporate reports were coded')


ls <- c(ls1, ls2)
cat('There are', ls %>% length(), 'corporate reports were coded, in total.')

```




## Random samples from the machine-coded results

  **Note1**: We randomly choose 4200 sentences for inspection from the 500 reports. Among the 4200, 200 are the common samples for all the coders, and the rest 4000 are evenly distributed to four coders (each get another 1000) for independent inspection.
  
  **Note2**: For the in total 4200 sentences, 50% comes from sentences with SDG labels while the rest 50% from sentences without any SDG labels. 
  
```{r - Parameter settings, include=FALSE}
nth_round <- 3   ## which round of inspection
len_min   <- 40  ## exclude super short sentences

## --> On average, sentences today range from 15 to 20 words. The average word in the English language is 4.7 characters.
## --> https://medium.com/@theacropolitan/sentence-length-has-declined-75-in-the-past-500-years-2e40f80f589f
## --> https://www.wyliecomm.com/2021/11/whats-the-best-length-of-a-word-online/
```


```{r - Pull data}
### to put all coded report together
coded_bind <- data.frame() 
for (f in ls) {
  # print(f)
  com_name <- gsub('\\.RData|_coded', '', basename(f)); #print(com_name)
  load(f) ## all coded reports were named "coded" as Rdata
  coded <- coded %>% dplyr::mutate(company = com_name) %>%
    dplyr::select(company, everything())
  ## bind all coded data together 
  coded_bind <- rbind(coded_bind, coded)
}

unique(coded_bind$company) %>% length()
cat('There are', nrow(coded_bind), 'sentences in total from the coded companies.')

# gc()
```




```{r - Subset the samples}

### take random samples from the whole dataset -------------------------------------------
set.seed(nth_round*123)

cat('We choose 4200, or', round(4200/nrow(coded_bind)*100, digits = 2), '% of all the sentences for inspection.\n\n')

## 50% (n = 2100) rows with coded info
coded_sample1 <- coded_bind %>% 
  dplyr::filter(nchar(sdgs) > 3)       %>%      ## with coded info
  dplyr::filter(nchar(statement) > len_min) %>% ## remove sentences that are too short
  
  ## !!! remove the rows that are labeled as "SDGx_general" only - this is for inspection use only
  dplyr::mutate(myfilter = stringr::str_count(sdgs, ",") - stringr::str_count(sdgs, "general")) %>%
  dplyr::filter(myfilter != 0) %>%
  dplyr::select(-myfilter) %>%
  
  dplyr::sample_n(., size = 2100, replace = F) %>%
  as.data.frame()


## 50% (n = 2100) rows without any coded SDG labels info
coded_sample0 <- coded_bind %>% 
  dplyr::filter(nchar(sdgs) < 3)       %>%
  dplyr::filter(nchar(statement) > len_min) %>% ## remove sentences that are too short
  dplyr::sample_n(., size = 2100, replace = F)  

dfs <- rbind(coded_sample1, coded_sample0)
n   <- unique(dfs$company) %>% length(); 
cat(n, 'companies are included in the sample.\n\n')


### save all the hits to xlsx for easier inspection. 
fname <- paste0(dirname(dir.reports), '/coded_validation_coder/planB/screening_dfs_planB_R', nth_round, '.xlsx');  fname
writexl::write_xlsx(x = dfs, path = fname)
fname <- paste0(dirname(dir.reports), '/coded_validation_coder/planB/screening_dfs_planB_R', nth_round, '.RData'); fname
save(dfs, file = fname)
```



## Format the samples for human coders

   - (1) add additional columns for coders
   - (2) get the unique SDG target and sort them for easy checking

```{r}

fname <- paste0(dirname(dir.reports), '/coded_validation_coder/planB/screening_dfs_planB_R', nth_round, '.RData'); fname
load(fname)
names(dfs)

### load the function 
source('./Code/function_format_coded.R')


### add additional columns for coders 
dfs_format <- dfs %>%
  dplyr::select(company, id, everything()) %>%
  dplyr::select(-n_total, -sdgs_n)         %>%
  dplyr::rename(sdg_by_machine = sdgs)     %>%
  dplyr::arrange(desc(nchar(sdg_by_machine)))  %>%
  dplyr::mutate(
    # statement = str_to_sentence(statement),     ## change all capitalized words
    statement = trimws(statement),
    correct_or_not = "", 
    which_target_ifnot = "", 
    coder_notes = "")


### get the unique SDG target and sort them for easy checking
dfs_format1 <- dfs_format %>%
  dplyr::mutate(sdg_by_machine = gsub('^\\,', '', sdg_by_machine)) 

dfs_format2 <- data.frame()
for (i in 1:nrow(dfs_format1)) {
  
  ## 0. get one row 
  d <- dfs_format1[i, ]
  n <- nchar(d$sdg_by_machine) ## if n > 0, there are SDGs were detected for this row

  if (n>0) {
    ## 1. get the coded SDG list and take the unique and sorted values
    sdg_ls <- d$sdg_by_machine %>% 
      strsplit(., split = ',') %>% unlist() %>%                   ## split this long string to a vector
      # stringr::str_subset(., pattern = "general", negate = T) %>% ## remove SDGs with 'general'
      unique() %>% sort() %>%                                     ## get the unique SDG list
      paste(., collapse = ', ')                                   ## combine the vector to a long string
    
    ## 2. update the sdg list in the original dataframe
    d$sdg_by_machine <- sdg_ls
    
    ## 3. rename the sdg column 
    d2 <- d %>% dplyr::rename(target_by_machine = sdg_by_machine)
  
  } else {
    d2 <- d %>% dplyr::rename(target_by_machine = sdg_by_machine)
  }
  
  dfs_format2 <- rbind(dfs_format2, d2)
}

```



## Generate tasks for each coder

  - 200 common sentences for all coders. 
  
  - 1000 sentences for each coder
  
```{r echo=FALSE, message=FALSE, warning=FALSE}


dfs_format3 <- dfs_format2 %>%
  # arrange(nchar(statement)) %>%  ## to inspect short sentences
  group_by(statement) %>%
  arrange(target_by_machine) %>%
  as.data.frame()

n_novalue <- dfs_format3 %>% dplyr::filter(nchar(target_by_machine) < 3) %>% nrow(); n_novalue
n_value   <- dfs_format3 %>% dplyr::filter(nchar(target_by_machine) > 3) %>% nrow(); n_value

nrow(dfs_format3)
(n_value+n_novalue)

percent_rows <- (n_value/(n_value+n_novalue)) %>% scales::percent()
cat(percent_rows, 'of the selected samples have machine-coded info.')



## split the workload --------------------------------------------------------------------
n_coders = 4

####################################### ###
### 1. Select the 200 for common pool   ###
####################################### ###

dfs_task1 <- dfs_format3 %>%
  dplyr::sample_n(., size = 200, replace = F) %>%
  ungroup() %>%
  dplyr::mutate(target_by_machine = ifelse(nchar(target_by_machine)<3, NA, target_by_machine)) %>%
  arrange(is.na(target_by_machine), target_by_machine) %>%
  as.data.frame()

output_dir <- paste0(dirname(dir.reports), '/coded_validation_coder/planB/task1_R', nth_round); output_dir
if (!dir.exists(output_dir)) {dir.create(output_dir)}

dir_eff <- paste0(output_dir, '/task1_R', nth_round, '.xlsx');  dir_eff
file.remove(list.files(path = dir_eff, full.names = TRUE))
writexl::write_xlsx(dfs_task1, path = dir_eff)

names(dfs_task1)


####################################### ###
### 2. Split the 4000 to each           ### 
####################################### ###

dfs_task2 <- dfs_format3 %>%
  anti_join(., dfs_task1, by = c("company", "id")) %>% ## exclude the 200 common pool list
  dplyr::mutate(target_by_machine = ifelse(nchar(target_by_machine)<3, NA, target_by_machine)) %>%
  arrange(is.na(target_by_machine), target_by_machine) %>%
  as.data.frame()

output_dir <- paste0(dirname(dir.reports), '/coded_validation_coder/planB/task2_R', nth_round); output_dir
if (!dir.exists(output_dir)) {dir.create(output_dir)}

file.remove(list.files(path = output_dir, full.names = TRUE))
metagear::effort_distribute(dfs_task2, initialize = T, 
                  reviewers = paste0('coder', seq(1:n_coders)), 
                  save_split = TRUE, 
                  directory  = output_dir)


### 2.1. save the task2 as xlsx
for (i in 1:n_coders) {
  # print(i)
  
  ### read in and format
  dir_eff <- output_dir
  f <- list.files(dir_eff, pattern = paste0("effort_coder", i), full.names = T); f
  d <- read_csv(file = f) %>% dplyr::select(-INCLUDE)
  file.remove(f)

  ### save to file
  fxlsx <- gsub('\\.csv$', paste0('_R', nth_round, '\\.xlsx'), f);  fxlsx
  fxlsx <- gsub('effort', 'task2', fxlsx);  fxlsx
  writexl::write_xlsx(x = d, path = fxlsx)
  
    
  ### data desc
  n_tagged <- d %>% dplyr::filter(nchar(target_by_machine) > 3) %>% nrow(); n_tagged
  
  cat('There are', nrow(d), "rows for coder", i, ', and', (n_tagged/nrow(d))*100, '% with SDG tags.')
}

```



