---
title: "Text_mining"
author: "Yingjie"
date: "01/23/2022"
output: html_document
editor_options: 
  chunk_output_type: inline
---


  This script aims to produce randomly selected reports (25%) and text lines (200 rows per report) to validate the text mining results. 
  
  **Before clicking Run All**
  - update `nth_round` 
  
  

# Directories and packages

```{r include=FALSE}
### To clear your environment 
remove(list = ls())

## set work dir
path <- rstudioapi::getSourceEditorContext()$path
dir  <- dirname(rstudioapi::getSourceEditorContext()$path); dir
setwd(dir)
getwd()
dirname(dir)
setwd(dirname(dir))
getwd()

# directories for Yingjie
  dir.reports <- './Data/data_TextMining/annual_reports/'
  dir.results <- './Data/data_results/'
  dir.figures <- './Data/figures/'
  dir.tm      <- './Data/data_TextMining/annual_reports/pdf_coded_human/'

# load packages
  source('./Code/_packages.R')

  library(tm)        # text mining: readPDF(), Corpus()
  library(tidyverse) # piping and wrangling
  library(tabulizer) # importing PDFs
  #library(remotes)  # installing from remote repositories
  library(metagear)  # for `effort_distribute()`
  
today <- format(Sys.time(), "%Y%m%d_%H%M"); today
ymd   <- format(Sys.time(), "%Y%m%d"); ymd

```



# Data in

## specify which round

```{r}
gdrive <- "G:/My Drive/_paper/SDGs/SDGs_Corporations/data_TextMining_shared/"

nth_round <- 2

dir.task1 <- paste0(gdrive, "task1_R", nth_round, "_done"); dir.task1




f.ls <- list.files(path = dir.task1, pattern = "^task1_", full.names = T); f.ls
## test line
# f    <- "./Data/data_TextMining/coded_validation_coder/planB_done/task1/task1_YL.xlsx" 
ds   <- data.frame()
for (f in f.ls) {
  
  coder <- basename(f) %>% gsub('task1_|\\.xlsx', '', .); coder
  d <- readxl::read_excel(path = f) %>%
    dplyr::mutate(coder = coder, index = as.numeric(row.names(.)))
  ds <- rbind(ds, d)
  
}

unique(ds$correct_or_not)
unique(ds$coder)





## unify the checking result to "0, 1, NA" only ------------------------------------------
ds0 <- ds %>%
  dplyr::mutate(coder = gsub(pattern = '.*_', '', coder)) %>%                    ## clean coder name
  dplyr::mutate(correct_or_not = gsub(pattern = '\\*', '', correct_or_not)) %>%  ## clean coder's response
  dplyr::mutate(correct = case_when(correct_or_not == "1" ~ 1,
                                    correct_or_not == "0" ~ 0,
                                    is.na(correct_or_not) ~ NA_real_,
                                    grepl("^Y", correct_or_not) ~ 1,
                                    TRUE                  ~ 0)) %>%
  dplyr::select(coder, correct, correct_or_not, everything()) 


ds1 <- ds0 %>%
  arrange(correct_or_not)



## to check the alignment across coders --------------------------------------------------
ds2 <- ds1 %>%
  dplyr::select(coder, correct, company, index) %>%
  ## only analyze rows being checked
  # dplyr::filter(!is.na(correct)) %>%
  spread(key = coder, value = correct) %>%
  dplyr::mutate(same12 = ifelse(MC == VF, 1, 0),
                same13 = ifelse(MC == YL, 1, 0),
                same14 = ifelse(MC == YZ, 1, 0),
                same23 = ifelse(VF == YL, 1, 0),
                same24 = ifelse(VF == YZ, 1, 0),
                same34 = ifelse(YL == YZ, 1, 0),
                same3  = ifelse(MC == YL & YZ == YL, 1, 0),
                same4  = ifelse(MC == YL & YZ == YL & VF == YL, 1, 0)) %>%
  as.data.frame()
```



## how good TM is
```{r}

names(ds2)

### The accuracy of our SDGdetector judged by SDG experts
ds_accuracy <- ds2 %>%
  dplyr::select(company, index, MC, VF, YL, YZ) %>%
  gather(key = 'coder', value = "value", 3:ncol(.)) %>%
  dplyr::group_by(coder) %>%
  dplyr::summarise(accuracy = sum(value, na.rm = T)/nrow(ds2)) %>%
  dplyr::mutate(id = row.names(.)) %>% dplyr::select(id, everything())
ds_accuracy


### test code
# (sum(ds2$MC, na.rm = T)/nrow(ds2)) %>% 
#   scales::percent() %>% 
#   cat('accuracy by MC:', .)
```






## check the alignment across coders
```{r}
names(ds2)

### The inter-expert reliability 
ds_intercoder <- ds2 %>%
  dplyr::select(company, index, same12, same13, same14, same23, same24, same34) %>%
  gather(key = 'pair', value = "value", 3:ncol(.)) %>%
  dplyr::group_by(pair) %>%
  dplyr::summarise(alignment = sum(value, na.rm = T)/nrow(ds2))

ds_intercoder
```


## save result in xlsx
```{r}
## save to XLSX for easy read
f <- paste0(dirname(dir.task1), '/', 'results_accuracy_',   basename(dir.task1), '.xlsx'); f
writexl::write_xlsx(ds_accuracy, path = f)

f <- paste0(dirname(dir.task1), '/', 'results_intercoder_', basename(dir.task1), '.xlsx'); f
writexl::write_xlsx(ds_intercoder, path = f)
```



```{r read in results}
## for accuracy 
ind <- 'results_accuracy_'
fs <- list.files(path = dirname(dir.task1), pattern = ind, full.names = T)
# f <- fs[1]
dfs_acc <- data.frame()

for (f in fs) {
  # print(f)
  round_id <- f %>%
    basename(.) %>%
    gsub(ind, '', .) %>%
    gsub('task1_|_done.xlsx', '', .)
  # print(round_id)
  
  acc <- readxl::read_excel(f) %>%
    dplyr::mutate(round_id = round_id)
  dfs_acc <- rbind(dfs_acc, acc)
}



## for intercoder
ind <- 'results_intercoder_'
fs <- list.files(path = dirname(dir.task1), pattern = ind, full.names = T)
# f <- fs[1]
dfs_int <- data.frame()

for (f in fs) {
  # print(f)
  round_id <- f %>%
    basename(.) %>%
    gsub(ind, '', .) %>%
    gsub('task1_|_done.xlsx', '', .)
  # print(round_id)
  
  int <- readxl::read_excel(f) %>%
    dplyr::mutate(round_id = round_id)
  dfs_int <- rbind(dfs_int, int)
}
```


```{r plot acc}
## plot ----------------------------------------------------------------------------------

mean(dfs_acc$accuracy)
fun_mean <- function(x){
  return(data.frame(y=mean(x),label=round(mean(x,na.rm=T), digits = 2)))}

p1 <- dfs_acc %>%
  ggplot(aes(x = 1, y = accuracy)) +
  geom_boxplot(fill = 'gray', show.legend = F, varwidth = .5) + # , fill = round_id
  stat_summary(fun =mean, geom="point", shape=15, size=3, alpha = 0.6, color="red", fill="red") +
  stat_summary(fun.data = fun_mean, geom="text", vjust=.5, hjust = -0.2, color="red") +
  scale_y_continuous(limits = c(0.7, .85)) +
  geom_jitter(color="black", shape = 1, size=2, alpha=0.6, width = .05) +
  xlab('Overall') +
  ylab('Accuracy') +
  theme_bw() +
  theme(panel.grid = element_blank(), 
        axis.text.x = element_text(colour='transparent'), 
        axis.ticks = element_blank(), 
        legend.position = "none")
p2 <- dfs_acc %>%
  ggplot(aes(x = round_id, y = accuracy)) + # , fill = round_id
  geom_boxplot(alpha = .8) + # 
  scale_y_continuous(limits = c(0.7, .85)) +
  geom_jitter(color="black", shape = 1, size=2, alpha=0.6, width = .05) +
  xlab('Each Round of Inspection') +
  ylab('') +
  theme_bw() +
  theme(legend.position = "none")
p <- ggarrange(p1, p2, widths = c(1,3))

fname <- paste0(dir.figures, 'Inspection_Accuracy.png');fname
ggsave(fname, plot = p, width = 6.5, height = 3.2, units = 'in', dpi = 300)  
```


```{r plot inter-coder}

p3 <- dfs_int %>%
  ggplot(aes(x = 1, y = alignment)) +
  geom_boxplot(fill = 'gray', show.legend = F, varwidth = .5) + # , fill = round_id
  stat_summary(fun =mean, geom="point", shape=15, size=3, alpha = 0.6, color="red", fill="red") +
  stat_summary(fun.data = fun_mean, geom="text", vjust=.7, hjust = -0.3, color="red") +
  scale_y_continuous(limits = c(0.7, .9)) +
  geom_jitter(color="black", shape = 1, size=2, alpha=0.6, width = .05) +
  xlab('Overall') +
  ylab('Inter-expert Reliability') +
  theme_bw() +
  theme(panel.grid = element_blank(), 
        axis.text.x = element_text(colour='transparent'), 
        axis.ticks = element_blank(), 
        legend.position = "none")


p4 <- dfs_int %>%
  ggplot(aes(x = round_id, y = alignment)) + # , fill = round_id
  geom_boxplot(alpha = .8) + # 
  scale_y_continuous(limits = c(0.7, .9)) +
  geom_jitter(color="black", shape = 1, size=2, alpha=0.6, width = .05) +
  xlab('Each Round of Inspection') +
  ylab('') +
  theme_bw() +
  theme(legend.position = "none")
p <- ggarrange(p3, p4, widths = c(1,3))

fname <- paste0(dir.figures, 'Inspection_InterExpert.png');fname
ggsave(fname, plot = p, width = 6.5, height = 3.2, units = 'in', dpi = 300)  
```


  *Test code
```{r}

# (sum(ds2$same3, na.rm = T)/nrow(ds2)) %>% 
#   scales::percent() %>% 
#   cat('Alignment between MC-YL-YZ:', .)
# 
# (sum(ds2$same4, na.rm = T)/nrow(ds2)) %>% 
#   scales::percent() %>% 
#   cat('Alignment between 4 ppl:', .)




## only look at the rows inspected by all of us ------------------------------------------
# ds4 <- ds2 %>%
#   dplyr::filter(!is.na(YZ))
# 
# (sum(ds4$same3, na.rm = T)/nrow(ds4)) %>% 
#   scales::percent() %>% 
#   cat('Alignment between MC-YL-YZ:', ., '(when only count rows being inspected by all)')
# 
# (sum(ds4$same4, na.rm = T)/nrow(ds4)) %>% 
#   scales::percent() %>% 
#   cat('Alignment between 4 ppl:', ., '(when only count rows being inspected by all)')
```




## look into the difference in text
```{r}

## pull coder comments together and add to the compare table later
dsnote <- ds0 %>% dplyr::select(coder, company, index, 
                                # statement, 
                                # target_by_machine, 
                                coder_notes) %>%
  # dplyr::mutate(id_order = row.names(.)) %>%
  # ungroup() %>% 
  group_by(coder) %>%
  as.data.frame() %>%
  # tidyr::pivot_wider(id_cols = c(company, index), names_from = coder, values_from = coder_notes) %>%
  tidyr::spread(key = coder, value = coder_notes) %>%
  as.data.frame()
  
dsnote1 <- d %>%
  dplyr::select(index, statement, target_by_machine) %>%
  left_join(., dsnote, by = 'index')
  
## the comparison table
dsdiff <- ds2 %>%
  dplyr::select(1:6, same13, same23, same34, same4) %>%
  left_join(x =., 
            y = dsnote1, 
            by = c('company', 'index')) %>%
  # arrange(same4) %>%
  arrange(index) %>%
  as.data.frame()

dsdiff[, 13:16] <- sapply(dsdiff[, 13:16], function(col) ifelse(is.na(col), ' ', col))

## save to XLSX for easy read
f <- paste0(dirname(dir.task1), '/', basename(dir.task1), '_analysis.xlsx'); f
writexl::write_xlsx(dsdiff, path = f)

```




# Process of evaluate the inspection results

  1. Compare the difference between `YL` and others Based on the file "taskx_Rx_done_analysis.xlsx".
  
  2. Read each notes (either from the above xlsx or individual xlsx) to understand the difference. 
  
  3. Edit "SDG keywords for Text Mining Codebook" according to the notes and comments. 
  
  4. Add the controversial ones to the Appendix of "SDG_TM_Inspection_Protocol" for further discussion. 
  
