---
title: "sdg_llm"
author: "Yingjie"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: inline
---


```{r setup}

# rm(list = ls())


dir.code <- getwd(); dir.code
## set working directory
setwd(dirname(dir.code))


library(purrr)
source('./code/_packages.R')

# Load custom functions
source("./code/function_expand_col_to_long.R") ## for expand the sdgdetector column

dir.llm <- "G:/Shared drives/gdrive/_paper/SDGs/SDGs_Corporations_g/data/data_llm/"
dir.assignments <- file.path(dirname(dir.llm), "data_LLM_validation")   # output folder

```



```{r  - functions}

##' Helper: sort one character vector of tokens
##'   sort numerically (by the leading number), then by the part after the dot with this order:
##'   no suffix (e.g., 13) < numeric suffix (e.g., 13.2) < letter suffix (e.g., 13.b).
##'   Within each category, we sort by value/letter.
##'   
sort_mixed_codes <- function(v) {
  u <- unique(trimws(v))                    # de-dupe + trim spaces
  tibble(tok = u) %>%
    mutate(
      major = as.numeric(str_extract(tok, "^\\d+")),
      minor_num = suppressWarnings(as.numeric(str_match(tok, "^\\d+\\.(\\d+)")[,2])),
      minor_chr = str_match(tok, "^\\d+\\.([A-Za-z]+)")[,2],
      # order: none (0) < numeric (1) < letter (2)
      minor_type = case_when(
        is.na(minor_num) & is.na(minor_chr) ~ 0L,
        !is.na(minor_num)                    ~ 1L,
        TRUE                                 ~ 2L
      )
    ) %>%
    arrange(major, minor_type, minor_num, minor_chr) %>%
    pull(tok)
}

```


## load llm data 

```{r}

## -- test code on one file --- 
# f <- file.path(dir.llm, "sdg_llm_output_20250623.xlsx")
# f <- file.path(dir.llm, "sdg_llm_output_20250804.xlsx")
# llm <- readxl::read_excel(path = f)
# 
# 
# llm_sub <- llm %>%
#   dplyr::select(-any_of(c("nchr", "n_total", "sdgs_n", "human_coded", "token_count"))) %>%
#   rename_with(~ gsub("(_|-)?-4o-mini-\\d{4}-\\d{2}-\\d{2}", "", .x, ignore.case = TRUE)) %>%
#   dplyr::select(-any_of(c("gpt"))) %>%
#   rename(
#     'sdgdetector' = 'sdgs'
#   ) %>%
#   dplyr::mutate(
#     sdgdetector = gsub("SDG|_general", "", sdgdetector, ignore.case = TRUE),
#     sdgdetector = gsub("_", ".", sdgdetector, ignore.case = TRUE),
#     sdgdetector = gsub(",", ", ", sdgdetector, ignore.case = TRUE),
#   ) %>%
#   dplyr::select(company, year, statement, sdgdetector, sdg_goal_gpt, sdg_target_gpt, engagement_level_gpt) %>%
#   as.data.frame()
# 
# names(llm_sub) 
```


```{r}

# List all matching files
files <- list.files(
  path = dir.llm,
  pattern = "^sdg_llm_output_\\d{8}\\.xlsx$",
  full.names = TRUE
)

# Function to read & clean one file
clean_llm_file <- function(file_path) {
  readxl::read_excel(file_path) %>%
    dplyr::select(-any_of(c("nchr", "n_total", "sdgs_n", "human_coded", "token_count"))) %>%
    # Remove model+date suffixes in column names
    dplyr::rename_with(~ gsub(
      "(_|-)?-4o-mini-\\d{4}-\\d{2}-\\d{2}",
      "",
      .x,
      ignore.case = TRUE
    )) %>%
    dplyr::select(-any_of(c("gpt"))) %>%
    dplyr::rename(sdgdetector = sdgs) %>%
    dplyr::mutate(
      sdgdetector = gsub("SDG|_general", "", sdgdetector, ignore.case = TRUE),
      sdgdetector = gsub("_", ".", sdgdetector, ignore.case = TRUE),
      sdgdetector = gsub(",", ", ", sdgdetector, ignore.case = TRUE)
    ) %>%
    dplyr::select(company, year, statement, sdgdetector,
           sdg_goal_gpt, sdg_target_gpt, engagement_level_gpt) %>%
    as.data.frame()
}

# Apply to all files and bind
llm_sub <- files %>%
  map_dfr(clean_llm_file, .id = "source_file") %>%
  dplyr::select(-source_file) %>%
  dplyr::distinct(company, year, statement, .keep_all = TRUE) %>%
  arrange(sdgdetector) 

```


```{r tidy data}

llm_sub_ <- llm_sub %>%
  dplyr::mutate(
    statement_id = paste0(company, "_", year, "_", row_number()),
    ## clean up the json format columns
    sdg_goal_gpt   = gsub("\\[|\\]|\'", "", sdg_goal_gpt),
    sdg_target_gpt = gsub("\\[|\\]|\'", "", sdg_target_gpt),
    
    ## sort the sdg codes in each cell
    sdg_target_gpt =  sdg_target_gpt %>%
      str_split(",\\s*") %>%
      map(sort_mixed_codes) %>%
      map_chr(~ paste(.x, collapse = ", ")),
    
    ## replace blank `sdg_target_gpt` with "NA"
    sdg_goal_gpt   = ifelse(sdg_goal_gpt == "", 'NA', sdg_goal_gpt),
    sdg_target_gpt = ifelse(sdg_target_gpt == "", 'NA', sdg_target_gpt),
    
    sdgdetector   = sdgdetector %>%
      str_split(",\\s*") %>%
      map(sort_mixed_codes) %>%
      map_chr(~ paste(.x, collapse = ", "))
  ) %>%
  
  dplyr::rename(
    'targets_nlp' = 'sdgdetector',
    'goals_llm'   = 'sdg_goal_gpt',
    'targets_llm' = 'sdg_target_gpt',
    'engagement_llm' = 'engagement_level_gpt'
  ) %>%
  # select(1:targets_nlp, targets_nlp2, everything()) %>%
  
  ## reformatted so coders see short, clear, standardized labels that minimize confusion or typos when they manually code.
  as.data.frame()
```



## Freq of SDG goals detected by LLM and SDGdetector

```{r stats}

llm_sub_l_gpt <- llm_sub_ %>%
  ## expand the `targets_nlp` column
  expand_col_to_long(data = ., target_col = "goals_llm", sep_list = c(", ")) %>%
  # expand_col_to_long(data = ., target_col = "sdg_target_gpt", sep_list = c(", ")) %>%
  as.data.frame()

llm_sub_l_nlp <- llm_sub_ %>%
  ## expand the `targets_nlp` column
  expand_col_to_long(data = ., target_col = "targets_nlp", sep_list = c(", ")) %>%
  as.data.frame()
```
```{r engagement levels}

names(llm_sub_l_gpt)


llm_sub_l_gpt_summ <- llm_sub_l_gpt %>%
  filter(!goals_llm %in% c(NA, 'NA')) %>%
  group_by(goals_llm, engagement_llm) %>%
  summarise(n = n(), .groups = "drop") %>%
  mutate(
    engagement_llm = factor(
      engagement_llm,
      levels = c(
        "Symbolic Alignment",
        "Strategic Commitment",
        "Substantive Implementation"
      )
    ),
    # sdg as ordered factor 1–17
    goals_llm = factor(goals_llm, levels = 1:17, ordered = TRUE)
  )


unique(llm_sub_l_gpt_summ$engagement_llm)


# 2. Plot with ggplot (grouped bar chart)
llm_sub_l_gpt_summ %>%
  ggplot(.,
         aes(x = goals_llm,
                        y = n,
                        fill = engagement_llm)) +
  # geom_col(position = "fill") + # position = "dodge"
  geom_col() +
  
  scale_fill_manual(
    # name  = "Engagement level",
    values = c(
      "Symbolic Alignment"         = "#e0f3db",  # light
      "Strategic Commitment"       = "#a8ddb5",  # medium
      "Substantive Implementation" = "#43a2ca"   # dark
    ) ) + 
  
  labs(
    x = "SDG",
    y = "Count",
    # fill = "Engagement level",
    fill = "",
    title = "Engagement level by SDG"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    # axis.text.x = element_text(angle = 45, hjust = 1), 
    legend.position = c(0.2, 0.8)
  )

ggsave(
  filename = paste0("./figures/engagement_level_", ymd, ".png"),
  plot = last_plot(),
  width = 8, height = 5, unit = 'in', dpi = 300
)
```


```{r plot}
# Process and summarize
llm_sub_goal_summary_gpt <- llm_sub_l_gpt %>%
  filter(!is.na(goals_llm)) %>%
  filter(!goals_llm %in% c('', 'NA')) %>%
  mutate(
    goals_llm = trimws(goals_llm)
  ) %>%
  count(goals_llm, sort = TRUE) %>%
  mutate(
    percent = 100 * n / sum(n)                       # calculate percentage
  )

library(tidyr)

llm_sub_goal_summary_nlp <- llm_sub_l_nlp %>%
  ## extract the integer part of the SDG goal
  mutate(targets_nlp = str_split(targets_nlp, ",\\s*")) %>%
  unnest(targets_nlp) %>%
  mutate(
    targets_nlp = trimws(targets_nlp),
    goal_detector = str_extract(targets_nlp, "^\\d+")   # integer part only
  ) %>%
  select(1:targets_nlp, goal_detector, everything()) %>%
  
  ## filter out empty or NA values, and count occurrences
  filter(!is.na(goal_detector)) %>%
  filter(!goal_detector %in% c('', 'NA')) %>%
  mutate( goal_detector = trimws(goal_detector) ) %>%
  count(goal_detector, sort = TRUE) %>%
  mutate(
    percent = 100 * n / sum(n)                       # calculate percentage
  )


p.gpt <- 
  ggplot(llm_sub_goal_summary_gpt, aes(x = reorder(goals_llm, -n), y = n)) +
  geom_col(fill = "steelblue") +
  geom_text(aes(label = paste0(round(percent, 1), "%")),
            vjust = -0.5, size = 3) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
  labs(x = "SDG Goal", y = "Count", title = "Distribution of SDG Goals detected by LLM") +
  theme_minimal()

p.det <- 
  ggplot(llm_sub_goal_summary_nlp, aes(x = reorder(goal_detector, -n), y = n)) +
  geom_col(fill = "steelblue") +
  geom_text(aes(label = paste0(round(percent, 1), "%")),
            vjust = -0.5, size = 3) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
  labs(x = "SDG Goal", y = "Count", title = "Distribution of SDG Goals detected by SDGdetector") +
  theme_minimal()

## combine the two plots
library(cowplot)
plot_combined <- plot_grid(p.gpt, p.det, ncol = 1, labels = 'auto', align = "v", axis = "tb")
plot_combined

ggsave(
  filename = paste0("./figures/sdg_detected_distribution_", ymd, ".png"),
  plot = plot_combined,
  width = 7, height = 6, unit = 'in', dpi = 300
)
```



## Sampling

  This function enforces coverage of all 17 goals (if available), oversamples rare goals and target-bearing statements, then fills the remainder by weighted random sampling. It returns both the sample and diagnostics.
  
  We will sample N statements, ensuring at least k per goal, oversampling rare goals by a factor of x and target-bearing statements by a factor of y.

```{r - function }
library(dplyr)
library(tidyr)
library(stringr)
library(purrr)


# ## test data
# df <- llm_sub_
# 
# N_total = 800
# min_per_goal = 10
# rare_rule = "prevalence"
# rare_threshold = 0.05
# topk_common = 5
# rare_boost = 3.0
# target_boost = 1.5
# seed = 42


## function 
sample_statements <- function(df,
                              N_total = 800,
                              min_per_goal = 10,       # guarantee per-goal coverage up to this cap
                              rare_rule = c("prevalence","topk"),
                              rare_threshold = 0.05,    # <5% prevalence = rare (if prevalence rule)
                              topk_common = 5,          # top-k common (if topk rule)
                              rare_boost = 3.0,         # weight multiplier if any rare goal present
                              target_boost = 1.5,       # weight multiplier if has any target
                              seed = 42) {

  rare_rule <- match.arg(rare_rule)

  # clean + explode goals
  goals_long <- df %>%
    mutate(goals_llm = ifelse(is.na(goals_llm), "NA", goals_llm)) %>%
    separate_rows(goals_llm, sep = ",\\s*") %>%
    mutate(goals_llm = str_to_upper(str_trim(goals_llm))) %>%
    filter(!goals_llm %in% c("", "NA")) 
  
  
  G_pre <- goals_long %>%
    group_by(statement_id) %>%
    summarise(primary_goal = first(sort(unique(goals_llm))), .groups = "drop") %>%
    filter(!is.na(primary_goal), primary_goal != "NA") #%>%
    # dplyr::n_distinct(primary_goal)
  
  
  # Step 3: Count distinct primary goals present
  G_present <- n_distinct(G_pre$primary_goal)
  target_share <- 0.25  # aim for 25% from ensured stage (tune to taste)
  min_per_goal_new <- floor((target_share * N_total) / G_present)
  
  message("Auto-tuned min_per_goal = ", min_per_goal_new, 
        " (G_present = ", G_present, ", target_share = ", target_share, ")")


  # compute prevalence
  goal_freq <- goals_long %>%
    count(goals_llm, name = "n_goal") %>%
    mutate(p_goal = n_goal / sum(n_goal)) %>%
    arrange(desc(p_goal))

  # rarity tags
  goal_freq <- goal_freq %>%
    mutate(rarity = dplyr::case_when(
      rare_rule == "prevalence" & p_goal < rare_threshold ~ "RARE",
      rare_rule == "prevalence" ~ "COMMON",
      rare_rule == "topk" & row_number() <= topk_common ~ "COMMON",
      TRUE ~ "RARE"
    ))

  # per-statement features
  per_stmt <- goals_long %>%
    left_join(select(goal_freq, goals_llm, rarity), by = "goals_llm") %>%
    group_by(statement_id) %>%
    summarize(
      goals = paste(sort(unique(goals_llm)), collapse = "; "),
      any_rare_goal = any(rarity == "RARE"),
      primary_goal = first(sort(unique(goals_llm))),  # simple "primary"
      .groups = "drop"
    )

  df2 <- df %>%
    left_join(per_stmt, by = "statement_id") %>%
    mutate(
      has_target = !is.na(targets_llm) & targets_llm != "" & targets_llm != "NA",
      any_rare_goal = if_else(is.na(any_rare_goal), FALSE, any_rare_goal),
      weight = 1 * (if_else(any_rare_goal, rare_boost, 1)) * (if_else(has_target, target_boost, 1))
    )

  # Stage 1: ensure per-goal coverage (up to min_per_goal each)
  set.seed(seed)
  ensured <- df2 %>%
    filter(!is.na(primary_goal)) %>%
    group_by(primary_goal) %>%
    
    ##' `group_modify()` hands you each group .x as a data frame, so you can safely 
    ##'   compute nrow(.x) and pass a constant n_take into slice_sample() for that group.
    group_modify(\(.x, .y) {
      n_take <- min(min_per_goal, nrow(.x))
      dplyr::slice_sample(.x, n = n_take, weight_by = weight, replace = FALSE)
    }) %>%
    ungroup()

  # Stage 2: fill remaining N with weighted sample excluding already selected
  remaining_needed <- max(0, N_total - nrow(ensured))
  pool <- df2 %>%
    filter(!statement_id %in% ensured$statement_id)

  filler <- if (remaining_needed > 0 && nrow(pool) > 0) {
    dplyr::slice_sample(pool, n = min(remaining_needed, nrow(pool)),
                        weight_by = weight, replace = FALSE)
  } else {
    pool[0,]
  }

  sampled <- bind_rows(ensured, filler) %>% distinct(statement_id, .keep_all = TRUE)

  # Diagnostics
  diag_goal_cov <- sampled %>%
    mutate(primary_goal = if_else(is.na(primary_goal), "NONE", primary_goal)) %>%
    count(primary_goal, name = "n_sampled") %>%
    arrange(desc(n_sampled))

  diag_rare_rate <- sampled %>%
    summarize(
      n = n(),
      rare_statements = sum(any_rare_goal, na.rm = TRUE),
      rare_rate = rare_statements / n
    )

  list(
    sample = sampled,
    goal_frequency = goal_freq,
    diagnostics = list(
      per_goal_sample_counts = diag_goal_cov,
      rare_rate = diag_rare_rate,
      ensured_n = nrow(ensured),
      filled_n = nrow(filler)
    )
  )
}

```


`rare_rate`: Proportion of sampled statements flagged as containing rare goals. 
  Why it matters: If your plan was to oversample rare goals with a multiplier (e.g., rare_boost = 3), this number should be higher than the rare-goal prevalence in the full dataset.

```{r - run sampling}

N_total_sample <- 400  # Total sample size


# Run the sampling function
sample_result <- sample_statements(
  df = llm_sub_,
  N_total = N_total_sample,
  min_per_goal = 10,            # guarantee per-goal coverage up to this cap
  rare_rule = "prevalence",     # or "topk"
  rare_threshold = 0.05,        # <5% prevalence = rare (if prevalence rule)
  topk_common = 5,              # top-k common (if topk rule)
  rare_boost = 3.0,             # weight multiplier if any rare goal present
  target_boost = 1.5,           # weight multiplier if has any target - if you want more emphasis on statements that include any target (helps when target PPV is a key metric).
  seed = 2025
)


sampled_df <- sample_result$sample %>%
  ##' creates this `stratum` column to
  ##'   Ensures coders see both common and rare targets, not just common ones
  ##'   Balanced coverage across engagement levels
  mutate(stratum = paste0(any_rare_goal, "_", engagement_llm)) 
  
  
sample_result$diagnostics$per_goal_sample_counts
sample_result$diagnostics$rare_rate


##' Or rare_rule = "topk" with topk_common = 5 to define “common = top-5 most frequent; rest rare”.
##' 
##' Diversity check: Ensure filled_n is large enough to give variety beyond the guaranteed picks.
sample_result$diagnostics$filled_n

library(scales)

pct_ensured <- (sample_result$diagnostics$ensured_n) / N_total_sample ## Aim for ~20–35%. 
pct_ensured_str <- scales::percent(pct_ensured, accuracy = 0.1)
pct_random_str  <- scales::percent(1 - pct_ensured, accuracy = 0.1)

cat(
  pct_ensured_str, "of your sample came from the guaranteed-minimum stage [aiming for 20-35%],",
  "and the rest (~", pct_random_str, ") came from weighted random sampling.\n"
)

##' 
##' Parameter tuning:
##' If this percentage is too high (>50%), your random stage may be too small, reducing diversity. 
##'   We can 1) increase `N_total`, 2) Lower `min_per_goal` cap.
##' If this percentage is too low (<5%), your coverage rule may not be doing much — and rare goals might be missed.
##' 
```



```{r - save sample data}

f <- paste0(dir.assignments, 'sample_result.RData') ## `sample_result`, `sampled_df`
save(sample_result, sampled_df, file = f)

```




```{r - sample stats / plots}

# ---- Requirements ----
library(dplyr)
library(tidyr)
library(stringr)
library(forcats)
library(ggplot2)
library(scales)

# df: full dataset with columns statement_id and goals_llm (semicolon-separated)
# sample_result: output from sample_statements(df, ...)
#   - sample_result$sample (sampled statements with primary_goal, any_rare_goal, etc.)
#   - sample_result$goal_frequency (goal-level frequency table with 'rarity' column)

build_goal_distribution_plot <- function(df, sample_result, label_percent_accuracy = 0.1) {

  # 1) Compute ORIGINAL per-statement primary_goal (match the sampler’s logic)
  orig_goals_long <- df %>%
    mutate(goals_llm = if_else(is.na(goals_llm), "", goals_llm)) %>%
    tidyr::separate_rows(goals_llm, sep = ",\\s*") %>%
    mutate(goals_llm = str_to_upper(str_trim(goals_llm))) %>%
    filter(goals_llm != "")

  orig_per_stmt <- orig_goals_long %>%
    group_by(statement_id) %>%
    summarise(primary_goal = first(sort(unique(goals_llm))), .groups = "drop")

  original_counts <- orig_per_stmt %>%
    count(primary_goal, name = "count_original")

  # 2) SAMPLED per-statement primary_goal (already present in sample_result$sample)
  sampled_counts <- sample_result$sample %>%
    filter(!is.na(primary_goal), primary_goal != "NA") %>%
    count(primary_goal, name = "count_sampled")

  # 3) Merge + rarity from sample_result$goal_frequency (goal-level rarity)
  rarity_map <- sample_result$goal_frequency %>%
    transmute(primary_goal = goals_llm, rarity)

  df_counts <- full_join(original_counts, sampled_counts, by = "primary_goal") %>%
    replace_na(list(count_original = 0L, count_sampled = 0L)) %>%
    left_join(rarity_map, by = "primary_goal") %>%
    mutate(rarity = if_else(is.na(rarity), "COMMON", rarity)) %>%
    filter(!is.na(primary_goal), primary_goal != "NA") %>%
    ## Reorder primary_goal by count_original
    mutate(primary_goal = forcats::fct_reorder(primary_goal, count_original, .desc = TRUE)  )

  # 4) Long format + percentages
  df_long <- df_counts %>%
    pivot_longer(cols = c(count_original, count_sampled),
                 names_to = "set", values_to = "count") %>%
    mutate(set = recode(set,
                        count_original = "Original",
                        count_sampled  = "Sampled"))

  # Totals for percent
  totals <- df_long %>%
    group_by(set) %>% 
    summarise(total = sum(count), .groups = "drop")

  df_long <- df_long %>%
    left_join(totals, by = "set") %>%
    mutate(pct = if_else(total > 0, 100 * count / total, 0))

  # 5) Determine which goals are "oversampled rare":
  # rare goal AND (Sampled % > Original %)
  wide_pct <- df_long %>%
    select(primary_goal, set, pct) %>%
    pivot_wider(names_from = set, values_from = pct, values_fill = 0)

  df_counts <- df_counts %>%
    left_join(wide_pct, by = "primary_goal") %>%
    mutate(oversampled_rare = rarity == "RARE" & (Sampled > Original)) 

  # 6) Order goals by Original share (or change to Sampled if you prefer)
  goal_order <- df_long %>%
    filter(set == "Original") %>%
    arrange(desc(pct)) %>%
    pull(primary_goal)

  df_long <- df_long %>%
    mutate(primary_goal = factor(primary_goal, levels = goal_order))

  # 7) Aesthetic category for outline color
  #    "Rare (oversampled)" vs "Rare" vs "Common"
  goal_category <- df_counts %>%
    transmute(primary_goal,
              goal_cat = case_when(
                oversampled_rare ~ "Rare (oversampled)",
                rarity == "RARE" ~ "Rare",
                TRUE ~ "Common"
              ))

  df_long <- df_long %>% 
    left_join(goal_category, by = "primary_goal")

  # 8) Build the plot
  p <- ggplot(df_long, aes(x = primary_goal, y = pct, fill = set, color = goal_cat)) +
    geom_col(position = position_dodge(width = 0.8), width = 0.75, alpha = 0.9) +
    # bar labels: count + percent
    geom_text(
      aes(label = paste0(count, "\n(", percent(pct/100, accuracy = label_percent_accuracy), ")")),
      position = position_dodge(width = 0.8),
      vjust = -0.35, 
      size = 2, ## in mm
      show.legend = FALSE
    ) +
    labs(
      x = NULL,
      y = "Share of statements (%)",
      title = "SDG Goal Distribution: Original vs Sampled",
      subtitle = "Bars show percentage within each set; labels show count (percent)",
      fill = "Set",
      color = "Goal Type"
    ) +
    ## Formatting 
    scale_y_continuous(labels = function(x) paste0(x, "%"), expand = expansion(mult = c(0.02, 0.1))) +
    # Colors: keep fills for Original/Sampled; outline color for goal type
    scale_fill_manual(values = c("Original" = "#9fb5d0", "Sampled" = "#3a6ea5")) +
    scale_color_manual(values = c(
      "Common" = "#666666",
      "Rare" = "#bb8800",
      "Rare (oversampled)" = "#d22000"
    )) +
    guides(color = guide_legend(override.aes = list(fill = NA)) ) +
    theme_minimal(base_size = 7) +
    theme(
      text = element_text(size = 7),                # global default for all text
      legend.key = element_rect(fill = "transparent", colour = NA), # remove gray box
      legend.position = c(0.8, 0.6),
      # axis.text.x = element_text(angle = 45, hjust = 1),
      panel.grid.major.x = element_blank(),
      panel.grid.minor = element_blank()
    )

  list(
    plot = p,
    table = df_long %>%
      select(primary_goal, set, count, pct, rarity = goal_cat) %>%
      arrange(primary_goal, set),
    oversampled_rare_goals = df_counts %>% filter(oversampled_rare) %>% pull(primary_goal)
  )
}



# After you run:
#   sample_result <- sample_statements(df, N_total = 800, min_per_goal = 10, rare_rule = "prevalence", rare_threshold = 0.05)


# Build the plot -------------------------------------------------------------------------
viz <- build_goal_distribution_plot(df = llm_sub_, sample_result)

# Inspect the tidy table (counts + %)
head(viz$table)

# Which goals are rare AND oversampled?
viz$oversampled_rare_goals

# Show the plot
print(viz$plot)

ggsave(
  filename = paste0("./figures/sdg_llm_sampling_distribution_", ymd, ".png"),
  plot = viz$plot,
  width = 7, height = 5, unit = 'in', dpi = 300
)

```



## Assignment with double-coding

```{r - coder list}

# INPUTS ---------------------------------------------------------------
set.seed(2025)

annotators <- c("A01","A02","A03", "A04", "A05", "A06")  # 6–10 experts

```


### Plan 1 - double only 
  

```{r - double-annotated}

per_item_coders <- 2                                     # double-coding
triple_share <- 0.10                                     # 20% triple-annotated
duplicate_rate <- 0.05                                   # 5% or 10% per coder

# sampled_df: sample_result$sample from your sampler (one row per statement)
# Expected columns at minimum:
#   statement_id, statement_text, stratum,
#   llm_pred_target, llm_pred_engagement, primary_goal (optional)
stopifnot(all(c("statement_id", "statement") %in% names(sampled_df)))

# 1) Build coder pairs per statement (round-robin by stratum to keep balance)
# ---------------------------------------------------------------------------
# Strategy: within each stratum, rotate coder pairs so each coder sees a fair mix.
pair_grid <- t(combn(annotators, per_item_coders)) %>% as.data.frame()
names(pair_grid) <- paste0("coder_", seq_len(per_item_coders))
stopifnot(nrow(pair_grid) > 0)  # ensure combinations exist

assign_pairs <- function(df_stratum) {
  n <- nrow(df_stratum)
  if (n == 0) return(df_stratum)  # nothing to assign
  # repeat the pair grid to at least n rows (THIS was the bug)
  pairs_rep <- pair_grid[rep(seq_len(nrow(pair_grid)), length.out = n), , drop = FALSE]

  bind_cols(df_stratum, pairs_rep)
}

assigned_pairs <- sampled_df %>%
  mutate(.strat_order = row_number()) %>%                 # stable order
  group_by(stratum) %>%
  arrange(.strat_order, .by_group = TRUE) %>%
  group_modify(~assign_pairs(.x)) %>%
  ungroup() %>%
  select(-.strat_order)


## --> quick check 
# 1) No NA coders
assigned_pairs %>% summarise(
  n = n(),
  na_coder1 = sum(is.na(coder_1)),
  na_coder2 = sum(is.na(coder_2))
)

# 2) Per-coder load
assigned_pairs %>%
  pivot_longer(starts_with("coder_"), names_to = "slot", values_to = "coder_id") %>%
  count(coder_id, name = "items") %>%
  arrange(desc(items))


# 2) Convert wide (coder_1, coder_2) to long (one row per (statement, coder))
# ---------------------------------------------------------------------------
assign_long <- assigned_pairs %>%
  pivot_longer(cols = starts_with("coder_"),
               names_to = "coder_slot", values_to = "coder_id") %>%
  mutate(is_duplicate = 0L,
         duplicate_group_id = NA_character_)
```



```{r - add salted duplicates}


# 3) Add salted duplicates per coder (~duplicate_rate of their unique items)
# ---------------------------------------------------------------------------
source(here('code', 'function_inject_duplicates.R'))

assignment_per_coder <- assign_long %>%
  group_split(coder_id) %>%
  map_df(~inject_duplicates(.x, dup_rate = duplicate_rate))

# 4) Create per-coder CSVs and a master assignment table
# ---------------------------------------------------------------------------
# # (Uncomment to write files)
# dir.create(dir.assignments, showWarnings = FALSE)
# assignment_per_coder %>%
#   group_by(coder_id) %>%
#   group_walk(~ readr::write_csv(.x, file = file.path("assignments", paste0(.y$coder_id[1], "_queue.csv"))))

assignment_master <- assignment_per_coder %>%
  arrange(coder_id, statement_id)


## Check the master assignment
total_dupes <- sum(assignment_master$is_duplicate, na.rm = TRUE)
dupes_per_coder <- total_dupes / length(annotators)

cat(
  total_dupes, "total duplicates injected across all coders.\n",
  "On average,", round(dupes_per_coder, 1), "duplicates per coder.\n"
)

```


### Plan 2 - double + triple

  The pilot coding was conducted using this approach. 
  
  Then, we changed to Plan 3 based on group feedback and discussion. 

```{r - triple-annotated}

library(dplyr)
library(tidyr)
library(purrr)

# -------------------------
# Inputs
# -------------------------
### >= 3 coders needed
stopifnot(length(annotators) >= 3) # need at least 3 for triples


# assignment knobs
per_item_coders_default <- 2      # double-annotated baseline
triple_share   <- 0.10            # 10% triple-annotated or 20% if you prefer
duplicate_rate <- 0.05            # 5% salted duplicates per coder



# Make coder combination grids
pair_grid   <- t(combn(annotators, 2)) |> as.data.frame()
triple_grid <- t(combn(annotators, 3)) |> as.data.frame()
names(pair_grid)   <- paste0("coder_", 1:2)
names(triple_grid) <- paste0("coder_", 1:3)
stopifnot(nrow(pair_grid) > 0, nrow(triple_grid) > 0)


# Helper: repeat a grid to length n and bind as columns with df
assign_k <- function(df_group, grid){
  n <- nrow(df_group)
  if (n == 0) return(df_group)
  grid_rep <- grid[rep(seq_len(nrow(grid)), length.out = n), , drop = FALSE]
  bind_cols(df_group, grid_rep)
}

# -------------------------
# Choose triple-annotated statements (stratified if `stratum` exists)
# -------------------------
if ("stratum" %in% names(sampled_df)) {
  picked <- sampled_df %>%
    group_by(stratum) %>%
    mutate(.row = row_number()) %>%
    group_modify(~{
      n_triple <- ceiling(nrow(.x) * triple_share)
      .x %>%
        dplyr::slice_sample(n = min(n_triple, nrow(.x))) %>%
        mutate(triple_flag = TRUE)
    }) %>%
    ungroup() %>%
    select(statement_id, triple_flag)

  sampled_marked <- sampled_df %>%
    left_join(picked, by = "statement_id") %>%
    mutate(triple_flag = if_else(is.na(triple_flag), FALSE, triple_flag))
} else {
  n_triple <- ceiling(nrow(sampled_df) * triple_share)
  ids_triple <- sampled_df %>% slice_sample(n = n_triple) %>% pull(statement_id)
  sampled_marked <- sampled_df %>%
    mutate(triple_flag = statement_id %in% ids_triple)
}

# -------------------------
# Assign coders: triples get 3, others get 2
# -------------------------
triples <- sampled_marked %>% filter(triple_flag)
pairs   <- sampled_marked %>% filter(!triple_flag)

assigned_triples_wide <- assign_k(triples, triple_grid)   # adds coder_1..coder_3
assigned_pairs_wide   <- assign_k(pairs,   pair_grid)     # adds coder_1..coder_2

assigned_wide <- bind_rows(assigned_pairs_wide, assigned_triples_wide)

# -------------------------
# Long format (one row per statement × coder)
# -------------------------
assigned_long <- assigned_wide %>%
  pivot_longer(
    cols = starts_with("coder_"),
    names_to = "coder_slot",
    values_to = "coder_id"
  ) %>%
  filter(!is.na(coder_id)) %>%            # keep only real slots (pairs won’t have coder_3)
  mutate(
    is_duplicate = 0L,
    duplicate_group_id = NA_character_
  )

# -------------------------
# (Optional) inject salted duplicates per coder (~10%)
# Reuse your working inject_duplicates() that preserves coder_id.
# -------------------------
per_coder_queues <- assigned_long %>%
  group_split(coder_id) %>%
  map_df(~inject_duplicates(.x, dup_rate = duplicate_rate))

## or if you’re not injecting duplicates immediately:
# per_coder_queues <- assigned_long
```


```{r - export tasks}

# ================================
# 5) Exports: per-coder CSVs + master
# ================================

dir.create(dir.assignments, showWarnings = FALSE)


# Per-coder queues ------
per_coder_queues_clean <- per_coder_queues %>%
  ## remove unnecessary columns 
  select(-any_of(c("company", "year", "primary_goal", "goals", "any_rare_goal", "has_target", 
                   "weight", "triple_flag", "is_duplicate", "duplicate_group_id", 
                   "goals_llm",
                   "coder_slot", "stratum"))) %>%
  ## add additional columns
  mutate(
    targets_coder        = NA_character_,
    targets_rationale    = NA_character_,
    engagement_coder     = NA_character_,
    engagement_rationale = NA_character_,
    comments_coder       = NA_character_,

  ) %>%
  ## change the order of columns 
  select(coder_id, statement_id, statement, 
         targets_nlp,	
         targets_llm,	   targets_coder,	   targets_rationale,
         engagement_llm, engagement_coder, engagement_rationale,
         comments_coder, 
         everything()) 
names(per_coder_queues_clean)


# Master assignments (for tracking) ------
assignment_master <- per_coder_queues_clean %>%
  arrange(coder_id, statement_id)
# readr::write_csv(assignment_master, file.path(dir.assignments, "master_assignments.csv"))



## ===================================================== #
## split the tasks and save as CSV / xlsx files
## ===================================================== #

##' 1. easy and quick CSV export
# per_coder_queues_clean %>%
#   group_by(coder_id) %>%
#   # group_walk(~ readr::write_csv(.x, file = file.path(dir.assignments, paste0(.y$coder_id[1], "_queue.csv"))))
#   group_walk(~ writexl::write_xlsx(.x, path = file.path(dir.assignments, paste0(.y$coder_id[1], "_queue.xlsx"))))


##' 2. xlsx export with styles

xlsx_postfix <- paste0("_queue_", 'YourFirstName',".xlsx"); xlsx_postfix
# source('./code/helper_write_xlsx_with_style.R')

```



```{r - diagnostics summary}

# -------------------------
# Sanity checks
# -------------------------

total_dupes <- sum(assignment_master$is_duplicate, na.rm = TRUE)
dupes_per_coder <- total_dupes / length(annotators)
cat(
  total_dupes, "total duplicates injected across all coders.\n",
  "On average,", round(dupes_per_coder, 1), "duplicates per coder.\n"
)


# % triple annotated
pct_triple <- mean(sampled_marked$triple_flag)
message("Triple-annotated share = ", scales::percent(pct_triple, accuracy = 0.1))

pct_ensured <- (sample_result$diagnostics$ensured_n) / N_total_sample
cat("Ensured stage share:", percent(pct_ensured, accuracy = 0.1), "\n")

# No NAs in coder_id
stopifnot(sum(is.na(per_coder_queues$coder_id)) == 0)

# Per-coder load overview
load_table <- per_coder_queues %>%
  count(coder_id, name = "items") %>%
  arrange(desc(items))
print(load_table)

# How many triples vs pairs?
table_triple <- sampled_marked %>% count(triple_flag, name = "n_statements")
print(table_triple)

```



