---
title: "Text_mining"
author: "Yingjie"
date: "01/23/2022"
output: html_document
editor_options: 
  chunk_output_type: inline
---


  This script aims to validate the LLM results. 
  
  **Before clicking Run All**
  - update `nth_round` 
  
  

# Directories and packages

```{r include=FALSE}

### To clear your environment
remove(list = ls())

## set work dir
getwd()


# load packages
source('./Code/_packages.R')
source('./code/_directories.R')

library(here)
library(readxl)
library(dplyr)
library(stringr)
library(purrr)
library(tidyr)
library(conflicted)

# Fail loudly on ambiguous function names:
conflict_prefer("filter", "dplyr")
conflict_prefer("lag",    "dplyr")
conflict_prefer("select", "dplyr")
conflict_prefer("rename", "dplyr")
conflict_prefer("slice",  "dplyr")
conflict_prefer("summarise", "dplyr")   # or "summarize" if you use that alias
conflict_prefer("arrange",   "dplyr")
conflict_prefer("mutate",    "dplyr")
conflict_prefer("distinct",  "dplyr")
conflict_prefer("count",     "dplyr")


ymd   <- format(Sys.time(), "%Y%m%d"); ymd


## load functions 
source(here('code', 'func_ggsave_nature.R'))
```



# Data in

## load data - specify which round

```{r}

gdrive <- "G:/Shared drives/gdrive/_paper/SDGs/SDGs_Corporations_g/data/data_LLM_validation/"

nth_round <- 1

dir.task1 <- paste0(gdrive, "llm_R", nth_round); dir.task1

cat('\n')



# 1) List files
fs <- list.files(path = dir.task1, pattern = "^B.*_task.*xlsx", full.names = T); fs

```


```{r}

library(stringr)
library(dplyr)

#' Excel and R both use IEEE-754 doubles; numbers like 10.2 can’t be represented exactly in binary, so you sometimes see 10.199999999999999 when R prints the full precision.
#' 
#' preserve explicit trailing zeros like "16.10" while still fixing ugly long tails such as "10.199999999999999", use a conditional cleanup: only reformat when the decimal tail is obviously an artifact; otherwise leave the token as-is.
#' 
#' 

# detect obvious long-tail artifacts (many trailing 9s/0s or very long decimals)
needs_rounding <- function(s) {
  m <- regexec("^([+-]?\\d+)\\.(\\d+)$", s)
  z <- regmatches(s, m)
  if (length(z) == 0 || length(z[[1]]) < 3) return(FALSE)
  dec <- z[[1]][3]
  nchar(dec) >= 8 || grepl("(9{4,}|0{4,})$", dec)
}

# Clean a mixed text column:
# - trims tokens
# - only rounds numeric-looking tokens with long-tail artifacts
# - preserves tokens like "16.10" exactly
clean_mixed_col <- function(x, digits = 3) {
  x_trim <- trimws(x)
  numish <- grepl("^[+-]?(\\d+\\.?|\\d*\\.\\d+)$", x_trim)

  out <- x_trim
  idx <- which(numish & vapply(x_trim, needs_rounding, logical(1)))

  if (length(idx)) {
    # round & then drop trailing zeros just for the artifacty ones
    rounded <- sprintf(paste0("%.", digits, "f"), as.numeric(x_trim[idx]))
    rounded <- sub("0+$", "", rounded)   # drop trailing zeros
    rounded <- sub("\\.$", "", rounded)  # drop trailing dot if any
    out[idx] <- rounded
  }
  out
}


```


```{r message=FALSE}

# 2) Vectorized coder IDs from filenames (e.g., "B01")
coders <- str_extract(basename(fs), "^B\\d{2}")

# 3) Fast read + bind all (adds coder + row index per file)
# df <- map2_dfr(
#   fs, coders,
#   ~ read_excel(.x, col_types = "text") %>%
#       mutate(coder = .y, index = row_number()) %>%
#       # convert back to best types, but keep goals_llm as character:
#       mutate(goals_llm = as.character(goals_llm)) #%>%
#       # type_convert() # guess other columns ,-- this step is very slow
# )


df <- map2_dfr(
  fs, coders,
  ~ read_excel(.x) %>%  # Remove col_types = "text"
      mutate(coder = .y, index = row_number()) %>%
      mutate(goals_llm = as.character(goals_llm))
) %>%
  mutate(targets_coder = clean_mixed_col(targets_coder)) 

```






# Data stats


## metrics 

```{r - F1 vs Jaccard}
```

Because F1 and Jaccard are equivalent up to a transform, including both in the main text is usually unnecessary. A pragmatic approach:

Main text: Per-label `F1` (pooled) with 95% CIs and support; overall micro/macro summaries; plus one prevalence-vs-performance figure.

  `F1 = 2TP / (2TP+FP+FN)`

Supplement: Provide `Jaccard` columns (or a simple note: `F1=2J/(1+J))` for completeness/sensitivity. Label-level Jaccard (IoU) across all statements

  `J = TP / (TP+FP+FN)`


Primary (recommended): Report per-label F1 (pooled/micro), because it’s the most familiar in multi-label classification, and pair it with support (how many statements contain that label in the consensus).

Also acceptable: Report Jaccard instead of F1 if your audience resonates more with set similarity / IoU (e.g., some IR/segmentation communities). It reads naturally as “fraction of hits among all opportunities to be right.




```{r - Precision vs Recall}
```

Precisionℓ = TPℓ / (TPℓ + FPℓ) — “when LLM predicts ℓ, how often is it right?”

Recallℓ = TPℓ / (TPℓ + FNℓ) — “when ℓ is truly present, how often does LLM find it?”

You can compute these either:

Pooled over all statements for each label (recommended for stability), or

Per statement and then average (rarely useful for precision/recall; more variance, odd edge cases).



**Averaging schemes (what you average over)**
Across labels (typical in multi-label)
  
  Macro_precision = meanℓ(Precisionℓ)
  
  Macro_recall = meanℓ(Recallℓ)
  
  Unweighted: treats rare and common labels equally (good to expose weak labels).
  
  Weighted-macro (optional): weight by label support (more stable if many rare labels).
  
  *Micro_precision / Micro_recall (pooled):*
  Compute one global TP, FP, FN by summing across all labels and statements, then:
  
  micro_precision = ΣTP / (ΣTP + ΣFP)
  
  micro_recall = ΣTP / (ΣTP + ΣFN)
  Micro averages are dominated by frequent labels and statements; they reflect overall performance under class imbalance.



When they differ (and why it matters)

*Macro vs Micro*

  Macro highlights performance on rare labels (each label counts equally).
  
  Micro highlights performance on common labels (counts are pooled; frequent labels dominate).

*Precision vs Recall trade-off*

  High precision + low recall ⇒ conservative (few false alarms, more misses).

  Low precision + high recall ⇒ aggressive (more hits, more false alarms).
  
  
  
## calculation 


This multi-coder, duplicate-aware pipeline that:

  parses labels robustly,
  
  handles repeated statement_id (reviewed by ≥2 coders),
  
  keeps within-coder duplicates for intra-coder reliability,
  
  builds an inter-coder consensus per statement (configurable threshold),
  
  compares LLM vs consensus and LLM vs each coder,
  
  returns per-statement, per-coder, and overall metrics.

```{r - para + functions}
# ==============================
# Params you can tweak
# ==============================
MIN_VOTES <- 2        # consensus threshold (label present if >= MIN_VOTES coders picked it)
BINWIDTH  <- 0.05     # for any histograms/plots later

# ==============================
# 1) Parsing helpers
# ==============================

#' Parse comma-separated numeric values from a string
#'
#' Takes a string containing comma-separated numbers and returns a numeric vector
#' of unique values. Handles empty strings, whitespace, and NA values gracefully.
#'
#' @param x A character string containing comma-separated numeric values
#'
#' @return A numeric vector of unique values. Returns an empty numeric vector
#'   if the input is NA, empty, or contains no valid numbers.
#'
#' @examples
#' parse_vals("1, 2, 3")           # Returns: c(1, 2, 3)
#' parse_vals("1, 2, 2, 3")        # Returns: c(1, 2, 3) (unique values)
#' parse_vals("1, NA, 3")          # Returns: c(1, 3)
#' parse_vals("")                  # Returns: numeric(0)
#' parse_vals(NA)                  # Returns: numeric(0)
#' parse_vals("  1 ,  2  ")        # Returns: c(1, 2) (trimmed whitespace)
#'
#' --- This function can only retain numbers but not string-like labels such as "13.a"
# parse_vals <- function(x) {
#   # Return empty vector if input is NA or empty string
#   if (is.na(x) || trimws(x) == "") return(numeric(0))
#   # Split string by commas
#   xs <- str_split(x, ",")[[1]]
#   # Remove leading/trailing whitespace from each element
#   xs <- str_trim(xs)
#   # Filter out empty strings and "NA" text
#   xs <- xs[xs != "" & xs != "NA"]
#   # Convert to numeric, suppress warnings for non-numeric values, return unique values
#   suppressWarnings(unique(as.numeric(xs)))
# }


#' --- An updated function
parse_vals <- function(x, 
                       canonical_numeric = TRUE,
                       squish_internal = TRUE) {
  # Empty -> character(0) to allow mixed tokens downstream
  if (is.na(x) || trimws(x) == "") return(character(0))
  
  
  # 1) normalize whitespace (handles Unicode spaces), split, trim
  x    <- str_replace_all(x, "[\\h\\v\\p{Z}]+", " ")
  
  # 1) split on commas
  toks <- str_split(x, ",")[[1]]

  # 2) trim leading/trailing whitespace for each token
  toks <- str_trim(toks)
  
  # 3) (optional) collapse internal runs of spaces to a single space
  if (squish_internal) toks <- str_squish(toks)
  
  # 4) drop empties and literal "NA"
  toks <- toks[toks != "" & toks != "NA"]
  if (!length(toks)) return(character(0))
  
  # Unique preserving first occurrence
  unique(toks)
}




# turn a list-column of numeric vectors into a long binary table against a label universe
make_binary_long <- function(df_list, id_cols, label_universe) {
  df_list %>%
    rowwise() %>%
    mutate(all_labels = list(label_universe)) %>%
    ungroup() %>%
    tidyr::unnest_longer(all_labels, values_to = "label") %>%
    mutate(y = map2_lgl(all_labels, labels, ~ .y %in% .x), .keep = "unused")
}
```


```{r - stats}

# ==============================
# 2) Normalize inputs
#    Expect columns: statement_id, coder_id, targets_coder, targets_llm
# ==============================
df_norm <- df %>%
  dplyr::rename('coder_id' = 'coder') %>%
  dplyr::mutate(
    coder_id      = as.character(coder_id),
    ## store sdg code in a vector format
    labels_coder  = map(targets_coder, parse_vals),
    labels_llm    = map(targets_llm,   parse_vals)
  ) %>%
  ## re-order columns
  select(1:targets_coder, labels_llm, labels_coder, coder_id, everything())

# one LLM set per statement: keep first non-empty; else empty
# llm_by_stmt0 <- df_norm %>% ## --> warning message
#   group_by(statement_id) %>%
#   summarise(
#     labels_llm = {
#       # first non-empty list, else empty
#       non_empty <- keep(labels_llm, ~ length(.x) > 0)
#       if (length(non_empty)) non_empty[[1]] else numeric(0)
#     },
#     .groups = "drop"
#   )



llm_by_stmt <- df_norm %>%
  group_by(statement_id) %>%
  summarise(
    labels_llm = {
      non_empty <- purrr::keep(labels_llm, ~ length(.x) > 0)
      list(if (length(non_empty)) non_empty[[1]] else numeric(0))
    },
    .groups = "drop"
  )


# ==============================
# 3) Build a label universe per statement (coders ∪ LLM)
# ==============================
universe_by_stmt <- df_norm %>%
  select(statement_id, labels_coder) %>%
  group_by(statement_id) %>%
  summarise(labels_union = list(sort(unique(unlist(labels_coder)))), .groups = "drop") %>%
  left_join(llm_by_stmt, by = "statement_id") %>%
  mutate(
    label_universe = map2(labels_union, labels_llm, ~ sort(unique(c(.x, .y))))
  ) %>%
  select(statement_id, labels_llm, label_universe)


# ==============================
# 4) Inter-coder “votes” table (binary, per statement × coder × label)
# ==============================
coder_long <- df_norm %>%
  select(statement_id, coder_id, labels_coder) %>%
  left_join(universe_by_stmt %>% select(statement_id, label_universe), by = "statement_id") %>%
  rowwise() %>%
  mutate(
    # expand across universe
    tmp = list(tibble(
      label = label_universe,
      y_true = label %in% labels_coder
    ))
  ) %>%
  ungroup() %>%
  select(statement_id, coder_id, tmp) %>%
  unnest(tmp)

# ==============================
# 5) Inter-coder consensus per statement (threshold MIN_VOTES)
# ==============================
consensus <- coder_long %>%
  group_by(statement_id, label) %>%
  summarise(votes = sum(y_true), n_coders = n(), .groups = "drop") %>%
  group_by(statement_id) %>%
  summarise(
    labels_consensus = list(sort(unique(label[votes >= MIN_VOTES]))),
    # diagnostics
    support_tbl = list(tibble(label = label, votes = votes, n_coders = n_coders)),
    .groups = "drop"
  )

# ==============================
# 6) Intra-coder reliability (duplicates of same coder & statement)
#    - If a coder coded the same statement multiple times, compare all pairs (Jaccard)
# ==============================
coder_sets <- df_norm %>%
  select(statement_id, coder_id, labels_coder)

intra_pairs <- coder_sets %>%
  group_by(statement_id, coder_id) %>%
  mutate(n_rows = n()) %>%
  filter(n_rows > 1) %>%
  mutate(row_id = row_number()) %>%
  ungroup() %>%
  # all pairs within coder×statement
  group_by(statement_id, coder_id) %>%
  tidyr::expand(row_id1 = row_id, row_id2 = row_id) %>%
  filter(row_id1 < row_id2) %>%
  left_join(coder_sets %>% group_by(statement_id, coder_id) %>% mutate(row_id = row_number()),
            by = c("statement_id","coder_id","row_id1"="row_id")) %>%
  rename(labels1 = labels_coder) %>%
  left_join(coder_sets %>% group_by(statement_id, coder_id) %>% mutate(row_id = row_number()),
            by = c("statement_id","coder_id","row_id2"="row_id")) %>%
  rename(labels2 = labels_coder) %>%
  ungroup() %>%
  mutate(
    inter_len = map2_int(labels1, labels2, ~ length(intersect(.x, .y))),
    union_len = map2_int(labels1, labels2, ~ length(union(.x, .y))),
    jaccard   = ifelse(union_len > 0, inter_len/union_len, NA_real_)
  )

intra_summary <- intra_pairs %>%
  group_by(coder_id) %>%
  summarise(
    n_dup_pairs = n(),
    mean_jaccard_dup = mean(jaccard, na.rm = TRUE),
    median_jaccard_dup = median(jaccard, na.rm = TRUE),
    .groups = "drop"
  )

# ==============================
# 7) LLM vs CONSENSUS — per statement metrics
# ==============================
llm_vs_consensus <- universe_by_stmt %>%
  left_join(consensus, by = "statement_id") %>%
  mutate(
    labels_consensus = map(labels_consensus, ~ .x %||% numeric(0)),
    inter_len = map2_int(labels_llm, labels_consensus, ~ length(intersect(.x, .y))),
    union_len = map2_int(labels_llm, labels_consensus, ~ length(union(.x, .y))),
    tp = inter_len,
    fp = map2_int(labels_llm, labels_consensus, ~ length(setdiff(.x, .y))),
    fn = map2_int(labels_consensus, labels_llm, ~ length(setdiff(.x, .y))),
    precision = ifelse(tp + fp > 0, tp/(tp+fp), NA_real_),
    recall    = ifelse(tp + fn > 0, tp/(tp+fn), NA_real_),
    f1        = ifelse(!is.na(precision + recall) & (precision + recall) > 0,
                       2*precision*recall/(precision+recall), NA_real_),
    jaccard   = ifelse(union_len > 0, inter_len/union_len, NA_real_),
    exact_match = as.integer(jaccard == 1),
    any_overlap = as.integer(inter_len > 0)
  ) %>%
  select(statement_id, precision, recall, f1, jaccard, exact_match, any_overlap, tp, fp, fn)

# overall macro/micro for LLM vs consensus
macro_consensus <- llm_vs_consensus %>%
  summarise(
    macro_precision = mean(precision, na.rm = TRUE),
    macro_recall    = mean(recall,    na.rm = TRUE),
    macro_f1        = mean(f1,        na.rm = TRUE),
    mean_jaccard    = mean(jaccard,   na.rm = TRUE),
    exact_match_rate= mean(exact_match, na.rm = TRUE),
    any_overlap_rate= mean(any_overlap, na.rm = TRUE)
  )


micro_consensus <- llm_vs_consensus %>%
  summarise(
    tp = sum(tp), fp = sum(fp), fn = sum(fn)
  ) %>%
  mutate(
    micro_precision = ifelse(tp + fp > 0, tp/(tp+fp), NA_real_),
    micro_recall    = ifelse(tp + fn > 0, tp/(tp+fn), NA_real_),
    micro_f1        = ifelse(!is.na(micro_precision + micro_recall) & (micro_precision + micro_recall) > 0,
                             2*micro_precision*micro_recall/(micro_precision+micro_recall), NA_real_)
  ) %>% select(micro_precision, micro_recall, micro_f1)

# ==============================
# 8) LLM vs EACH CODER — per-coder and overall
# ==============================
# Per row (coder×statement), compare LLM to that coder
llm_vs_coder_row <- df_norm %>%
  select(statement_id, coder_id, labels_coder) %>%
  left_join(llm_by_stmt, by = "statement_id") %>%
  mutate(
    inter_len = map2_int(labels_llm, labels_coder, ~ length(intersect(.x, .y))),
    union_len = map2_int(labels_llm, labels_coder, ~ length(union(.x, .y))),
    tp = inter_len,
    fp = map2_int(labels_llm, labels_coder, ~ length(setdiff(.x, .y))),
    fn = map2_int(labels_coder, labels_llm, ~ length(setdiff(.x, .y))),
    precision = ifelse(tp + fp > 0, tp/(tp+fp), NA_real_),
    recall    = ifelse(tp + fn > 0, tp/(tp+fn), NA_real_),
    f1        = ifelse(!is.na(precision + recall) & (precision + recall) > 0,
                       2*precision*recall/(precision+recall), NA_real_),
    jaccard   = ifelse(union_len > 0, inter_len/union_len, NA_real_)
  )

# Aggregate per coder
llm_vs_coder_bycoder <- llm_vs_coder_row %>%
  group_by(coder_id) %>%
  summarise(
    macro_precision = mean(precision, na.rm = TRUE),
    macro_recall    = mean(recall,    na.rm = TRUE),
    macro_f1        = mean(f1,        na.rm = TRUE),
    mean_jaccard    = mean(jaccard,   na.rm = TRUE),
    n_rows          = n(),
    .groups = "drop"
  ) %>%
  left_join(intra_summary, by = "coder_id")  # attach intra-coder dup stats

# Overall micro across all coder rows
llm_vs_coder_micro <- llm_vs_coder_row %>%
  summarise(tp = sum(tp), fp = sum(fp), fn = sum(fn)) %>%
  mutate(
    micro_precision = ifelse(tp + fp > 0, tp/(tp+fp), NA_real_),
    micro_recall    = ifelse(tp + fn > 0, tp/(tp+fn), NA_real_),
    micro_f1        = ifelse(!is.na(micro_precision + micro_recall) & (micro_precision + micro_recall) > 0,
                             2*micro_precision*micro_recall/(micro_precision+micro_recall), NA_real_)
  ) %>% select(micro_precision, micro_recall, micro_f1)

# ==============================
# 9) Inter-coder agreement diagnostics (optional)
#    - label-level vote fractions per statement (helps find contentious labels)
# ==============================
vote_detail <- coder_long %>%
  group_by(statement_id, label) %>%
  summarise(vote_frac = mean(y_true), voters = n(), votes = sum(y_true), .groups = "drop")

# ==============================
# 10) Key outputs
# ==============================
# - llm_vs_consensus : per-statement metrics of LLM vs consensus
# - macro_consensus, micro_consensus : overall metrics vs consensus
# - llm_vs_coder_row : per (coder×statement) metrics of LLM vs that coder
# - llm_vs_coder_bycoder : per-coder aggregates + intra-coder dup stats
# - llm_vs_coder_micro : overall pooled metrics vs coders
# - vote_detail : per statement×label vote fractions (useful for audits)
# - intra_summary : duplicate consistency per coder


```

# Plot

```{r}

font_size_base = 10

# Set theme default
theme_set(theme_minimal(base_size = font_size_base))

# # Or update theme defaults
# theme_update(text = element_text(size = font_size_base))

```


## 1) Distribution of agreement (LLM vs consensus)

**Why:** overall similarity signal; easy to cite.
**What:** histogram (or density) of per-statement Jaccard; dashed mean.


```{r}

df_plot <- llm_vs_consensus |> filter(!is.na(jaccard))
m <- mean(df_plot$jaccard, na.rm = TRUE)


p_hist <-
  ggplot(df_plot, aes(jaccard)) +
  geom_histogram(binwidth = 0.05, color = "white") +
  geom_vline(xintercept = m, linetype = "dashed") +
  annotate("text", x = m, y = Inf, vjust = 1.4,
           label = sprintf("Mean = %.2f", m)) +
  # scale_x_continuous(limits = c(0,1), breaks = seq(0,1,0.2)) +
  labs(x = "Jaccard similarity (LLM vs consensus)", y = "Count") 

p_hist
```



## 2) Precision–Recall scatter per statement (LLM vs consensus)

**Why:** separates over- vs under-prediction at the item level.
**What:** scatter of precision vs recall; size by #labels in consensus; color by exact match.

```{r}

p_pr <- ggplot(
  llm_vs_consensus, aes(precision, recall)) +
  geom_point(aes(size = tp + fn, shape = factor(exact_match)), alpha = 0.7) +
  coord_equal() +
  scale_shape_discrete(name = "Exact match") +
  scale_size_continuous(name = "Consensus labels") +
  labs(x = "Precision", y = "Recall") 


p_pr
```



---

## 3) Per-coder performance bars (LLM vs each coder)

**Why:** shows heterogeneity across coders; pairs well with intra-coder reliability.
**What:** bar/point-range of macro-F1 (and Jaccard) per coder; overlay duplicate reliability.

```{r}
p_coder <- 
  ggplot(llm_vs_coder_bycoder,
         aes(x = reorder(coder_id, macro_f1), y = macro_f1)) +
  geom_col(width = 0.6, alpha = 0.5) +
  geom_point(aes(y = mean_jaccard_dup), shape = 21, stroke = 1, size = 3) +
  geom_hline(yintercept = 0.5, linetype = 'dashed', colour = 'blue') + 
  geom_hline(yintercept = 1,   linetype = 'dashed', colour = 'blue') + 
  coord_flip() +
  labs(x = "Coder", y = "Macro F1 (points = mean duplicate Jaccard)") 


p_coder
```



## 4) Intra-coder duplicate reliability (per coder)

**Why:** documents consistency within coder; reviewers love this.
**What:** violin/box of duplicate-pair Jaccard by coder.

```{r}

# p_dup <- 
  ggplot(intra_pairs, aes(x = reorder(coder_id, jaccard, FUN = mean), y = jaccard)) +
  geom_violin(trim = T, alpha = .7) +
  geom_boxplot(width = 0.15, colour = 'blue', outlier.shape = NA) +
  coord_flip() +
  labs(x = "Coder", y = "Jaccard across duplicate pairs") 


```



## ? 5) Label prevalence vs performance

**Why:** performance usually tracks prevalence; highlights rare-label issues.
**What:** for each label, plot support (coder votes or consensus count) on x vs F1/Jaccard on y.

```{r eval=FALSE, include=FALSE}
# Label support (how many statements include the label in consensus)
label_support <- vote_detail |>
  dplyr::group_by(label) |>
  dplyr::summarise(consensus_support = sum(vote_frac >= 2/7), .groups="drop")

# Label-wise performance (LLM vs consensus)
by_label_perf <- llm_vs_coder_row |>
  dplyr::group_by(label = NULL) # (if you compute label-level TP/FP/FN, join here)

# Example using coder-level support vs LLM-vs-coder Jaccard mean
lab_perf <- df_long |>
  dplyr::group_by(label) |>
  dplyr::summarise(support = sum(y_true), .groups="drop") |>
  dplyr::left_join(
    llm_vs_coder_row |>
      dplyr::mutate(label_set = purrr::map2(labels_coder, labels_llm, ~intersect(.x,.y))) |>
      tidyr::unnest_longer(label_set, values_to="label") |>
      dplyr::group_by(label) |>
      dplyr::summarise(mean_jaccard = mean(jaccard, na.rm=TRUE), .groups="drop"),
    by = "label"
  )

ggplot(lab_perf, aes(support, mean_jaccard)) +
  geom_point() +
  scale_x_log10() +
  labs(x = "Label support (log scale)", y = "Mean Jaccard")
```

*(If you prefer, compute TP/FP/FN per label vs consensus and plot F1 instead.)*




```{r}
library(dplyr)
library(tidyr)
library(purrr)
library(ggplot2)

# ---------------------------
# 5) Label prevalence vs performance
# ---------------------------
# Goal:
#  - For each label, compute its prevalence (support) in the CONSENSUS
#  - Compute LLM performance vs CONSENSUS aggregated across all statements:
#       TP = LLM & CONS
#       FP = LLM & !CONS
#       FN = !LLM & CONS
#  - Derive Precision, Recall, F1, Jaccard per label
#  - (Optional) Add coder vote-based prevalence diagnostics

# Ensure 'labels_consensus' exists and replace NULL with empty numeric(0)
cons_fix <- consensus %>%
  mutate(labels_consensus = map(labels_consensus, ~ .x %||% numeric(0)))

# Build long table over the label universe for each statement,
# with booleans for "in LLM" and "in CONSENSUS"
label_long <- universe_by_stmt %>%
  # universe_by_stmt: statement_id, labels_llm, label_universe
  left_join(cons_fix, by = "statement_id") %>%
  tidyr::unnest_longer(label_universe, values_to = "label") %>%
  mutate(
    in_llm  = map2_lgl(labels_llm,       label, ~ .y %in% .x),
    in_cons = map2_lgl(labels_consensus, label, ~ .y %in% .x)
  )

# Aggregate to label-level counts and metrics
label_perf <- label_long %>%
  group_by(label) %>%
  summarise(
    support   = sum(in_cons), # how many statements include this label in consensus
    tp        = sum(in_llm  & in_cons),
    fp        = sum(in_llm  & !in_cons),
    fn        = sum(!in_llm & in_cons),
    precision = ifelse(tp + fp > 0, tp / (tp + fp), NA_real_),
    recall    = ifelse(tp + fn > 0, tp / (tp + fn), NA_real_),
    f1        = ifelse(!is.na(precision + recall) & (precision + recall) > 0,
                       2 * precision * recall / (precision + recall), NA_real_),
    jaccard   = ifelse((tp + fp + fn) > 0, tp / (tp + fp + fn), NA_real_),
    .groups = "drop"
  ) %>%
  arrange(desc(support))


label_perf %>%
  ggplot(aes(x=f1, y = jaccard)) +
  geom_point() +
  labs(title = 'F1 vs Jaccard')


#' (Optional) Add coder vote diagnostics: total votes and mean vote fraction per label
#' The optional mean_vote_frac color scale helps reviewers see that rare & contentious labels (low vote fraction) typically have lower F1

label_votes <- vote_detail %>%           # from earlier: statement_id, label, vote_frac, voters, votes
  group_by(label) %>%
  summarise(
    total_votes    = sum(votes, na.rm = TRUE),
    n_stmt_voted   = n(),                         # count of (statement,label) entries observed
    mean_vote_frac = mean(vote_frac, na.rm = TRUE),
    .groups = "drop"
  )

label_perf <- label_perf %>%
  left_join(label_votes, by = "label")

# ---------------------------
# Plots
# ---------------------------

# A) Support vs F1 (primary)
ggplot(label_perf, aes(x = support, y = f1)) +
  geom_point() +
  # optional smoother if you like trend lines:
  # geom_smooth(method = "loess", se = TRUE, formula = y ~ x, span = 0.75) +
  scale_x_continuous(trans = "log10") +
  labs(
    x = "Label support in consensus (log scale)",
    y = "F1 (LLM vs consensus)",
    title = "Label prevalence vs performance"
  ) +
  theme_minimal()

# B) Support vs Jaccard (alternative / supplement)
ggplot(label_perf, aes(x = support, y = jaccard)) +
  geom_point() +
  scale_x_continuous(trans = "log10") +
  labs(
    x = "Label support in consensus (log scale)",
    y = "Jaccard (LLM vs consensus)",
    title = "Label prevalence vs Jaccard"
  ) +
  theme_minimal()

# C) If you want to color by mean_vote_frac (how contentious a label is):
ggplot(label_perf, aes(x = support, y = f1, color = mean_vote_frac)) +
  geom_point() +
  scale_x_continuous(trans = "log10") +
  scale_color_viridis_c(option = "C", end = 0.9) +
  labs(
    x = "Label support in consensus (log scale)",
    y = "F1 (LLM vs consensus)",
    color = "Mean vote fraction",
    title = "Label prevalence vs F1, colored by coder agreement"
  ) +
  theme_minimal()

```
```{r -boost-trap}

library(dplyr)
library(tidyr)
library(purrr)
library(ggplot2)
library(scales)



# ---------------------------
# Bootstrap CIs for F1 & Jaccard (per label)
# ---------------------------
set.seed(42)
n_boot <- 1000  # adjust as needed

all_stmts <- label_long %>% distinct(statement_id) %>% pull()

boot_res <- map_dfr(seq_len(n_boot), function(i) {
  samp_ids <- sample(all_stmts, length(all_stmts), replace = TRUE)

  label_long %>%
    filter(statement_id %in% samp_ids) %>%
    group_by(label) %>%
    summarise(
      tp = sum(in_llm & in_cons),
      fp = sum(in_llm & !in_cons),
      fn = sum(!in_llm & in_cons),
      f1_boot = {
        prec <- ifelse(tp + fp > 0, tp / (tp + fp), NA_real_)
        rec  <- ifelse(tp + fn > 0, tp / (tp + fn), NA_real_)
        ifelse(!is.na(prec + rec) & (prec + rec) > 0, 2 * prec * rec / (prec + rec), NA_real_)
      },
      jacc_boot = ifelse((tp + fp + fn) > 0, tp / (tp + fp + fn), NA_real_),
      .groups = "drop"
    ) %>%
    mutate(iter = i)
})

# Summarise bootstrap into CIs (95%)
boot_ci <- boot_res %>%
  group_by(label) %>%
  summarise(
    f1_lo    = quantile(f1_boot, 0.025, na.rm = TRUE),
    f1_hi    = quantile(f1_boot, 0.975, na.rm = TRUE),
    jacc_lo  = quantile(jacc_boot, 0.025, na.rm = TRUE),
    jacc_hi  = quantile(jacc_boot, 0.975, na.rm = TRUE),
    .groups = "drop"
  )

label_perf_ci <- label_perf %>%
  left_join(boot_ci, by = "label")

# ---------------------------
# Ranked bar charts with CIs
# ---------------------------

# A) Labels ranked by F1, with 95% CI error bars; support shown as text
plot_f1_ranked <- label_perf_ci %>%
  arrange(desc(f1)) %>%
  mutate(label = factor(label, levels = label)) %>%
  ggplot(aes(x = label, y = f1)) +
  geom_col() +
  geom_errorbar(aes(ymin = f1_lo, ymax = f1_hi), width = 0.2) +
  geom_text(aes(y = pmax(f1_hi, f1, na.rm = TRUE) + 0.02,
                label = paste0("n=", comma(support))),
            size = 3, vjust = 0) +
  coord_flip() +
  scale_y_continuous(limits = c(0, 1.05), breaks = seq(0, 1, 0.2)) +
  labs(
    x = "Label",
    y = "F1 (LLM vs consensus)",
    title = "Per-label performance ranked by F1",
    subtitle = "Bars = F1; error bars = 95% bootstrap CI; text = consensus support"
  ) +
  theme_minimal()

# B) Labels ranked by Jaccard, with 95% CI error bars; support shown as text
plot_jacc_ranked <- label_perf_ci %>%
  arrange(desc(jaccard)) %>%
  mutate(label = factor(label, levels = label)) %>%
  ggplot(aes(x = label, y = jaccard)) +
  geom_col() +
  geom_errorbar(aes(ymin = jacc_lo, ymax = jacc_hi), width = 0.2) +
  geom_text(aes(y = pmax(jacc_hi, jaccard, na.rm = TRUE) + 0.02,
                label = paste0("n=", comma(support))),
            size = 3, vjust = 0) +
  coord_flip() +
  scale_y_continuous(limits = c(0, 1.05), breaks = seq(0, 1, 0.2)) +
  labs(
    x = "Label",
    y = "Jaccard (LLM vs consensus)",
    title = "Per-label performance ranked by Jaccard",
    subtitle = "Bars = Jaccard; error bars = 95% bootstrap CI; text = consensus support"
  ) +
  theme_minimal()

# Print (or ggsave) the plots
plot_f1_ranked
plot_jacc_ranked

```


---

## 6) Vote-fraction heatmap (contentiousness map)

**Why:** shows how much coders agree per statement × label; identifies ambiguous items.
**What:** heatmap of `vote_frac` with statements (rows) clustered, labels (cols) ordered by prevalence.

```{r}

library(tidyr)
library(forcats)

mat_long <- vote_detail %>%
  mutate(label = as.character(label)) %>%
  group_by(label) %>%
  mutate(label_count = n()) %>%
  # mutate(label = forcats::fct_reorder(label, n(), .fun = sum)) %>%
  ungroup() %>%
  mutate(label = fct_reorder(label, label_count))

p_heat <- 
  ggplot(mat_long, 
         aes(x = label, y = factor(statement_id),
             fill = vote_frac)) +
  geom_tile() +
  scale_fill_viridis_c(limits = c(0,1), direction = -1) +
  labs(x = "Label", y = "Statement", fill = "Vote fraction") +
  theme(axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(),
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)
        )

p_heat


## save figure
f <- file.path(dir.figures, 'llm_accuracy', paste0('Vote-fraction heatmap_', ymd, '.png'))
func_ggsave_nature(path = f, column = 2)
```

---

## 7) Error anatomy (TP/FP/FN) per label

This script analyzes error patterns of an LLM's label predictions compared to a consensus (ground truth). Here's a breakdown:

  *Purpose: Identifies how the LLM makes mistakes for each label:*

  TP (True Positive):  LLM correctly predicted the label
  FP (False Positive): LLM predicted the label when it shouldn't have
  FN (False Negative): LLM missed the label when it should have predicted it

```{r}

# Build label-wise TP/FP/FN vs consensus
lab_counts <- universe_by_stmt |>
  # Joins LLM predictions with consensus labels
  dplyr::left_join(consensus, by = "statement_id") |>
  # Expands label_universe so each row = one statement-label combination
  tidyr::unnest_longer(label_universe, values_to="label") |>
  # Classify each label instance
  dplyr::mutate(
    in_llm  = purrr::map2_lgl(labels_llm, label, ~ .y %in% .x),
    in_cons = purrr::map2_lgl(labels_consensus, label, ~ .y %in% (.x %||% numeric(0))),
    cat = dplyr::case_when(in_llm & in_cons ~ "TP",  # LLM said yes, consensus said yes
                           in_llm & !in_cons ~ "FP", # LLM said yes, consensus said no
                           !in_llm & in_cons ~ "FN", # LLM said no, consensus said yes
                           TRUE ~ "TN")              # LLM said no, consensus said no
  ) |>
  # Count and prepare for plotting
  dplyr::count(label, cat) |>
  dplyr::filter(cat != "TN") |>    # Remove True Negatives (not interesting)
  dplyr::group_by(label) |>
  dplyr::mutate(total = sum(n)) |> # Total errors per label
  dplyr::ungroup() |>
  dplyr::mutate(label = reorder(label, -total)) # Order by most errors

# Colors = TP (correct), FP (over-labeled, or over-predict), FN (missed, or under-predict)
# A label with mostly FP → LLM is too aggressive with this label
# A label with mostly FN → LLM frequently misses this label
# A label with mostly TP → LLM performs well on this label



# Define clear colors for each category
error_colors <- c(
  "TP" = "#2ecc71",  # Green - correct predictions
  "FP" = "#e74c3c",  # Red - over-predictions (Type I error)
  "FN" = "#f39c12"   # Orange - missed predictions (Type II error)
)


p_err <-
  ggplot(lab_counts, aes(label, n, fill = cat)) +
  geom_col() +
    
  scale_fill_manual(
  values = error_colors,
  labels = c("TP" = "True Positive (Correct)",
             "FP" = "False Positive (Over-labeled)", 
             "FN" = "False Negative (Missed)")
) +
    
  coord_flip() +
  labs(x = "Label", y = "Count", fill = "Classification",
       title = "Error Anatomy: LLM Performance by Label") +
  theme(
    legend.position = "top",
    panel.grid.major.y = element_blank()
  )
p_err


## save figure
f <- file.path(dir.figures, 'llm_accuracy', paste0('LLM Performance by Label_', ymd, '.png'))
func_ggsave_nature(plot = p_err, path = f, column = 2)
```

---

## 8) Threshold sweep (consensus as ≥k votes)

**Why:** shows robustness; reviewers may ask “what if consensus rule changes.”
**What:** vary `k` (1…max coders) and plot macro-F1 (LLM vs consensus(k)).

```{r}
k_vals <- 1:7
res_k <- purrr::map_dfr(k_vals, function(k) {
  cons_k <- coder_long |>
    dplyr::group_by(statement_id, label) |>
    dplyr::summarise(votes = sum(y_true), .groups="drop") |>
    dplyr::group_by(statement_id) |>
    dplyr::summarise(labels_consensus = list(sort(unique(label[votes >= k]))), .groups="drop")

  m <- universe_by_stmt |>
    dplyr::left_join(cons_k, by="statement_id") |>
    dplyr::mutate(
      labels_consensus = purrr::map(labels_consensus, ~ .x %||% numeric(0)),
      tp = purrr::map2_int(labels_llm, labels_consensus, ~ length(intersect(.x,.y))),
      fp = purrr::map2_int(labels_llm, labels_consensus, ~ length(setdiff(.x,.y))),
      fn = purrr::map2_int(labels_consensus, labels_llm, ~ length(setdiff(.x,.y))),
      precision = ifelse(tp+fp>0, tp/(tp+fp), NA_real_),
      recall    = ifelse(tp+fn>0, tp/(tp+fn), NA_real_),
      f1        = ifelse(!is.na(precision+recall) & precision+recall>0, 
                         2*precision*recall/(precision+recall), NA_real_)
    ) |>
    dplyr::summarise(macro_f1 = mean(f1, na.rm=TRUE), .groups="drop")

  dplyr::tibble(k = k, macro_f1 = m$macro_f1)
})


## Consensus-threshold sweep (robustness)
# p_k <- 
ggplot(res_k, aes(k, macro_f1)) +
  geom_line() + 
  geom_point(size = 1.6) +
  scale_x_continuous(breaks = k_vals) +
  labs(x = "Consensus threshold (k votes)", y = "Macro F1 (LLM vs consensus)") 
```

---

## ? 9) UpSet of label overlaps (LLM vs consensus vs coders)

**Why:** compact view of intersection structure (which labels everyone agrees on).
**What:** UpSet plot of sets {LLM}, {Consensus}, optionally {Coder A}, {Coder B}, …
**Note:** use `{ComplexUpset}`:

```{r}
# install.packages("ComplexUpset")
library(ComplexUpset)
# build a long binary matrix across sets, then:
ComplexUpset::upset(data_matrix, intersect = c("LLM","Consensus","Coder_A","Coder_B"))
```

---

## 10) “Hard cases” gallery (auditable figure/table)

**Why:** qualitative insight; great for supplements.
**What:** table/figure listing the top N statements with lowest F1 (or zero overlap), showing LLM set, consensus set, vote fractions, and coder count.

```{r}
hard <- llm_vs_consensus |>
  dplyr::arrange(dplyr::coalesce(f1, -Inf)) |>
  dplyr::slice_head(n = 20) |>
  dplyr::left_join(vote_detail |> dplyr::group_by(statement_id) |>
                     dplyr::summarise(n_labels = dplyr::n(), .groups="drop"),
                   by="statement_id")
# then gt::gt(hard) for a nice table
```









# ----------------------

* Design tips (so they look like a paper)

* Use **consistent fonts** (e.g., `theme_minimal(base_family="Arial")` if available).
* Prefer **color-blind safe** palettes (`scale_fill_brewer(palette="Set2")` or `viridis`).
* Show **uncertainty** (IQR/CI) where possible, not just means.
* Use **panel letters** (A, B, C) if figures combine multiple plots.
* Put **key numbers in captions** (e.g., macro/micro F1, exact-match rate).

If you tell me your target journal style (e.g., Nature Cities), I can format sizes, fonts, and export DPI accordingly, and bundle these into a single R script that saves ready-to-submit PNG/PDFs.













## measure agreement between LLM and coder

`binary overlap flag` -- overlap_any: 1 if any element in targets_llm is in targets_coder, else 0.

`similarity score (Jaccard)` -- jaccard: 0–1 similarity; 1 means identical sets, 0 means no overlap. proportion/score (e.g. Jaccard)

`exact-set match flag` exact_match: 1 if the two sets are exactly the same (ignores order/dups), else 0.

```{r}
names(dfs)

unique(dfs$coder)


library(dplyr)
library(stringr)
library(purrr)

# helper: parse "5.5, 8.3" -> numeric c(5.5, 8.3); handle "NA", blanks
parse_vals <- function(x) {
  if (is.na(x) || trimws(x) == "") return(numeric(0))
  xs <- str_split(x, ",")[[1]]        # split only on comma
  xs <- str_trim(xs)                  # remove leading/trailing whitespace
  xs <- xs[xs != "" & xs != "NA"]     # drop empties or "NA" strings
  suppressWarnings(unique(as.numeric(xs)))
}

df_out <- dfs %>%
  rowwise() %>%
  mutate(
    llm_vals   = list(parse_vals(targets_llm)),
    coder_vals = list(parse_vals(targets_coder)),
    inter_len  = length(intersect(llm_vals, coder_vals)),
    union_len  = length(union(llm_vals, coder_vals)),
    # 1) Binary: any overlap?
    overlap_any = as.integer(inter_len > 0),
    # 2) Similarity score: Jaccard = |A ∩ B| / |A ∪ B|
    jaccard     = ifelse(union_len > 0, inter_len / union_len, NA_real_),
    # 3) Exact set match (order ignored, duplicates ignored)
    exact_match = as.integer(setequal(llm_vals, coder_vals))
  ) %>%
  ungroup() %>%
  # select(-llm_vals, -coder_vals, -inter_len, -union_len) %>%
  as.data.frame()

```



## compute agreement metrics at two levels:

Row-level (per item): precision, recall, F1

Dataset-level: macro- and micro-averages, plus class-wise performance


  `per_row`: see which items disagree and why (low recall ⇒ LLM missed coder labels; low precision ⇒ extra labels predicted).
  
  `macro`: average performance across items (treats each row equally).
  
  `micro`: pooled performance over all items (weights rows by number of labels).
  
  `by_label`: which target numbers the LLM nails or struggles with.

*Optional add-ons*

  Thresholding/tolerance: if two numbers within ±0.02 should count as the same, replace the exact membership checks with the fuzzy functions I shared earlier.
  
  Diagnostics: inspect rows with f1 == 0 or is.na(precision) (often when LLM predicted nothing but coder had labels, or vice versa).
  
  Plots: histogram of jaccard; bar chart of label-wise F1 by support.

```{r}

library(dplyr)
library(stringr)
library(purrr)
library(tidyr)

# --- parser (from earlier, with trimming) ---
parse_vals <- function(x) {
  if (is.na(x) || trimws(x) == "") return(numeric(0))
  xs <- str_split(x, ",")[[1]]
  xs <- str_trim(xs)
  xs <- xs[xs != "" & xs != "NA"]
  suppressWarnings(unique(as.numeric(xs)))
}

# Assume df has columns: targets_llm, targets_coder
df_parsed <- dfs %>%
  mutate(row_id = row_number(),
         llm   = map(targets_llm, parse_vals),
         coder = map(targets_coder, parse_vals))

# --- explode to long for confusion components per row/label ---
df_long <- df_parsed %>%
  rowwise() %>%
  mutate(all_labels = list(sort(unique(c(llm, coder))))) %>%
  ungroup() %>%
  select(row_id, llm, coder, all_labels) %>%
  tidyr::unnest_longer(all_labels, values_to = "label") %>%
  group_by(row_id) %>%
  mutate(
    y_true = label %in% coder[[1]],
    y_pred = label %in% llm[[1]]
  ) %>%
  ungroup()

# --- per-row counts & metrics ---
per_row <- df_long %>%
  group_by(row_id) %>%
  summarise(
    tp = sum(y_true & y_pred),
    fp = sum(!y_true & y_pred),
    fn = sum(y_true & !y_pred),
    precision = ifelse(tp + fp > 0, tp / (tp + fp), NA_real_),
    recall    = ifelse(tp + fn > 0, tp / (tp + fn), NA_real_),
    f1        = ifelse(!is.na(precision + recall) & precision + recall > 0,
                       2 * precision * recall / (precision + recall), NA_real_)
  ) %>%
  ungroup()

# --- add your earlier columns (overlap_any, jaccard, exact_match) if you created df_out ---
# If you haven't, you can compute them quickly here:
quick_overlap <- df_parsed %>%
  mutate(
    jaccard = map2_dbl(llm, coder, ~ {
      inter <- length(intersect(.x, .y))
      uni   <- length(union(.x, .y))
      if (uni > 0) inter/uni else NA_real_
    }),
    overlap_any = as.integer(jaccard > 0),
    exact_match = as.integer(jaccard == 1)
  ) %>% select(row_id, overlap_any, jaccard, exact_match)

per_row <- per_row %>% left_join(quick_overlap, by = "row_id")


# --- dataset-level (macro & micro) ---
macro <- per_row %>%
  summarise(
    macro_precision = mean(precision, na.rm = TRUE),
    macro_recall    = mean(recall,    na.rm = TRUE),
    macro_f1        = mean(f1,        na.rm = TRUE),
    mean_jaccard    = mean(jaccard,   na.rm = TRUE),
    exact_match_rate= mean(exact_match, na.rm = TRUE),
    any_overlap_rate= mean(overlap_any, na.rm = TRUE)
  )

micro <- df_long %>%
  summarise(
    tp = sum(y_true & y_pred),
    fp = sum(!y_true & y_pred),
    fn = sum(y_true & !y_pred)
  ) %>%
  mutate(
    micro_precision = ifelse(tp + fp > 0, tp / (tp + fp), NA_real_),
    micro_recall    = ifelse(tp + fn > 0, tp / (tp + fn), NA_real_),
    micro_f1        = ifelse(!is.na(micro_precision + micro_recall) &
                               micro_precision + micro_recall > 0,
                             2 * micro_precision * micro_recall /
                               (micro_precision + micro_recall), NA_real_)
  ) %>%
  select(micro_precision, micro_recall, micro_f1)


# --- class-wise performance (how each target number performs overall) ---
by_label <- df_long %>%
  group_by(label) %>%
  summarise(
    tp = sum(y_true & y_pred),
    fp = sum(!y_true & y_pred),
    fn = sum(y_true & !y_pred),
    precision = ifelse(tp + fp > 0, tp / (tp + fp), NA_real_),
    recall    = ifelse(tp + fn > 0, tp / (tp + fn), NA_real_),
    f1        = ifelse(!is.na(precision + recall) & precision + recall > 0,
                       2 * precision * recall / (precision + recall), NA_real_),
    support   = sum(y_true)   # how often the coder used this label
  ) %>%
  arrange(desc(support)) %>%
  ungroup()

```




```{r - plot - jaccard}

library(dplyr)
library(ggplot2)
# per_row should contain a numeric column `jaccard` from the previous step

df_plot <- per_row %>% filter(!is.na(jaccard))
m <- mean(df_plot$jaccard, na.rm = TRUE)

# get a reasonable y for the label (top of the histogram)
h <- hist(df_plot$jaccard, breaks = seq(0, 1, by = 0.05), plot = FALSE)
y_top <- max(h$counts, na.rm = TRUE)

df_lab <- data.frame(jaccard = m, y = y_top)

ggplot(df_plot, aes(x = jaccard)) +
  geom_histogram(binwidth = 0.05, boundary = 0, closed = "left", color = "white") +
  geom_vline(xintercept = m, linetype = "dashed") +
  geom_text(data = df_lab, aes(x = jaccard, y = y, label = sprintf("Mean = %.2f", jaccard)),
            vjust = -0.3, inherit.aes = FALSE) +
  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.1)) +
  labs(x = "Jaccard similarity", y = "Count",
       title = "Distribution of Jaccard similarity (LLM vs. Coder)") +
  theme_minimal()


```








```{r}
## unify the checking result to "0, 1, NA" only ------------------------------------------
ds0 <- dfs %>%
  dplyr::mutate(coder = gsub(pattern = '.*_', '', coder)) %>%                    ## clean coder name
  dplyr::mutate(correct_or_not = gsub(pattern = '\\*', '', correct_or_not)) %>%  ## clean coder's response
  dplyr::mutate(correct = case_when(correct_or_not == "1" ~ 1,
                                    correct_or_not == "0" ~ 0,
                                    is.na(correct_or_not) ~ NA_real_,
                                    grepl("^Y", correct_or_not) ~ 1,
                                    TRUE                  ~ 0)) %>%
  dplyr::select(coder, correct, correct_or_not, everything()) 


ds1 <- ds0 %>%
  arrange(correct_or_not)



## to check the alignment across coders --------------------------------------------------
ds2 <- ds1 %>%
  dplyr::select(coder, correct, company, index) %>%
  ## only analyze rows being checked
  # dplyr::filter(!is.na(correct)) %>%
  spread(key = coder, value = correct) %>%
  dplyr::mutate(same12 = ifelse(MC == VF, 1, 0),
                same13 = ifelse(MC == YL, 1, 0),
                same14 = ifelse(MC == YZ, 1, 0),
                same23 = ifelse(VF == YL, 1, 0),
                same24 = ifelse(VF == YZ, 1, 0),
                same34 = ifelse(YL == YZ, 1, 0),
                same3  = ifelse(MC == YL & YZ == YL, 1, 0),
                same4  = ifelse(MC == YL & YZ == YL & VF == YL, 1, 0)) %>%
  as.data.frame()
```



## how good TM is
```{r}

names(ds2)

### The accuracy of our SDGdetector judged by SDG experts
ds_accuracy <- ds2 %>%
  dplyr::select(company, index, MC, VF, YL, YZ) %>%
  gather(key = 'coder', value = "value", 3:ncol(.)) %>%
  dplyr::group_by(coder) %>%
  dplyr::summarise(accuracy = sum(value, na.rm = T)/nrow(ds2)) %>%
  dplyr::mutate(id = row.names(.)) %>% dplyr::select(id, everything())
ds_accuracy


### test code
# (sum(ds2$MC, na.rm = T)/nrow(ds2)) %>% 
#   scales::percent() %>% 
#   cat('accuracy by MC:', .)
```






## check the alignment across coders
```{r}
names(ds2)

### The inter-expert reliability 
ds_intercoder <- ds2 %>%
  dplyr::select(company, index, same12, same13, same14, same23, same24, same34) %>%
  gather(key = 'pair', value = "value", 3:ncol(.)) %>%
  dplyr::group_by(pair) %>%
  dplyr::summarise(alignment = sum(value, na.rm = T)/nrow(ds2))

ds_intercoder
```


## save result in xlsx
```{r}
## save to XLSX for easy read
f <- paste0(dirname(dir.task1), '/', 'results_accuracy_',   basename(dir.task1), '.xlsx'); f
writexl::write_xlsx(ds_accuracy, path = f)

f <- paste0(dirname(dir.task1), '/', 'results_intercoder_', basename(dir.task1), '.xlsx'); f
writexl::write_xlsx(ds_intercoder, path = f)
```



```{r read in results}
## for accuracy 
ind <- 'results_accuracy_'
fs <- list.files(path = dirname(dir.task1), pattern = ind, full.names = T)
# f <- fs[1]
dfs_acc <- data.frame()

for (f in fs) {
  # print(f)
  round_id <- f %>%
    basename(.) %>%
    gsub(ind, '', .) %>%
    gsub('task1_|_done.xlsx', '', .)
  # print(round_id)
  
  acc <- readxl::read_excel(f) %>%
    dplyr::mutate(round_id = round_id)
  dfs_acc <- rbind(dfs_acc, acc)
}



## for intercoder
ind <- 'results_intercoder_'
fs <- list.files(path = dirname(dir.task1), pattern = ind, full.names = T)
# f <- fs[1]
dfs_int <- data.frame()

for (f in fs) {
  # print(f)
  round_id <- f %>%
    basename(.) %>%
    gsub(ind, '', .) %>%
    gsub('task1_|_done.xlsx', '', .)
  # print(round_id)
  
  int <- readxl::read_excel(f) %>%
    dplyr::mutate(round_id = round_id)
  dfs_int <- rbind(dfs_int, int)
}
```


```{r plot acc}
## plot ----------------------------------------------------------------------------------

mean(dfs_acc$accuracy)
fun_mean <- function(x){
  return(data.frame(y=mean(x),label=round(mean(x,na.rm=T), digits = 2)))}

p1 <- dfs_acc %>%
  ggplot(aes(x = 1, y = accuracy)) +
  geom_boxplot(fill = 'gray', show.legend = F, varwidth = .5) + # , fill = round_id
  stat_summary(fun =mean, geom="point", shape=15, size=3, alpha = 0.6, color="red", fill="red") +
  stat_summary(fun.data = fun_mean, geom="text", vjust=.5, hjust = -0.2, color="red") +
  scale_y_continuous(limits = c(0.7, .85)) +
  geom_jitter(color="black", shape = 1, size=2, alpha=0.6, width = .05) +
  xlab('Overall') +
  ylab('Accuracy') +
  theme_bw() +
  theme(panel.grid = element_blank(), 
        axis.text.x = element_text(colour='transparent'), 
        axis.ticks = element_blank(), 
        legend.position = "none")
p2 <- dfs_acc %>%
  ggplot(aes(x = round_id, y = accuracy)) + # , fill = round_id
  geom_boxplot(alpha = .8) + # 
  scale_y_continuous(limits = c(0.7, .85)) +
  geom_jitter(color="black", shape = 1, size=2, alpha=0.6, width = .05) +
  xlab('Each Round of Inspection') +
  ylab('') +
  theme_bw() +
  theme(legend.position = "none")
p <- ggarrange(p1, p2, widths = c(1,3))

fname <- paste0(dir.figures, 'Inspection_Accuracy_', ymd, '.png'); fname
ggsave(fname, plot = p, width = 6.5, height = 3.2, units = 'in', dpi = 300)  
```


```{r plot inter-coder}

p3 <- dfs_int %>%
  ggplot(aes(x = 1, y = alignment)) +
  geom_boxplot(fill = 'gray', show.legend = F, varwidth = .5) + # , fill = round_id
  stat_summary(fun =mean, geom="point", shape=15, size=3, alpha = 0.6, color="red", fill="red") +
  stat_summary(fun.data = fun_mean, geom="text", vjust=.7, hjust = -0.3, color="red") +
  scale_y_continuous(limits = c(0.7, .9)) +
  geom_jitter(color="black", shape = 1, size=2, alpha=0.6, width = .05) +
  xlab('Overall') +
  ylab('Inter-expert Reliability') +
  theme_bw() +
  theme(panel.grid = element_blank(), 
        axis.text.x = element_text(colour='transparent'), 
        axis.ticks = element_blank(), 
        legend.position = "none")


p4 <- dfs_int %>%
  ggplot(aes(x = round_id, y = alignment)) + # , fill = round_id
  geom_boxplot(alpha = .8) + # 
  scale_y_continuous(limits = c(0.7, .9)) +
  geom_jitter(color="black", shape = 1, size=2, alpha=0.6, width = .05) +
  xlab('Each Round of Inspection') +
  ylab('') +
  theme_bw() +
  theme(legend.position = "none")
p <- ggarrange(p3, p4, widths = c(1,3))

getwd()
fname <- paste0(dir.figures, 'Inspection_InterExpert_', ymd, '.png');fname
ggsave(fname, plot = p, width = 6.5, height = 3.2, units = 'in', dpi = 300)  
```


  *Test code
```{r}

# (sum(ds2$same3, na.rm = T)/nrow(ds2)) %>% 
#   scales::percent() %>% 
#   cat('Alignment between MC-YL-YZ:', .)
# 
# (sum(ds2$same4, na.rm = T)/nrow(ds2)) %>% 
#   scales::percent() %>% 
#   cat('Alignment between 4 ppl:', .)




## only look at the rows inspected by all of us ------------------------------------------
# ds4 <- ds2 %>%
#   dplyr::filter(!is.na(YZ))
# 
# (sum(ds4$same3, na.rm = T)/nrow(ds4)) %>% 
#   scales::percent() %>% 
#   cat('Alignment between MC-YL-YZ:', ., '(when only count rows being inspected by all)')
# 
# (sum(ds4$same4, na.rm = T)/nrow(ds4)) %>% 
#   scales::percent() %>% 
#   cat('Alignment between 4 ppl:', ., '(when only count rows being inspected by all)')
```




## look into the difference in text

```{r}

## pull coder comments together and add to the compare table later
dsnote <- ds0 %>% dplyr::select(coder, company, index, 
                                # statement, 
                                # target_by_machine, 
                                coder_notes) %>%
  # dplyr::mutate(id_order = row.names(.)) %>%
  # ungroup() %>% 
  group_by(coder) %>%
  as.data.frame() %>%
  # tidyr::pivot_wider(id_cols = c(company, index), names_from = coder, values_from = coder_notes) %>%
  tidyr::spread(key = coder, value = coder_notes) %>%
  as.data.frame()
  
dsnote1 <- d %>%
  dplyr::select(index, statement, target_by_machine) %>%
  left_join(., dsnote, by = 'index')
  
## the comparison table
dsdiff <- ds2 %>%
  dplyr::select(1:6, same13, same23, same34, same4) %>%
  left_join(x =., 
            y = dsnote1, 
            by = c('company', 'index')) %>%
  # arrange(same4) %>%
  arrange(index) %>%
  as.data.frame()

dsdiff[, 13:16] <- sapply(dsdiff[, 13:16], function(col) ifelse(is.na(col), ' ', col))

## save to XLSX for easy read
f <- paste0(dirname(dir.task1), '/', basename(dir.task1), '_analysis.xlsx'); f
writexl::write_xlsx(dsdiff, path = f)

```




# Process of evaluate the inspection results

  1. Compare the difference between `YL` and others Based on the file "taskx_Rx_done_analysis.xlsx".
  
  2. Read each notes (either from the above xlsx or individual xlsx) to understand the difference. 
  
  3. Edit "SDG keywords for Text Mining Codebook" according to the notes and comments. 
  
  4. Add the controversial ones to the Appendix of "SDG_TM_Inspection_Protocol" for further discussion. 
  
