---
title: "Untitled"
author: "Yingjie"
date: "12/3/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r}
### To clear your environment 
remove(list = ls())


library(tidyverse)
library(janitor)
```



## Raw data

### Wiki data

  1. Refer to the *List of countries and territories by land and maritime borders* from  https://en.wikipedia.org/wiki/List_of_countries_and_territories_by_land_and_maritime_borders; 
  
  2. *Convert Wiki Tables to CSV* using https://wikitable2csv.ggor.de/ (default setting) and download as *table-1.csv*. 
  
  3. Read into R and clean the table
  
  
```{r}
csv <- paste0('./Data/country/', 'wiki_List_of_ISO_3166_country_codes.csv')
# csv <- paste0('./Data/_distant_matrix/', 'table-1 (1).csv')

b <- read_csv(csv, skip = 1) %>%
  clean_names() %>%
  as.data.frame()

names(b)

names(b) <- c('country_name', 'official_state_name', 'sovereignty', 'alpha_2_code', 'alpha_3_code', 'numeric_code', 'subdivision_code_links', 'internet_cc_tld')


## bc -> borders cleaned
bc <- b %>%
  dplyr::filter(!is.na(country_name)) %>%
  dplyr::filter(stringr::str_detect(country_name, ' – See', negate = T)) %>%
  dplyr::mutate(country_name = gsub("\\s*\\[[^\\)]+\\]", "", country_name), ## remove `[numbers]`
                country_name = gsub("\\s*\\([^\\)]+\\)", "", country_name), ## remove `(strings)`
                country_name = stringr::str_replace_all(string = country_name, fixed("\n"), " "), ## erase new lines
                country_name = stringr::str_replace_all(string = country_name, fixed("\r"), " "), ## erase carriage return
                country_name = stringr::str_replace_all(string = country_name, fixed("\t"), " "), ## erase tabs
) %>%
  as.data.frame()
  
fname <- paste0('./Data/country/', 'wiki_List_of_ISO_3166_country_codes_cleaned.xlsx')
writexl::write_xlsx(x = bc, path = fname)
```

*Note*: this wiki data list was then added to the file '_ctr_iso2_iso3.xlsx'. 



### naturalearth 
```{r}
library(rnaturalearthdata)
# library(rnaturalearth)
# library(sf)

shp <- ne_countries(scale = 'medium', type = 'countries', returnclass = 'sf') %>%
  st_drop_geometry() %>%
  dplyr::select(name, type, iso_a3, economy, income_grp) %>%
  dplyr::mutate(iso_a3 = ifelse(name == 'France', 'FRA', iso_a3))
# plot(shp['iso_a3'])
shp_iso_na <- shp %>% 
  dplyr::filter(is.na(iso_a3))
shp_iso_na$name


### fill the gap 
shp <- shp %>%
  dplyr::mutate(iso_a3 = ifelse(name == "Norway", 'NOR', iso_a3),
                iso_a3 = ifelse(name == "N. Cyprus", 'CYP', iso_a3)) %>%
  filter(name != 'Antarctica')


fname <- paste0('./Data/country/', 'naturalearth_country_names.xlsx'); fname
writexl::write_xlsx(x = shp, path = fname)
```



## Country

### - Indididual names

```{r}
dirname(getwd())

xlsx <- paste0(dirname(getwd()), '/SDGs_Metacouplings_private/Data/', '_ctr_iso2_iso3.xlsx'); xlsx
xls2 <- paste0('./Data/country/', 'naturalearth_country_names.xlsx')

excel_sheets(xlsx)
## --> "readme" "fao"  "iso"  "iban" "worldbank" "wiki"

func_get_country <- function(xlsx, sheet, column) {
  ctr_name <- readxl::read_excel(path = xlsx, sheet = sheet) %>%
    dplyr::select(column)
  names(ctr_name) <- 'name'
  return(ctr_name)
}

ctr_name_fao  <- func_get_country(xlsx = xlsx, sheet = 'fao', column = 1)
ctr_name_iso  <- func_get_country(xlsx = xlsx, sheet = 'iso', column = 1)
ctr_name_iban <- func_get_country(xlsx = xlsx, sheet = 'iban', column = 1)
ctr_name_wiki <- func_get_country(xlsx = xlsx, sheet = 'wiki', column = 1)
ctr_name_naturalearth <- func_get_country(xlsx = xls2, sheet = 1, column = 1)
ctr_name_worldbank    <- readxl::read_excel(path = xlsx, sheet = 'worldbank') %>%
    dplyr::filter(!is.na(Region)) %>%
    dplyr::select(1)
names(ctr_name_worldbank) <- 'name'


ctr_names <- rbind(ctr_name_fao, ctr_name_iso, ctr_name_iban, ctr_name_wiki, ctr_name_worldbank, ctr_name_naturalearth) %>%
  dplyr::filter(stringr::str_detect(name, 'Least developed|income', negate = T)) %>%
  dplyr::mutate(name = gsub("\\s*\\[[^\\)]+\\]", "", name), ## remove `[numbers]`
                name = gsub("\\s*\\([^\\)]+\\)", "", name), ## remove `(strings)`
                name = stringr::str_replace_all(string = name, fixed("\n"), " "), ## erase new lines
                name = stringr::str_replace_all(string = name, fixed("\r"), " "), ## erase carriage return
                name = stringr::str_replace_all(string = name, fixed("\t"), " "), ## erase tabs
                name = gsub("\\.$", "", name),        ## remove period in the end of a string
                name = gsub(", The|\\*", "", name),   ## remove ", The" and "*"
                name = stringr::str_squish(name),     ## remove leading & trailing whitespace, and repeated whitespace inside a string
                ) %>%
  dplyr::distinct(name) %>%
  arrange(name)
```





### - Individual country code

```{r}
ctr_name_fao  <- func_get_country(xlsx = xlsx, sheet = 'fao', column = 3)
ctr_name_iso  <- func_get_country(xlsx = xlsx, sheet = 'iso', column = 3)
ctr_name_iban <- func_get_country(xlsx = xlsx, sheet = 'iban', column = 3)
ctr_name_wiki <- func_get_country(xlsx = xlsx, sheet = 'wiki', column = 5)
ctr_name_naturalearth <- func_get_country(xlsx = xls2, sheet = 1, column = 3)
ctr_name_worldbank    <- readxl::read_excel(path = xlsx, sheet = 'worldbank') %>%
  dplyr::filter(!is.na(Region)) %>%
  dplyr::select(2)
names(ctr_name_worldbank) <- 'name'


ctr_iso3 <- rbind(ctr_name_fao, ctr_name_iso, ctr_name_iban, ctr_name_wiki, ctr_name_worldbank, ctr_name_naturalearth) %>%
  dplyr::filter(!is.na(name)) %>%
  dplyr::distinct(name) %>%
  arrange(name)
```



## Regions

### Region names and number of country in each region 

  The region names are manually collected from Wiki, World Bank. 
  
```{r}
xlsx <- paste0('./Data/country/', 'Region_names.xlsx'); xlsx

regions <- readxl::read_excel(path = xlsx, sheet = 1) %>%
  as.data.frame()

```





## Bind together with multipliers
```{r}
ctr_names$group = 'country name'
ctr_names$num_country = 1

ctr_iso3$group = 'country iso3' 
ctr_iso3$num_country = 1


regions <- regions %>% dplyr::select(name, num_country)
regions$group = 'region name' 


## bind together 
country_region_names <- rbind(ctr_names, ctr_iso3, regions) %>%
  distinct(name, .keep_all = T) %>%
  # dplyr::mutate(name = paste0('^', name, '$')) %>% ## this is wrong, as this asking each sentence starting and ending with the 'name'
  as.data.frame()


## save to database
save(country_region_names, file = paste0('./Data/data_TextMining/database/', 'country_region_names.RData'))

## save to `SDGdetector` package
save(country_region_names, file = paste0('./Code/SDGdetector/data/', 'country_region_names.RData'))
```



