---
title: "Text_mining"
author: "Yingjie"
date: "6/17/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---


# Directories and packages

```{r include=FALSE}
### To clear your environment 
remove(list = ls())

source('./Code/_packages.R')

```


# SDG search terms


  Make a list of keywords for SDGs.

|SDG_id       |SDG_keywords     |
|SDG1_1       |keywords here    |

  These SDG search terms can be *direct mention*, such as "SDG 1", "SDG 2", "SDG 1.2", "SDG 1.a", or *indirect mention*.  

  This collection includes terms that are directly related to SDGs, i.e., if companies specifically mention SDG ids (e.g., 'SDG 13'), or the target or indicator ids (e.g., SDG 13.1.a). 
  
```{r - 1. Collection - direct commit}
source('./Code/helper_SDG_search_terms.R')

SDG_keys <- rbind(goal_keys, target_keys)

SDG_ls_str <- SDG_keys$SDG_id %>% as.character(); SDG_ls_str


SDG_keys_drc <- SDG_keys
```





 This collection includes terms that are *indirectly* related to SDGs, i.e., the terms are constructed based on the alignment to the description and meanings of each SDG or Target. 
  
```{r - 2. Collection - indrect commit}
source('./Code/helper_SDG_search_terms.R')

### bind these vectors and make it a dataframe to work from ----------------------------------------
SDG_ls_str <- ls(pattern = "SDG[0-9].*") %>% sort(); SDG_ls_str

SDG_ls_str <- grep("['xyzw]", SDG_ls_str, value = TRUE, invert = TRUE) # invert = TRUE means to return the values that were not matched.
SDG_ls_str

SDG_keys <- data.frame()  

for (i in 1:length(SDG_ls_str) ) {
  # print(i)
  sdg_i_str <- SDG_ls_str[i]
  sdg_i_obj <- get(sdg_i_str)
  df_i <- data.frame(SDG_id       = sdg_i_str, 
                     SDG_keywords = sdg_i_obj)
  SDG_keys <- rbind(SDG_keys, df_i) %>%
    dplyr::mutate(SDG_id       = as.character(SDG_id),
                  SDG_keywords = as.character(SDG_keywords))
}


SDG_keys_indrc <- SDG_keys
```




```{r - 3. Collection - both}

SDG_keys_drc$match_tpye   <- 'direct'
SDG_keys_indrc$match_tpye <- 'indirect'

SDG_keys <- rbind(SDG_keys_drc, SDG_keys_indrc)



## Save to database --------------------------------------------------------------------------------

### 1. for this project
fname <- paste0('./Data/data_TextMining/database/', 'SDG_keys.RData'); fname
save(SDG_keys_drc, SDG_keys_indrc, SDG_keys, file = fname)


### 2. save to `SDG_TM` for R package development
fname <- paste0(dirname(getwd()), '/SDG_TM/data/SDG_keys.RData'); fname
save(SDG_keys_drc, SDG_keys_indrc, SDG_keys, file = fname)

### 3. for Meng Cai's repo
fname <- paste0('./Code/findSDGs/R/', 'SDG_keys.RData'); fname
save(SDG_keys_drc, SDG_keys_indrc, SDG_keys, file = fname)
```
